### 2018-09-19 document/ms.tex
Start of the draft manuscript-- placeholders for now

%\documentclass[iop,revtex4]{emulateapj}% change onecolumn to iop for fancy, iop to twocolumn for manuscript
\documentclass[twocolumn]{emulateapj}% change onecolumn to iop for fancy, iop to onecolumn for manuscript
%\documentclass[12pt,preprint]{aastex}

%\usepackage{lineno}
%\usepackage{blindtext}
%\linenumbers
%\usepackage{breqn}
\usepackage{amsmath}

\let\pwiflocal=\iffalse \let\pwifjournal=\iffalse
%From: http://arxiv.org/format/1512.00483
%\input{setup}
\input{mgs_setup}

\newcommand{\iancze}{{\sc C15}}

\providecommand{\eprint}[1]{\href{http://arxiv.org/abs/#1}{#1}}
\providecommand{\adsurl}[1]{\href{#1}{ADS}}
\newcommand{\name}{LkCa 4 }
\newcommand{\project}[1]{\textsl{#1}}
%\def\vsini{$v\sin{i_*}$}

\slugcomment{In preparation}

\shorttitle{Spots on Sub-sub-giants}

\shortauthors{TBD}

\bibliographystyle{yahapj}

\begin{document}

\title{Starspots on sub sub giants }

\author{TBD,\altaffilmark{1}, author list TBD}

\altaffiltext{1}{TBD}

\begin{abstract}

We measure the starspots on a sub sub giant.

\end{abstract}

\keywords{stars: fundamental parameters ---  stars: statistics}

\maketitle

\section{Introduction}\label{sec:intro}

We do not know what causes some sub-sub giants!

%Fill in more thereoy here
\citet{somers15} emphasized the roll of starspots in inferring stellar ages.

\section{Conclusions}

Reiteration here.

\clearpage
\pagebreak

\appendix

\section{Are starspots confusing?}
\label{methods-details}

Short answer: no!

\acknowledgements

%ADS
We thank ADS!

%Kepler
This paper includes data collected by the Kepler mission. Funding for the Kepler mission is provided by the NASA Science Mission directorate.

% MAST
Some/all of the data presented in this paper were obtained from the Mikulski Archive for Space Telescopes (MAST). STScI is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS5-26555.

{\it Facilities:} \facility{Smith (IGRINS)}, \facility{AAVSO}, \facility{INTEGRAL (OMC)}, \facility{ASAS}, \facility{Gaia}

{\it Software: }
 \project{pandas} \citep{mckinney10},
 \project{emcee} \citep{foreman13},
 \project{matplotlib} \citep{hunter07},
 \project{numpy} \citep{vanderwalt11},
 \project{scipy} \citep{jones01},
 \project{ipython} \citep{perez07},
 \project{gatspy} \citep{JakeVanderplas2015},
 \project{starfish} \citep{czekala15},
 \project{seaborn} \citep{waskom14}
%\software{%
% \project{pandas} \citep{mckinney10}
%    \project{emcee} \citep{foreman13},
% \project{matplotlib} \citep{hunter07},
% \project{numpy} \citep{vanderwalt11},
% \project{scipy} \citep{jones01},
% \project{ipython} \citep{perez07},
% \project{gatspy} \citep{JakeVanderplas2015},
% \project{starfish} \citep{czekala15}}.

\clearpage

\bibliographystyle{apj}
\bibliography{ms}

\end{document}

### 2018-10-16 document/ms.tex

@@
 
-\shorttitle{Spots on Sub-sub-giants}
+\shorttitle{Spots on Sub-subgiants}
 
@@
 We do not know what causes some sub-sub giants!
+But now we know a little... more. Hence this paper!
 
-%Fill in more thereoy here
+%Fill in more theory here
 \citet{somers15} emphasized the roll of starspots in inferring stellar ages.
+
+\begin{itemize}
+\item What is a sub-subgiant?
+  \begin{itemize}
+  \item What causes sub sub giant stars (Leiner et al. 2017)
+  \end{itemize}
+\item M67 S1063
+\begin{itemize}
+  \item Prototypical subsub (Geller et al. 2017)
+  \item Binary orbit, SB1
+\end{itemize}
+\item Starspots as confounding factors
+\begin{itemize}
+  \item Inhibit convective efficiency (redder and bigger)
+  \item Also confound observations: assign incorrect Teff
+  \item This paper aims to measure the starspot coverage and temp
+\end{itemize}
+\item Layout of this paper
+\end{itemize}
+
+\section{Observation and data reduction}
+\begin{itemize}
+\item IGRINS observations
+\item Ground-based photometric monitoring- ASASSN, AAVSO, ASAS
+\item K2 data (Campaign 5), *stretch goal* C16
+\item *stretch goal* APOGEE?
+\item Gaia data (membership confirmed)
+\end{itemize}
+
+\section{Analysis}
+\begin{itemize}
+\item Summary and assumptions of our methods
+\item K2 Superstamp(s)
+\begin{itemize}
+  \item K2 detrending
+  \item Interpreting lightcurves
+  \item Period and amplitude of lightcurve, with multi-term Lomb-Scargle + Fourier reconstruction
+\end{itemize}
+\item Phase folded archival V-band photometry (ASASSN+)
+\item IGRINS two-temperature spectral inference w/ Starfish
+\begin{itemize}
+  \item MCMC convergence and posterior predictive checks
+  \item FIGURE: IGRINS Spectra
+  \item Internal consistency of vsini, $v_z$
+  \item FIGURE: Violin plot
+\end{itemize}
+\item Analysis of near-IR flux contribution from binary companion
+\begin{itemize}
+  \item Limits on companion types
+\end{itemize}
+\end{itemize}
+
+\section{Results}
+\begin{itemize}
+\item We detect spots in spectra
+\begin{itemize}
+  \item S1063 has ~X\% coverage fraction of spots with Tspot ~ Y based on IGRINS + Starfish
+  \item *bonus* Revised effective temperature using both temperature components $[f_{\textrm{spot}} * T_{\textrm{spot}}^4 + (1 -f_{\textrm{spot}}) * T_{\textrm{ambient}}^4] = T_{\textrm{eff}}^4$
+  \item *bonus* Rsini
+\end{itemize}
+\item IGRINS observations occurred at maximum of lightcurve, so total spot coverage is even greater
+\item FIGURE: $T_{spot}$ versus $f_{spot}$ plot
+\item What coverage fraction would we have measured across the rotational phase?
+\end{itemize}
+
+\section{Discussion}
+\begin{itemize}
+\item Spot coverage is consistent with formation theories
+\item Conceivable geometries with circumpolar active longitudes, or migrating active latitudes
+\item Biases introduced if we assume a spot-free model
+\begin{itemize}
+  \item Where does subsub sit in a new HR diagram? (new Somers models)
+  \item *bonus* FIGURE: PMS HR diagram with new Somers tracks
+  \item Spot impact on SED fits
+\end{itemize}
+\end{itemize}
 

### 2018-10-30 document/ms.tex
Update paper with Tspot vs. filling factor figure

@@
 
+\usepackage{graphicx}
+\usepackage{subfigure}
 %\usepackage{lineno}
@@
 \item FIGURE: $T_{spot}$ versus $f_{spot}$ plot
+
+\begin{figure*}[h]
+  \centering
+  \begin{tabular}{ccc}
+    \subfloat{\includegraphics[width=2in]{figures/H_band_Tspot_fillingfactor_m119.pdf}} &
+    \subfloat{\includegraphics[width=2in]{figures/H_band_Tspot_fillingfactor_m118.pdf}} &
+    \subfloat{\includegraphics[width=2in]{figures/H_band_Tspot_fillingfactor_m116.pdf}} \\
+    \subfloat{\includegraphics[width=2in]{figures/H_band_Tspot_fillingfactor_m114.pdf}} &
+    \subfloat{\includegraphics[width=2in]{figures/H_band_Tspot_fillingfactor_m113.pdf}} &
+    \subfloat{\includegraphics[width=2in]{figures/H_band_Tspot_fillingfactor_m110.pdf}} \\
+    \subfloat{\includegraphics[width=2in]{figures/H_band_Tspot_fillingfactor_m109.pdf}} &
+    \subfloat{\includegraphics[width=2in]{figures/H_band_Tspot_fillingfactor_m107.pdf}} &
+    \subfloat{\includegraphics[width=2in]{figures/H_band_Tspot_fillingfactor_m106.pdf}}
+  \end{tabular}
+\caption{Tspot vs filling factor}
+\end{figure*}
+
 \item What coverage fraction would we have measured across the rotational phase?

### 2018-12-05 document/ms.tex
Co-writing session!
Co-authored-by: gully <igully@gmail.com>
Co-authored-by: nattieg <ngosnell@coloradocollege.edu>

--- 2018-10-16 document/ms.tex
@@
 \item Phase folded archival V-band photometry (ASASSN+)
-\item IGRINS two-temperature spectral inference w/ Starfish
-\begin{itemize}
-  \item MCMC convergence and posterior predictive checks
-  \item FIGURE: IGRINS Spectra
-  \item Internal consistency of vsini, $v_z$
-  \item FIGURE: Violin plot
-\end{itemize}
+\subsection{IGRINS two-temperature spectral inference w/ Starfish}
+
+We performed two-temperature probabilistic spectral decomposition on the IGRINS $H-$band spectrum.
+We applied the spectral inference framework \texttt{Starfish} \citep{czekala15}, recently extended to support composite spectra comprised of mixtures of two distinct photospheric components \citep{2017ApJ...836..200G}.
+Here, the two temperature components are labeled as $T_{\mathrm{spot}}$ and $T_{\mathrm{amb}}$ for the starspot and ambient photospheric emission respectively, with a filling factor $f$ defined as the ratio of collective projected surface area of the spot groups to the projected area of the star.
+
+We employed the \texttt{PHOENIX} precomputed synthetic model grid with grid ranges of $3000 < T_{\mathrm{eff}} \; (K) < 5300 $, $3 < \log{g \;(cm/s)}  < 4 $, and $ -0.5 <  [\mathrm{Fe}/\mathrm{H}] <0.5$.
+We trained the spectral emulator \citep{czekala15} on this grid range, while preserving the absolute model mean fluxes to enable accurate flux comparison between two photospheres of disparate characteristic temperatures.
+This new approach offers improved accuracy over the scalar flux interpolated approach introduced in Appendix XX of \citet{2017ApJ...836..200G}, especially for such a large dynamic range in effective temperature.
+The spectral emulator approach propagates the uncertainty attributable to the coarsely sampled \texttt{PHOENIX} models.
+
+The pre-defined grid ranges place uniform priors over their domain.
+Additionally, a threshold of 4500 K separated the allowed domains for the spot and ambient temperatures, yielding uniform priors $3000 < T_{\mathrm{spot}} \; (K) < 4500 $ and $4500 < T_{\mathrm{amb}} \; (K) < 5300$.
+
+\subsubsection{MCMC convergence and posterior predictive checks}
+Each IGRINS spectral order was fit independently, yielding over 20 individual sets of MCMC posteriors.
+We employed \texttt{emcee} \citep{foreman13} with 5000 samples and 40 walkers, spot-checking the MCMC chains for signatures of steady-state posterior probability distributions suggestive of convergence.
+Some orders did not pass our convergence criteria, usually due to poor initialization of nuissance parameters or overfitting.
+These specrtral orders were removed from future analysis, yielding a total of nine spectral orders, shown in Figure \ref{fig:IGRINS_spectra3x3}.
+
+\subsubsection{FIGURE: IGRINS Spectra}
+\begin{figure*}
+ \centering
+ \includegraphics[width=0.98\textwidth]{figures/H_band_spectra_3x3.pdf}
+ \caption{Nine $H-$band IGRINS spectral orders with probabilistic spectral decomposition.}
+ \label{fig:IGRINS_spectra3x3}
+\end{figure*}
+
+\subsubsection{Internal consistency of vsini, $v_z$}
+We additionally spot-checked the MCMC posteriors with posterior predictive checks... XX
+
 \item Analysis of near-IR flux contribution from binary companion
@@
 \section{Results}
+
+Using the \texttt{Starfish} spectral inference results we investigate the relationship between spot temperature and filling factor.
+In Figure XX we show 2-dimensional distributions of filling factor and spot temperature of the last 200 samples for the nine orders with accepted fits.
+Across the nine orders, the median filling factor value is 32\% with a standard deviation of 7\%, with a corresponding spot temperature of $4000 \pm 200$ K.
+The ambient photosphere temperature ssociated with this spot signature is $5200\pm25$ K.
+This is similar to the optical spectroscopic temperature determined by Mathieu+2003, which is expected as the optical spectrum will have less significant spot signatures than the IGRINS spectrum in the NIR.
+
+The presence of spots impacts the effective temperature of S1063. Taking into account both temperature components, we can calculate the effective temperature using
+\begin{equation}
+T_{\textrm{eff}}^4 = f_{\textrm{spot}} T_{\textrm{spot}}^4 + (1 -f_{\textrm{spot}}) T_{\textrm{ambient}}^4 .
+\end{equation}
+This results in an updated effective temperature of 4900 K.
+
+The IGRINS observation occurred at maximum light (LIGHT CURVE FIGURE), so this measurement of the spot filling factor is a lower limit on the total spot filling factor of S1063.
+We can estimate the filling factor at minimum light...
+
+This spot coverage fraction is similar to the range of spot coverage seen on RS CVn of 30--40\% from measuring TiO band strength (O'Neal+ 1996, 98, 04) and Doppler imaging (Hackman+12).
+The similar spot coverage fraction on S1063 is further evidence that this sub-subgiant and likely other sub-subgiants have high magnetic activity.
+
 \begin{itemize}
@@
 \begin{itemize}
-  \item S1063 has ~X\% coverage fraction of spots with Tspot ~ Y based on IGRINS + Starfish
-  \item *bonus* Revised effective temperature using both temperature components $[f_{\textrm{spot}} * T_{\textrm{spot}}^4 + (1 -f_{\textrm{spot}}) * T_{\textrm{ambient}}^4] = T_{\textrm{eff}}^4$
+  \item S1063 has $32 \pm 7$\% coverage fraction of spots with Tspot $4000\pm200$ K based on IGRINS + Starfish
+  \item Revised effective temperature using both temperature components $[f_{\textrm{spot}} * T_{\textrm{spot}}^4 + (1 -f_{\textrm{spot}}) * T_{\textrm{ambient}}^4] = T_{\textrm{eff}}^4$
+
   \item *bonus* Rsini
@@
 \item IGRINS observations occurred at maximum of lightcurve, so total spot coverage is even greater
+\item *bonus* total spot filling factor estimate given light curve magnitude
 \item FIGURE: $T_{spot}$ versus $f_{spot}$ plot
+
+% \begin{figure*}[h]
+%   \centering
+%   \begin{tabular}{c}
+%     \subfloat{\includegraphics[width=2in]{figures/H_band_Tspot_fillingfactor_m119.pdf}}
+%     \subfloat{\includegraphics[width=2in]{figures/H_band_Tspot_fillingfactor_m118.pdf}} &
+%     \subfloat{\includegraphics[width=2in]{figures/H_band_Tspot_fillingfactor_m116.pdf}} \\
+%     \subfloat{\includegraphics[width=2in]{figures/H_band_Tspot_fillingfactor_m114.pdf}} &
+%     \subfloat{\includegraphics[width=2in]{figures/H_band_Tspot_fillingfactor_m113.pdf}} &
+%     \subfloat{\includegraphics[width=2in]{figures/H_band_Tspot_fillingfactor_m110.pdf}} \\
+%     \subfloat{\includegraphics[width=2in]{figures/H_band_Tspot_fillingfactor_m109.pdf}} &
+%     \subfloat{\includegraphics[width=2in]{figures/H_band_Tspot_fillingfactor_m107.pdf}} &
+%     \subfloat{\includegraphics[width=2in]{figures/H_band_Tspot_fillingfactor_m106.pdf}}
+%   \end{tabular}
+% \caption{2-dimensional distributions of filling factor and spot temperature for the nine accepted IGRINS orders for S1063.
+The median filling factor across these nine orders is $32 \pm 7$\% with a spot temperature of $4000\pm200$ K.
+As the IGRINS spectrum was observed at maximum light, these show a lower limit on the total spot coverage fraction.
+}
+% \end{figure*}
+
 \item What coverage fraction would we have measured across the rotational phase?

### 2018-12-05 document/ms.tex
Fixed the latex compilation bug-- needed an obscure usepackage toggle; update outline with progress and content

@@
 \usepackage{graphicx}
-\usepackage{subfigure}
+\usepackage[caption=false]{subfig}
 %\usepackage{lineno}
@@
 
-% \begin{figure*}[h]
-%   \centering
-%   \begin{tabular}{c}
-%     \subfloat{\includegraphics[width=2in]{figures/H_band_Tspot_fillingfactor_m119.pdf}}
-%     \subfloat{\includegraphics[width=2in]{figures/H_band_Tspot_fillingfactor_m118.pdf}} &
-%     \subfloat{\includegraphics[width=2in]{figures/H_band_Tspot_fillingfactor_m116.pdf}} \\
-%     \subfloat{\includegraphics[width=2in]{figures/H_band_Tspot_fillingfactor_m114.pdf}} &
-%     \subfloat{\includegraphics[width=2in]{figures/H_band_Tspot_fillingfactor_m113.pdf}} &
-%     \subfloat{\includegraphics[width=2in]{figures/H_band_Tspot_fillingfactor_m110.pdf}} \\
-%     \subfloat{\includegraphics[width=2in]{figures/H_band_Tspot_fillingfactor_m109.pdf}} &
-%     \subfloat{\includegraphics[width=2in]{figures/H_band_Tspot_fillingfactor_m107.pdf}} &
-%     \subfloat{\includegraphics[width=2in]{figures/H_band_Tspot_fillingfactor_m106.pdf}}
-%   \end{tabular}
-% \caption{2-dimensional distributions of filling factor and spot temperature for the nine accepted IGRINS orders for S1063.
+ \begin{figure*}[h]
+   \centering
+   \begin{tabular}{ccc}
+     \subfloat{\includegraphics[width=2in]{figures/H_band_Tspot_fillingfactor_m119.pdf}} &
+     \subfloat{\includegraphics[width=2in]{figures/H_band_Tspot_fillingfactor_m118.pdf}} &
+     \subfloat{\includegraphics[width=2in]{figures/H_band_Tspot_fillingfactor_m116.pdf}} \\
+     \subfloat{\includegraphics[width=2in]{figures/H_band_Tspot_fillingfactor_m114.pdf}} &
+     \subfloat{\includegraphics[width=2in]{figures/H_band_Tspot_fillingfactor_m113.pdf}} &
+     \subfloat{\includegraphics[width=2in]{figures/H_band_Tspot_fillingfactor_m110.pdf}} \\
+     \subfloat{\includegraphics[width=2in]{figures/H_band_Tspot_fillingfactor_m109.pdf}} &
+     \subfloat{\includegraphics[width=2in]{figures/H_band_Tspot_fillingfactor_m107.pdf}} &
+     \subfloat{\includegraphics[width=2in]{figures/H_band_Tspot_fillingfactor_m106.pdf}}
+   \end{tabular}
+ \caption{2-dimensional distributions of filling factor and spot temperature for the nine accepted IGRINS orders for S1063.
 The median filling factor across these nine orders is $32 \pm 7$\% with a spot temperature of $4000\pm200$ K.
@@
 }
-% \end{figure*}
+ \end{figure*}
 

### 2018-12-05 document/ms.tex
Update intro text and add references

@@
 
+Sub-subgiant stars are stars that lie below the subgiant branch on a cluster optical color-magnitude diagram (CMD), but are too red to be main sequence stars.
+These stars are commonly found in evolved open clusters and globular clusters, with 65 sub-subgiants currently identified across 17 different clusters \citep{geller17}.
+The majority of sub-subgiant stars are single-lined spectroscopic binaries with short orbital periods of a few days with moderate X-ray luminosities of $10^{30}$ to $10^{31}$ erg s$^{-1}$ \citep[and references therein]{geller17}.
+
+The presence of sub-subgiants cannot be explained with typical single-star stellar evolutionary pathways.
+Three possible formation scenarios for sub-subgiants were put forth by \citet{leiner17}: mass transfer in a binary system, stripping of a subgiant star envelope through a dynamical encounter, and reduced luminosity as a result of inhibited convection due to the presence of strong magnetic fields.
+\citet{leiner17} conclude that strong magnetic fields due to binary interactions would produce the largest number of sub-subgiants.
+
+In this paper we focus on a single sub-subgiant system, S1063 in the open cluster M67.
+This system is a prototypical sub-subgiant star, with an single-lined spectroscopic orbital period of 18.4 days \citep{geller17}, an X-ray luminosity of $1.3\times10^{31}$ erg s$^{-1}$ \citep{vandenberg99}, and a variable light curve in \textit{K2} (REF LIGHT CURVE SECTION?).
+
 %Fill in more theory here
@@
 We performed two-temperature probabilistic spectral decomposition on the IGRINS $H-$band spectrum.
-We applied the spectral inference framework \texttt{Starfish} \citep{czekala15}, recently extended to support composite spectra comprised of mixtures of two distinct photospheric components \citep{2017ApJ...836..200G}.
+We applied the spectral inference framework \texttt{Starfish} \citep{czekala15}, recently extended to support composite spectra comprised of mixtures of two distinct photospheric components \citep{gullysantiago17}.
 Here, the two temperature components are labeled as $T_{\mathrm{spot}}$ and $T_{\mathrm{amb}}$ for the starspot and ambient photospheric emission respectively, with a filling factor $f$ defined as the ratio of collective projected surface area of the spot groups to the projected area of the star.
@@
 We trained the spectral emulator \citep{czekala15} on this grid range, while preserving the absolute model mean fluxes to enable accurate flux comparison between two photospheres of disparate characteristic temperatures.
-This new approach offers improved accuracy over the scalar flux interpolated approach introduced in Appendix XX of \citet{2017ApJ...836..200G}, especially for such a large dynamic range in effective temperature.
+This new approach offers improved accuracy over the scalar flux interpolated approach introduced in Appendix XX of \citet{gullysantiago17}, especially for such a large dynamic range in effective temperature.
 The spectral emulator approach propagates the uncertainty attributable to the coarsely sampled \texttt{PHOENIX} models.
@@
 The ambient photosphere temperature ssociated with this spot signature is $5200\pm25$ K.
-This is similar to the optical spectroscopic temperature determined by Mathieu+2003, which is expected as the optical spectrum will have less significant spot signatures than the IGRINS spectrum in the NIR.
+This is similar to the optical spectroscopic temperature determined by \citet{mathieu03}, which is expected as the optical spectrum will have less significant spot signatures than the IGRINS spectrum in the NIR.
 
@@
 
-The IGRINS observation occurred at maximum light (LIGHT CURVE FIGURE), so this measurement of the spot filling factor is a lower limit on the total spot filling factor of S1063.
+The IGRINS observation occurred at maximum light (REF LIGHT CURVE FIGURE), so this measurement of the spot filling factor is a lower limit on the total spot filling factor of S1063.
 We can estimate the filling factor at minimum light...
 
-This spot coverage fraction is similar to the range of spot coverage seen on RS CVn of 30--40\% from measuring TiO band strength (O'Neal+ 1996, 98, 04) and Doppler imaging (Hackman+12).
+This spot coverage fraction is similar to the range of spot coverage seen on RS CVn of 30--40\% from measuring TiO band strength \citep{oneal96, oneal98, oneal04} and Doppler imaging \citep{hackman12}.
 The similar spot coverage fraction on S1063 is further evidence that this sub-subgiant and likely other sub-subgiants have high magnetic activity.

### 2018-12-17 document/ms.tex
Co-writing session

@@
 This system is a prototypical sub-subgiant star, with an single-lined spectroscopic orbital period of 18.4 days \citep{geller17}, an X-ray luminosity of $1.3\times10^{31}$ erg s$^{-1}$ \citep{vandenberg99}, and a variable light curve in \textit{K2} (REF LIGHT CURVE SECTION?).
+
+\subsection{Starspots as confounding factors}
+Mass, age, and metallicity uniquely map a main sequence star to its HR diagram position.
+A fourth factor---rotation---confounds this mapping in as-yet-unknown ways.
+Rotation might enhance spread in HR diagram positions (cite XX Davenport, Douglas?), with the most conspicuous spreads in the pre-main sequence regime (cite XX Covey, Stauffer).
+Spreads in the HR diagram offer clues to the consequences of rotation.
+Increased rotation heightens the magnetic dynamo strength and concommitant surface magnetic field.
+These magnetic fields suppress convective efficiency, meaning the star must increase in size at a lower effective temperature to allow the same amount of internal energy to escape (cite XX Feiden): rotating stars become bigger and cooler than their non-rotating counterparts (cite XX Somers).
+The interplay of rotation, dynamo, and surface fields remain an active area of research, with bright prospects for a unified theory involving the degree of magnetic complexity parameter (cite XX Garraffo).
+
+Surface magnetic fields offer two key observational manifestations.
+The Zeeman Effect splits spectral line levels in magnetic-sensitive atomic transitions (cite XX Johns-Krull).
+Starspots induce stellar surface inhomogeneities that can be seen in the modulation of
+
+The story in the post-main sequence is less clear.  Angular momentum transport governs rotation  as stars evolve over orders of magnitude in size.
 
@@
 Using the \texttt{Starfish} spectral inference results we investigate the relationship between spot temperature and filling factor.
-In Figure XX we show 2-dimensional distributions of filling factor and spot temperature of the last 200 samples for the nine orders with accepted fits.
-Across the nine orders, the median filling factor value is 32\% with a standard deviation of 7\%, with a corresponding spot temperature of $4000 \pm 200$ K.
-The ambient photosphere temperature ssociated with this spot signature is $5200\pm25$ K.
-This is similar to the optical spectroscopic temperature determined by \citet{mathieu03}, which is expected as the optical spectrum will have less significant spot signatures than the IGRINS spectrum in the NIR.
+In Figure~\ref{fig:tspot_fillingfactor3x3} we show 2-dimensional distributions of filling factor and spot temperature of the last 200 samples for the nine orders with accepted fits.
+Similar trends between spot temperature and filling factor appear across most of the orders.
+Across all nine orders, the median filling factor value is 32\% with a standard deviation of 7\%, with a corresponding spot temperature of $4000 \pm 200$ K.
+The ambient photosphere temperature associated with this spot signature is $5200\pm25$ K.
+This is similar to the optical spectroscopic temperature of 5000 K determined by \citet{mathieu03}, which is expected as the optical spectrum will have less significant spot signatures than the IGRINS spectrum in the NIR.
 
-The presence of spots impacts the effective temperature of S1063. Taking into account both temperature components, we can calculate the effective temperature using
+The presence of spots impacts the effective temperature of S1063. Taking into account both temperature components, we calculate the effective temperature using
 \begin{equation}
@@
 \end{equation}
-This results in an updated effective temperature of 4900 K.
+This results in an updated effective temperature for S1063 of $4900\pm125$ K.
 
-The IGRINS observation occurred at maximum light (REF LIGHT CURVE FIGURE), so this measurement of the spot filling factor is a lower limit on the total spot filling factor of S1063.
-We can estimate the filling factor at minimum light...
-
-This spot coverage fraction is similar to the range of spot coverage seen on RS CVn of 30--40\% from measuring TiO band strength \citep{oneal96, oneal98, oneal04} and Doppler imaging \citep{hackman12}.
-The similar spot coverage fraction on S1063 is further evidence that this sub-subgiant and likely other sub-subgiants have high magnetic activity.
+Over the course of \textit{K2} C5, the IGRINS spectrum was observed at approximately 97\% of maximum light (REF LIGHT CURVE FIGURE).
+From a first-order interpretation of light curve amplitudes, minimum light corresponds to the largest star spot coverage while maximum light corresponds to the least star spot coverage, although these assumptions are complicated by the possibility of spot evolution \citep{basri18}.
+At the time of observation, these spectral inference results suggest that the lower limit on the total star spot coverage of S1063 is approximately 32\%.
+We note that, in this case, the light curve maximum is not consistent with zero spot coverage.
+As seen in Figure LIGHT CURVE, during \textit{K2} C5 the absolute light curve minimum (occuring at HJD **some date here**) was approximately 5\% lower than the flux at the time of observation.
+This suggests that the maximum spot filling factor during the time of C5 was closer to 40\%.
 
@@
 The median filling factor across these nine orders is $32 \pm 7$\% with a spot temperature of $4000\pm200$ K.
-As the IGRINS spectrum was observed at maximum light, these show a lower limit on the total spot coverage fraction.
+As the IGRINS spectrum was observed near maximum light, these show a lower limit on the total spot coverage fraction.
 }
+ \label{fig:tspot_fillingfactor3x3}
  \end{figure*}
@@
 \section{Discussion}
+
+The spot coverage fraction measured here is consistent with the range of spot coverage seen on RS CVn of 30--40\% from measuring TiO band strength \citep{oneal96, oneal98, oneal04} and Doppler imaging \citep{hackman12}.
+The similar spot coverage fraction on S1063 is further evidence that this sub-subgiant and likely other sub-subgiants have high magnetic activity.
+
+In the absence of this spectral inference technique one could assume the \textit{K2} C5 light curve maximum corresponded to zero spot presence with the light curve amplitude change implying a maximum spot coverage of 7--10\%.
+This provides a fundamentally different view of the star ...
+
 \begin{itemize}

### 2019-03-25 document/ms.tex
Coauthored commit by me and @nattieg working on prose for the paper!

@@
 \section{Observation and data reduction}
-\begin{itemize}
-\item IGRINS observations
-\item Ground-based photometric monitoring- ASASSN, AAVSO, ASAS
-\item K2 data (Campaign 5), *stretch goal* C16
-\item *stretch goal* APOGEE?
-\item Gaia data (membership confirmed)
-\end{itemize}
+\subsection{IGRINS observations}
+A high resolution spectrum of S1063 was acquired with the $R=45,000$ Immersion Grating Infrared Spectrograph \citep[IGRINS;][]{park14} at UT 2015-04-26 $03^h29^m$ at the $2.7\;$m Harlan J.
+Smith Telescope at McDonald Observatory.
+Eight 600-second individual exposures were acquired in an ABBA nod pattern at an airmass of 1.2.
+The sky emission lines and telluric lines were removed with the IGRINS Pipeline Package  \citep[PLP;][]{jaejoonlee16} and a reference A0V star acquired nearby in time and airmass.
+The $H-$band spectra exhibited signal-to-noise ratio $S/N\sim30-80$ per pixel (check XX).
+The $K-$band spectra possessed low $S/N$ and were excluded from further analysis.
+
+\subsection{K2 superstamp lightcurves}
+K2 data Campaigns 5, 16, 18 Superstamps and detrending
+\subsection{Ground-based photometric monitoring}
+ASASSN, AAVSO, ASAS
+\subsection{Gaia data}
+M67 membership confirmed
 
@@
 \item Summary and assumptions of our methods
-\item K2 Superstamp(s)
+\item K2 data
 \begin{itemize}
-  \item K2 detrending
+  \item Zero points with FFIs or super stamps
   \item Interpreting lightcurves
@@
 
-The presence of spots impacts the effective temperature of S1063. Taking into account both temperature components, we calculate the effective temperature using
+From the 4-year light curve of S1063 (REF LIGHT CURVE FIGURE) we determine that the IGRINS spectrum was observed at a local maximum in the stellar variability, but this flux was approximately 7\% below the global maximum over the four year period covered by ASAS-SN and \textit{K2}.
+From a first-order interpretation of light curve amplitudes, minimum light corresponds to the largest star spot coverage while maximum light corresponds to the least star spot coverage, although these assumptions are complicated by the possibility of spot evolution \citep{basri18}.
+Assuming non-emitting spots, the stellar surface must be at least 7\% covered at the time of the IGRINS observation to account for the overall suppression in the maximum flux.
+If we adopt an ambient photosphere temperature of 5200 K and a spot temperature of 4000 K, the spot coverage would have to be 10\% to account for the flux suppression.
+At the time of observation, these spectral inference results show that the spot coverage was actually 32\%.
+This suggests that at the 4-year light curve maximum of S1063, the spot coverage was still around 20\% and definitely not an unspotted star.
+As seen in Figure LIGHT CURVE, the absolute light curve minimum (occuring at HJD **SOME DATE HERE**) was approximately 13\% lower than the flux at the time of observation.
+We conclude that the maximum spot filling factor at that time was closer to 50\%.
+
+The time average spot coverage fraction is AMOUNT over the four years, and with that we can calculate the time averaged effective temperature...
+
+(UPDATE THIS WITH TIME AVERAGED SPOT NUMBERS) The presence of spots impacts the effective temperature of S1063.
+Taking into account both temperature components, we calculate the effective temperature using
 \begin{equation}
@@
 
-Over the course of \textit{K2} C5, the IGRINS spectrum was observed at approximately 97\% of maximum light (REF LIGHT CURVE FIGURE).
-From a first-order interpretation of light curve amplitudes, minimum light corresponds to the largest star spot coverage while maximum light corresponds to the least star spot coverage, although these assumptions are complicated by the possibility of spot evolution \citep{basri18}.
-At the time of observation, these spectral inference results suggest that the lower limit on the total star spot coverage of S1063 is approximately 32\%.
-We note that, in this case, the light curve maximum is not consistent with zero spot coverage.
-As seen in Figure LIGHT CURVE, during \textit{K2} C5 the absolute light curve minimum (occuring at HJD **some date here**) was approximately 5\% lower than the flux at the time of observation.
-This suggests that the maximum spot filling factor during the time of C5 was closer to 40\%.
-
 \begin{itemize}
-\item We detect spots in spectra
+\item We MEASURE spots in spectra
 \begin{itemize}
@@
 
+%IGRINS
+This work used the Immersion Grating Infrared Spectrometer(IGRINS) that was developed under a collaboration between the University of Texas at Austin and the Korea Astronomy and Space Science Institute (KASI) with the financial support of the US National Science Foundation under grant AST-1229522, of the University of Texas at Austin, and of the Korean GMT Project of KASI.
+
 %Kepler

### 2019-03-25 document/ms.tex
Add pro-forma text about the observations

@@
 The sky emission lines and telluric lines were removed with the IGRINS Pipeline Package  \citep[PLP;][]{jaejoonlee16} and a reference A0V star acquired nearby in time and airmass.
-The $H-$band spectra exhibited signal-to-noise ratio $S/N\sim30-80$ per pixel (check XX).
+The $H-$band spectra exhibited signal-to-noise ratio $S/N\sim30-80$ per pixel (\textbf{verify XX}).
 The $K-$band spectra possessed low $S/N$ and were excluded from further analysis.
@@
 \subsection{K2 superstamp lightcurves}
-K2 data Campaigns 5, 16, 18 Superstamps and detrending
+The \emph{Kepler} spacecraft targeted S0163 (EPIC 211414597) during the \emph{K2} mission \citep{howell14} in Campaigns 5, 16, 18 as part of the M67 superstamps.
+The instrumental point spread function (PSF) of S1063 fell entirely within the oversized K2 target pixel files in Campaign 5 (K2 Custom Aperture ID 200008674) and Campaign 18 (K2 Custom Aperture ID 200233338).
+Aperture photometry was conducted with interactively-assigned custom apertures using the \texttt{lightkurve .interact()} feature \citep{geert_barentsen_2019_2565212}.
+The apertures were chosen to minimize flux-loss out of the aperture due to spacecraft-induced image motion, while avoiding low-$S/N$ pixels and the wings of adjacent PSFs.
+The Campaign 16 source PSF overlapped the border of two custom apertures (\textbf{numbers XX and XX}), which were stitched together before conducting aperture photometry.
+We detrended motion-induced image artifacts with the Self Flat Field algorithm \citep{vanderburg14} implemented in \texttt{lightkurve}.  Postage stamp images are shown in Figure \textbf{ref XX}.
+
+\begin{figure*}[htb!]
+  \centering
+  \begin{tabular}{ccccc}
+    \subfloat{\includegraphics[width=1in]{figures/S1063_60x60arcsec_PS1_g.png}} &
+    \subfloat{\includegraphics[width=1in]{figures/S1063_60x60arcsec_2M_J.png}} &
+    \subfloat{\includegraphics[width=1in]{figures/S1063_60x60arcsec_K2_C5.png}} &
+    \subfloat{\includegraphics[width=1in]{figures/S1063_60x60arcsec_K2_C16.png}} &
+    \subfloat{\includegraphics[width=1in]{figures/S1063_60x60arcsec_K2_C18.png}} \\
+  \end{tabular}
+\caption{Imaging of S1063 in $60'' \times 60''$ postage stamps. \emph{left-to-right:} Pan-STARRS $g$-band co-added image contemporaneous with C16; 2MASS $J-$band; K2 Campaigns 5, 16, 18.}
+\label{fig:imaging}
+\end{figure*}
+
 \subsection{Ground-based photometric monitoring}
-ASASSN, AAVSO, ASAS
+The retrieved $V-$ band photometry from the All-Sky Automated Survey for Supernovae \citep[ASAS-SN][]{shappee14} using the ``Precomputed Light Curve'' provided in the Variable Stars Database (source ASASSN-V J085113.44+115139.7) and $g-$band photometry from the Sky Portal \citep{2017PASP..129j4502K}.
+The $\sim8''$ pixels may cause some PSF blending of the nearby-albeit-fainter source seen at the bottom of Figure \ref{fig:imaging}.
+
 \subsection{Gaia data}

### 2019-03-26 document/ms.tex
The observations sections have content filled in

@@
 
-\subsection{K2 superstamp lightcurves}
-The \emph{Kepler} spacecraft targeted S0163 (EPIC 211414597) during the \emph{K2} mission \citep{howell14} in Campaigns 5, 16, 18 as part of the M67 superstamps.
-The instrumental point spread function (PSF) of S1063 fell entirely within the oversized K2 target pixel files in Campaign 5 (K2 Custom Aperture ID 200008674) and Campaign 18 (K2 Custom Aperture ID 200233338).
-Aperture photometry was conducted with interactively-assigned custom apertures using the \texttt{lightkurve .interact()} feature \citep{geert_barentsen_2019_2565212}.
-The apertures were chosen to minimize flux-loss out of the aperture due to spacecraft-induced image motion, while avoiding low-$S/N$ pixels and the wings of adjacent PSFs.
-The Campaign 16 source PSF overlapped the border of two custom apertures (\textbf{numbers XX and XX}), which were stitched together before conducting aperture photometry.
-We detrended motion-induced image artifacts with the Self Flat Field algorithm \citep{vanderburg14} implemented in \texttt{lightkurve}.  Postage stamp images are shown in Figure \textbf{ref XX}.
-
-\begin{figure*}[htb!]
+\begin{figure*}[hbt!]
   \centering
@@
 
+\subsection{K2 superstamp lightcurves}
+The \emph{Kepler} spacecraft targeted S0163 (EPIC 211414597) during the \emph{K2} mission \citep{howell14} in Campaigns 5, 16, 18 as part of the M67 superstamps.
+The instrumental point spread function (PSF) of S1063 fell entirely within the oversized K2 target pixel files in Campaign 5 (K2 Custom Aperture ID 200008674) and Campaign 18 (K2 Custom Aperture ID 200233338).
+Aperture photometry was conducted with interactively-assigned custom apertures using the \texttt{lightkurve .interact()} feature \citep{geert_barentsen_2019_2565212}.
+The apertures were chosen to minimize flux-loss out of the aperture due to spacecraft-induced image motion, while avoiding low-$S/N$ pixels and the wings of adjacent PSFs.
+The Campaign 16 source PSF overlapped the edge of Custom Aperture ID 200200534; a mosaic of adjacent superstamps was assembled before conducting aperture photometry.
+We detrended motion-induced image artifacts with the Self Flat Field algorithm \citep{vanderburg14} implemented in \texttt{lightkurve}.  Postage stamp images are shown in Figure \ref{fig:imaging}.
+
 \subsection{Ground-based photometric monitoring}
-The retrieved $V-$ band photometry from the All-Sky Automated Survey for Supernovae \citep[ASAS-SN][]{shappee14} using the ``Precomputed Light Curve'' provided in the Variable Stars Database (source ASASSN-V J085113.44+115139.7) and $g-$band photometry from the Sky Portal \citep{2017PASP..129j4502K}.
-The $\sim8''$ pixels may cause some PSF blending of the nearby-albeit-fainter source seen at the bottom of Figure \ref{fig:imaging}.
+We retrieved All-Sky Automated Survey for Supernovae \citep[ASAS-SN][]{shappee14} lightcurves from the Sky Portal \citep{2017PASP..129j4502K}.
+The lightcurves contained 758 epochs of $V-$ band photometry spanning 2013-2018 (source ASASSN-V J085113.44+115139.7) and 823 epochs of $g-$band photometry spanning mid-2017$-$2018.
+The $\sim8''$ ASAS-SN pixels may cause some PSF blending of the nearby-albeit-fainter source seen at the bottom of Figure \ref{fig:imaging}.
+The pixel images were not available to evaluate the extent of blending.
+%% Option: Pan-STARRS
 
 \subsection{Gaia data}
-M67 membership confirmed
+\emph{Gaia} DR2 astrometry \citep{2016A&A...595A...1G, 2018A&A...616A...1G} indicates a parallax ($1.17\pm0.025 \;$mas) and proper motion for S1063 (\emph{Gaia} DR2 604921030968952832) consistent with other M67 members, and approaching 100\% membership probability \citep{2018ApJ...869....9G}.
 
@@
 
+%gaia
+This work has made use of data from the European Space Agency (ESA) mission
+{\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed by the {\it Gaia}
+Data Processing and Analysis Consortium (DPAC,
+\url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding for the DPAC
+has been provided by national institutions, in particular the institutions
+participating in the {\it Gaia} Multilateral Agreement.
+
 {\it Facilities:} \facility{Smith (IGRINS)}, \facility{AAVSO}, \facility{INTEGRAL (OMC)}, \facility{ASAS}, \facility{Gaia}

### 2019-12-04 document/ms.tex
Remove placeholder text
Add prose describing the K2 FFI zero-point calibration.

@@
 \section{Introduction}\label{sec:intro}
-
-We do not know what causes some sub-sub giants!
-But now we know a little... more. Hence this paper!
 
@@
   \end{tabular}
-\caption{Imaging of S1063 in $60'' \times 60''$ postage stamps. \emph{left-to-right:} Pan-STARRS $g$-band co-added image contemporaneous with C16; 2MASS $J-$band; K2 Campaigns 5, 16, 18.}
+\caption{Imaging of S1063 in $60'' \times 60''$ postage stamps.
+\emph{left-to-right:} Pan-STARRS $g$-band co-added image contemporaneous with C16; 2MASS $J-$band; K2 Campaigns 5, 16, 18 from Full Frame Images.
+S1063 is sufficiently separated from nearby sources in the coarse \emph{Kepler} imaging.}
 \label{fig:imaging}
@@
 We detrended motion-induced image artifacts with the Self Flat Field algorithm \citep{vanderburg14} implemented in \texttt{lightkurve}.  Postage stamp images are shown in Figure \ref{fig:imaging}.
+
+\subsection{Inter-campaign relative photometry with K2 Full Frame Images}
+
+Stellar activity cycles on S1063 can secularly change the stellar brightness on timescales comparable to the separation of the three campaigns of \emph{K2} observations.
+The comparison of flux levels among repeated \emph{K2} campaigns requires accounting for detector responsivity degradation on these same timescales.
+The absolute sensitivity of the \emph{Kepler} detector pixels decay at $XX \%\;yr^{-1}$ due to sudden pixel sensitivity dropouts and other environmental lifetime factors (CITE Caldwell,Montet).
+We calibrated the system-integrated throughput for \emph{Kepler} detector channels possessing the M67 field in campaigns 5, 16, and 18.
+We measured aperture photometry for about two thousand isolated reference stars using the Full Frame Images (FFIs), keeping only reference stars that had repeated observations in all three campaigns.
+Campaign 16 reference stars had a median flux of $93.9\pm4.2\%$ relative to campaign 5; campaign 18 showed $98.2\pm2.8\%$ relative to campaign 5.
+These flux ratios dictate the vertical registration of the \emph{K2} lightcurves in Figure XX.
 

### 2020-10-16 document/ms.tex
Tick off a task on the writing todo list
Slight intro text changes

@@
 
-We measure the starspots on a sub sub giant.
+We measure the starspots on a sub-subgiant.
 
@@
 \section{Introduction}\label{sec:intro}
+Recent studies illuminate the important role stellar magnetic activity plays in stellar structure.
+This impact of stellar activity and magnetic fields is seen throughout the Herzsprung-Russell Diagram.
+For example, by biasing isochronal ages of young clusters \citep{somers15}, inflating radii of active M-dwarfs (Torres2010, Morales2010, Jackson2019), causing redder multiple turnoffs in stellar clusters [Bastian2009, Sun2019], and altering the pulsation modes of red giants [Gaulme2020].
+As our ability to probe the detailed physics of stellar evolution continues to improve we must grapple with the complexities of stellar structure diverging from simpler theoretical expectations due to magnetic activity, which requires careful observational studies of magnetically active systems to test magnetic stellar models.
 
+One example of the impact of magnetic activity is seen in sub-subgiant (SSG) stars, defined to be stars that lie below the subgiant branch on a cluster optical color-magnitude diagram (CMD), but are too red to be main sequence stars.
 Sub-subgiant stars are stars that lie below the subgiant branch on a cluster optical color-magnitude diagram (CMD), but are too red to be main sequence stars.
@@
 \item Phase folded archival V-band photometry (ASASSN+)
+
 \subsection{IGRINS two-temperature spectral inference w/ Starfish}

### 2020-12-16 document/ms.tex

@@
 \providecommand{\adsurl}[1]{\href{#1}{ADS}}
-\newcommand{\name}{LkCa 4 }
 \newcommand{\project}[1]{\textsl{#1}}
-%\def\vsini{$v\sin{i_*}$}
 
@@
 Recent studies illuminate the important role stellar magnetic activity plays in stellar structure.
-This impact of stellar activity and magnetic fields is seen throughout the Herzsprung-Russell Diagram.
-For example, by biasing isochronal ages of young clusters \citep{somers15}, inflating radii of active M-dwarfs (Torres2010, Morales2010, Jackson2019), causing redder multiple turnoffs in stellar clusters [Bastian2009, Sun2019], and altering the pulsation modes of red giants [Gaulme2020].
+This impact of stellar activity and magnetic fields is seen throughout the Hertzsprung-Russell (HR) Diagram.
+For example, by biasing isochronal ages of young clusters \citep{somers15}, inflating radii of active M-dwarfs \citep{2010AJ....140.1158T,2010ApJ...718..502M,2019MNRAS.483.1125J}, causing redder multiple turnoffs in stellar clusters \citep{2009MNRAS.398L..11B,2019ApJ...876..113S}, and altering the pulsation modes of red giants \citep{2020A&A...639A..63G}.
 As our ability to probe the detailed physics of stellar evolution continues to improve we must grapple with the complexities of stellar structure diverging from simpler theoretical expectations due to magnetic activity, which requires careful observational studies of magnetically active systems to test magnetic stellar models.
@@
 One example of the impact of magnetic activity is seen in sub-subgiant (SSG) stars, defined to be stars that lie below the subgiant branch on a cluster optical color-magnitude diagram (CMD), but are too red to be main sequence stars.
-Sub-subgiant stars are stars that lie below the subgiant branch on a cluster optical color-magnitude diagram (CMD), but are too red to be main sequence stars.
 These stars are commonly found in evolved open clusters and globular clusters, with 65 sub-subgiants currently identified across 17 different clusters \citep{geller17}.
@@
 
-The presence of sub-subgiants cannot be explained with typical single-star stellar evolutionary pathways.
-Three possible formation scenarios for sub-subgiants were put forth by \citet{leiner17}: mass transfer in a binary system, stripping of a subgiant star envelope through a dynamical encounter, and reduced luminosity as a result of inhibited convection due to the presence of strong magnetic fields.
-\citet{leiner17} conclude that strong magnetic fields due to binary interactions would produce the largest number of sub-subgiants.
+The existence of sub-subgiants cannot be explained with typical single-star stellar evolutionary pathways.
+Three possible formation scenarios for sub-subgiants were put forth by \citet{leiner17}: mass transfer in a binary system, stripping of a subgiant star envelope through a dynamical encounter, and reduced luminosity as a result of inhibited convection and large starspot covering fractions due to the presence of strong magnetic fields.
+\citet{leiner17} conclude that the majority of sub-subgiants are likely the result of strong magnetic fields.
+This is supported by the presence of H-alpha and X-ray emission and optical variability seen across the known sub-subgiant population \citep{geller17}, all observational signatures of magnetic activity and the presence of starspots.
+
+The portion of the stellar surface covered with starspots is an important observational proxy for magnetic activity.
+Monochromatic light curves are often used to identify spotted stars \citep{2014ApJS..211...24M} but can only provide a limit on the differential spot coverage: a vast null space of longitudinally symmetric starspot geometries evade detection in monochromatic lightcurves alone \citep{2019AJ....157...64L}.
+Measuring the overall spot coverage typically requires Doppler imaging or interferometry studies restricted to only the brightest and most nearby sources \citep{roettenbacher16}, or relying on inferred covering fractions from TiO band observations \citep{oneal96,fang2016,2019AJ....158..101M}.
+Testing the next era of stellar activity models requires new analysis methodologies to measure spot-covering fractions of a larger number of targets, including sub-subgiants.
+
+Starspots emit a spectrum of their own at a lower temperature and with distinct absorption features compared to the ambient photosphere.
+The observed spectrum is a composite of the spot and photosphere spectra and can therefore be deconvolved.
+This deconvolution constrains the spot-covering fraction as well as the spot and photosphere temperatures.
+This is possible by performing a two-temperature probabilistic spectral decomposition using the spectral inference framework \texttt{Starfish} \citep{czekala15}, recently extended to support composite spectra \citep{gullysantiago17}.
+The resulting spot characterization can be used to anchor light curve information, providing insight into the overall stellar activity level and constraining the long-term spot coverage \citep{neff95}.
+This strategy only requires high-resolution echelle spectroscopy and photometric monitoring, dramatically increasing the number of sources for which we can observationally constrain spot-covering fractions.
 
 In this paper we focus on a single sub-subgiant system, S1063 in the open cluster M67.
-This system is a prototypical sub-subgiant star, with an single-lined spectroscopic orbital period of 18.4 days \citep{geller17}, an X-ray luminosity of $1.3\times10^{31}$ erg s$^{-1}$ \citep{vandenberg99}, and a variable light curve in \textit{K2} (REF LIGHT CURVE SECTION?).
-
-\subsection{Starspots as confounding factors}
-Mass, age, and metallicity uniquely map a main sequence star to its HR diagram position.
-A fourth factor---rotation---confounds this mapping in as-yet-unknown ways.
-Rotation might enhance spread in HR diagram positions (cite XX Davenport, Douglas?), with the most conspicuous spreads in the pre-main sequence regime (cite XX Covey, Stauffer).
-Spreads in the HR diagram offer clues to the consequences of rotation.
-Increased rotation heightens the magnetic dynamo strength and concommitant surface magnetic field.
-These magnetic fields suppress convective efficiency, meaning the star must increase in size at a lower effective temperature to allow the same amount of internal energy to escape (cite XX Feiden): rotating stars become bigger and cooler than their non-rotating counterparts (cite XX Somers).
-The interplay of rotation, dynamo, and surface fields remain an active area of research, with bright prospects for a unified theory involving the degree of magnetic complexity parameter (cite XX Garraffo).
-
-Surface magnetic fields offer two key observational manifestations.
-The Zeeman Effect splits spectral line levels in magnetic-sensitive atomic transitions (cite XX Johns-Krull).
-Starspots induce stellar surface inhomogeneities that can be seen in the modulation of
-
-The story in the post-main sequence is less clear.  Angular momentum transport governs rotation  as stars evolve over orders of magnitude in size.
-
-%Fill in more theory here
-\citet{somers15} emphasized the roll of starspots in inferring stellar ages.
-
-\begin{itemize}
-\item What is a sub-subgiant?
-  \begin{itemize}
-  \item What causes sub sub giant stars (Leiner et al. 2017)
-  \end{itemize}
-\item M67 S1063
-\begin{itemize}
-  \item Prototypical subsub (Geller et al. 2017)
-  \item Binary orbit, SB1
-\end{itemize}
-\item Starspots as confounding factors
-\begin{itemize}
-  \item Inhibit convective efficiency (redder and bigger)
-  \item Also confound observations: assign incorrect Teff
-  \item This paper aims to measure the starspot coverage and temp
-\end{itemize}
-\item Layout of this paper
-\end{itemize}
+This system is a prototypical sub-subgiant star, with an single-lined spectroscopic orbital period of 18.4 days \citep{geller17}, an X-ray luminosity of $1.3\times10^{31}$ erg s$^{-1}$ \citep{vandenberg99}, and a variable light curve in \textit{K2} and ASAS-SN (Section \ref{K2lightcurve}).
 
@@
 The sky emission lines and telluric lines were removed with the IGRINS Pipeline Package  \citep[PLP;][]{jaejoonlee16} and a reference A0V star acquired nearby in time and airmass.
-The $H-$band spectra exhibited signal-to-noise ratio $S/N\sim30-80$ per pixel (\textbf{verify XX}).
+The $H-$band spectra exhibited signal-to-noise ratio $S/N\sim50$ per pixel.
 The $K-$band spectra possessed low $S/N$ and were excluded from further analysis.
@@
 The \emph{Kepler} spacecraft targeted S0163 (EPIC 211414597) during the \emph{K2} mission \citep{howell14} in Campaigns 5, 16, 18 as part of the M67 superstamps.
-The instrumental point spread function (PSF) of S1063 fell entirely within the oversized K2 target pixel files in Campaign 5 (K2 Custom Aperture ID 200008674) and Campaign 18 (K2 Custom Aperture ID 200233338).
-Aperture photometry was conducted with interactively-assigned custom apertures using the \texttt{lightkurve .interact()} feature \citep{geert_barentsen_2019_2565212}.
+The instrumental point spread function (PSF) of S1063 fell entirely within the oversized K2 target pixel files in Campaign 5 (K2 Custom Aperture ID 200008674, channel 13) and Campaign 18 (K2 Custom Aperture ID 200233338).
+Aperture photometry was conducted with interactively-assigned custom apertures using the \texttt{lightkurve.interact()} feature \citep{geert_barentsen_2019_2565212}.
 The apertures were chosen to minimize flux-loss out of the aperture due to spacecraft-induced image motion, while avoiding low-$S/N$ pixels and the wings of adjacent PSFs.
@@
 
-\subsection{Inter-campaign relative photometry with K2 Full Frame Images}
+\subsection{Inter-campaign relative photometry with K2 Full Frame Images}\label{K2lightcurve}
 
@@
 The comparison of flux levels among repeated \emph{K2} campaigns requires accounting for detector responsivity degradation on these same timescales.
-The absolute sensitivity of the \emph{Kepler} detector pixels decay at $XX \%\;yr^{-1}$ due to sudden pixel sensitivity dropouts and other environmental lifetime factors (CITE Caldwell,Montet).
-We calibrated the system-integrated throughput for \emph{Kepler} detector channels possessing the M67 field in campaigns 5, 16, and 18.
-We measured aperture photometry for about two thousand isolated reference stars using the Full Frame Images (FFIs), keeping only reference stars that had repeated observations in all three campaigns.
-Campaign 16 reference stars had a median flux of $93.9\pm4.2\%$ relative to campaign 5; campaign 18 showed $98.2\pm2.8\%$ relative to campaign 5.
-These flux ratios dictate the vertical registration of the \emph{K2} lightcurves in Figure XX.
+The absolute sensitivity of the \emph{Kepler} detector pixels decay at $\sim1 \%\;\textrm{yr}^{-1}$ due to sudden pixel sensitivity dropouts and other environmental lifetime factors \citep{montet17}.
+
+To account for sensitivity changes, we calibrate the system-integrated throughput for \emph{Kepler} detector channels including the M67 field for Campaigns 5, 16, and 18.
+We measure aperture photometry for approximately 2000 isolated reference stars from the Full Frame Images, keeping only those stars that were observed in all three campaigns.
+Compared to Campaign 5, the reference stars have a median flux of $93.9\pm4.2\%$ in Campaign 16 and a median flux of $98.2\pm2.8\%$ in Campaign 18.
+Campaigns 5 and 18 were observed on the same detector channel while a different detector channel was used for Campaign 16, therefore these offsets are not a significant measure of detector degradation across campaigns.
+
+Given the full contemporaneous coverage between ground-based ASAS-SN data with Campaign 16, we set the overall vertical registration of the \emph{K2} lightcurves such that the ASAS-SN and Campaign 16 fluxes are consistent.
+As the uncertainty in the inter-campaign offsets is larger than the internal precision of the \emph{K2} photometry we adjust the Campaign 5 data within the offset uncertainty to match the approximately one week of contemporaneous ASAS-SN coverage.
+
+\begin{figure*}[hbt!]
+  \centering
+  \includegraphics[width=7.0in]{figures/2020_K2_ASASSN_lcurve_2panel.pdf}
+\caption{Four year lightcurve for S1063.
+\emph{K2} Campaigns 5, 16, and 18 (densely-sampled red points) and ASAS-SN $V-$band (coarsely-sampled gray points) show $\sim5-17\%$ peak-to-valley photometric variations indicative of secularly evolving surface coverage of starspots.
+The orange line shows a damped, driven harmonic oscillator \emph{celerit\`e} model \citep{2017AJ....154..220F} trained on the K2 and ASAS-SN data, and then applied to the noisy ASAS-SN points, with a standard-error uncertainty band in shaded orange.
+The vertical blue bar in mid-2015 shows the epoch of IGRINS data acquisition, which shows an approximately $8\%$ flux deficit compared to global upper envelope of flux in early 2017.}
+\label{fig:lightcurve}
+\end{figure*}
 
 \subsection{Ground-based photometric monitoring}
-We retrieved All-Sky Automated Survey for Supernovae \citep[ASAS-SN][]{shappee14} lightcurves from the Sky Portal \citep{2017PASP..129j4502K}.
+We retrieved All-Sky Automated Survey for Supernovae \citep[ASAS-SN;][]{shappee14} lightcurves from the Sky Portal \citep{2017PASP..129j4502K}.
 The lightcurves contained 758 epochs of $V-$ band photometry spanning 2013-2018 (source ASASSN-V J085113.44+115139.7) and 823 epochs of $g-$band photometry spanning mid-2017$-$2018.
@@
 The pixel images were not available to evaluate the extent of blending.
-%% Option: Pan-STARRS
 
@@
 \section{Analysis}
-\begin{itemize}
-\item Summary and assumptions of our methods
-\item K2 data
-\begin{itemize}
-  \item Zero points with FFIs or super stamps
-  \item Interpreting lightcurves
-  \item Period and amplitude of lightcurve, with multi-term Lomb-Scargle + Fourier reconstruction
-\end{itemize}
-\item Phase folded archival V-band photometry (ASASSN+)
 
-\subsection{IGRINS two-temperature spectral inference w/ Starfish}
+TBD
+
+1. Summary and assumptions of our methods
+2.  K2 data
+3.  Zero points with FFIs or super stamps
+4.   Interpreting lightcurves
+5.  Period and amplitude of lightcurve, with multi-term Lomb-Scargle + Fourier reconstruction
+6.  Phase folded archival V-band photometry (ASASSN+)
+
+\subsection{IGRINS two-temperature spectral decomposition}
 
@@
 We trained the spectral emulator \citep{czekala15} on this grid range, while preserving the absolute model mean fluxes to enable accurate flux comparison between two photospheres of disparate characteristic temperatures.
-This new approach offers improved accuracy over the scalar flux interpolated approach introduced in Appendix XX of \citet{gullysantiago17}, especially for such a large dynamic range in effective temperature.
+This new approach offers improved accuracy over the scalar flux interpolated approach introduced in Appendix A of \citet{gullysantiago17}, especially for such a large dynamic range in effective temperature.
 The spectral emulator approach propagates the uncertainty attributable to the coarsely sampled \texttt{PHOENIX} models.
@@
 \subsubsection{MCMC convergence and posterior predictive checks}
+
 Each IGRINS spectral order was fit independently, yielding over 20 individual sets of MCMC posteriors.
 We employed \texttt{emcee} \citep{foreman13} with 5000 samples and 40 walkers, spot-checking the MCMC chains for signatures of steady-state posterior probability distributions suggestive of convergence.
-Some orders did not pass our convergence criteria, usually due to poor initialization of nuissance parameters or overfitting.
-These specrtral orders were removed from future analysis, yielding a total of nine spectral orders, shown in Figure \ref{fig:IGRINS_spectra3x3}.
+Some orders did not pass our convergence criteria, usually due to poor initialization of nuisance parameters or overfitting.
+These spectral orders were removed from future analysis, yielding a total of nine spectral orders, shown in Figure \ref{fig:IGRINS_spectra3x3}.
 
@@
 \end{itemize}
-\end{itemize}
 
@@
 
-From the 4-year light curve of S1063 (REF LIGHT CURVE FIGURE) we determine that the IGRINS spectrum was observed at a local maximum in the stellar variability, but this flux was approximately 7\% below the global maximum over the four year period covered by ASAS-SN and \textit{K2}.
+From the 4-year light curve of S1063 (Figure~\ref{fig:lightcurve} we determine that the IGRINS spectrum was observed at a local maximum in the stellar variability, but this flux was only 91.2\% of the global maximum over the four year period covered by ASAS-SN and \textit{K2}.
 From a first-order interpretation of light curve amplitudes, minimum light corresponds to the largest star spot coverage while maximum light corresponds to the least star spot coverage, although these assumptions are complicated by the possibility of spot evolution \citep{basri18}.
-Assuming non-emitting spots, the stellar surface must be at least 7\% covered at the time of the IGRINS observation to account for the overall suppression in the maximum flux.
-If we adopt an ambient photosphere temperature of 5200 K and a spot temperature of 4000 K, the spot coverage would have to be 10\% to account for the flux suppression.
-At the time of observation, these spectral inference results show that the spot coverage was actually 32\%.
-This suggests that at the 4-year light curve maximum of S1063, the spot coverage was still around 20\% and definitely not an unspotted star.
-As seen in Figure LIGHT CURVE, the absolute light curve minimum (occuring at HJD **SOME DATE HERE**) was approximately 13\% lower than the flux at the time of observation.
-We conclude that the maximum spot filling factor at that time was closer to 50\%.
+Adopting an ambient photosphere temperature of 5200 K and a spot temperature of 4000 K, the spot coverage of S1063 must be at least 13\% to account for the flux at the time of observation, and yet these spectral inference results indicate the spot coverage at the time of the IGRINS observation was actually 32\%.
+This suggests that at maximum light over this 4-year period the spot coverage of S1063 was  approximately 20\% --- definitely not an unspotted star.
+Over the 4-years shown in Figure~\ref{fig:lightcurve}, the average flux variation is approximately 5\%, corresponding to an average spot covering fraction variation of $\pm$8\%, with a global flux minimum 10\% lower than the flux at the time of observation, requiring a spot filling factor closer to 45\%.
 
-The time average spot coverage fraction is AMOUNT over the four years, and with that we can calculate the time averaged effective temperature...
+SQUISHY TEFF TEXT
+The standard understanding of $T_{\textrm{eff}}$ is difficult to apply to spotted stars, especially stars with variation in the spot covering fraction.
+One interpretation is to calculate the surface-averaged $T_{\textrm{eff}}$:
 
-(UPDATE THIS WITH TIME AVERAGED SPOT NUMBERS) The presence of spots impacts the effective temperature of S1063.
-Taking into account both temperature components, we calculate the effective temperature using
 \begin{equation}
@@
 \end{equation}
-This results in an updated effective temperature for S1063 of $4900\pm125$ K.
+
+This, however, results in different $T_{\textrm{eff}}$ values for S1063 based on the instantaneous spot covering fraction.
+At the time of the IGRINS observation, the $T_{\textrm{eff}}$ would be $4900\pm100$ K, whereas the $T_{\textrm{eff}}$ corresponding to the 4-year light curve minimum would be approximately 4700 K.
 
@@
 
+%%% TODO: retool below discussion for the HRD discussion
+%\subsection{Starspots as confounding factors}
+%Mass, age, and metallicity uniquely map a main sequence star to its HR diagram position.
+A fourth factor---rotation---confounds this mapping in as-yet-unknown ways.
+Rotation might enhance spread in HR diagram positions (cite XX Davenport, Douglas?), with the most conspicuous spreads in the pre-main sequence regime (cite XX Covey, Stauffer).
+Spreads in the HR diagram offer clues to the consequences of rotation.
+Increased rotation heightens the magnetic dynamo strength and concomitant surface magnetic field.
+These magnetic fields suppress convective efficiency, meaning the star must increase in size at a lower effective temperature to allow the same amount of internal energy to escape (cite XX Feiden): rotating stars become bigger and cooler than their non-rotating counterparts (cite XX Somers).
+The interplay of rotation, dynamo, and surface fields remain an active area of research, with bright prospects for a unified theory involving the degree of magnetic complexity parameter (cite XX Garraffo).
+
+%Surface magnetic fields offer two key observational manifestations.
+The Zeeman Effect splits spectral line levels in magnetic-sensitive atomic transitions (cite XX Johns-Krull).
+Starspots induce stellar surface inhomogeneities that can be seen in the modulation of
+
+%The story in the post-main sequence is less clear.  Angular momentum transport governs rotation  as stars evolve over orders of magnitude in size.
+
 The spot coverage fraction measured here is consistent with the range of spot coverage seen on RS CVn of 30--40\% from measuring TiO band strength \citep{oneal96, oneal98, oneal04} and Doppler imaging \citep{hackman12}.
@@
 
-\appendix
-
-\section{Are starspots confusing?}
-\label{methods-details}
-
-Short answer: no!
+%\appendix
+%\section{Appendix heading}
+%\label{methods-details}
+%Placeholder text
 
@@
 %ADS
-We thank ADS!
-
+This research has made use of NASA’s Astrophysics Data System.
 %IGRINS
-This work used the Immersion Grating Infrared Spectrometer(IGRINS) that was developed under a collaboration between the University of Texas at Austin and the Korea Astronomy and Space Science Institute (KASI) with the financial support of the US National Science Foundation under grant AST-1229522, of the University of Texas at Austin, and of the Korean GMT Project of KASI.
-
+This work used the Immersion Grating Infrared Spectrometer (IGRINS) that was developed under a collaboration between the University of Texas at Austin and the Korea Astronomy and Space Science Institute (KASI) with the financial support of the US National Science Foundation under grant AST-1229522, of the University of Texas at Austin, and of the Korean GMT Project of KASI.
 %Kepler
 This paper includes data collected by the Kepler mission. Funding for the Kepler mission is provided by the NASA Science Mission directorate.
-
 % MAST
-Some/all of the data presented in this paper were obtained from the Mikulski Archive for Space Telescopes (MAST).
+Some of the data presented in this paper were obtained from the Mikulski Archive for Space Telescopes (MAST).
 STScI is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS5-26555.
@@
 
-{\it Facilities:} \facility{Smith (IGRINS)}, \facility{AAVSO}, \facility{INTEGRAL (OMC)}, \facility{ASAS}, \facility{Gaia}
+{\it Facilities:} \facility{Smith (IGRINS)}, \facility{ASAS}, \facility{Gaia}
 

### 2021-03-12 document/ms.tex
:truck: sync paper from Overleaf

@@
-%\documentclass[iop,revtex4]{emulateapj}% change onecolumn to iop for fancy, iop to twocolumn for manuscript
-\documentclass[twocolumn]{emulateapj}% change onecolumn to iop for fancy, iop to onecolumn for manuscript
-%\documentclass[12pt,preprint]{aastex}
+\documentclass[modern,trackchanges]{aastex631}
+\bibliographystyle{aasjournal}
 
-\usepackage{graphicx}
 \usepackage[caption=false]{subfig}
-%\usepackage{lineno}
-%\usepackage{blindtext}
-%\linenumbers
-%\usepackage{breqn}
-\usepackage{amsmath}
 
-\let\pwiflocal=\iffalse \let\pwifjournal=\iffalse
-%From: http://arxiv.org/format/1512.00483
-%\input{setup}
-\input{mgs_setup}
+\newcommand\natalienote[1]{\textbf{{\color{orange}#1}}}
+\newcommand\gullynote[1]{\textbf{{\color{magenta}#1}}}
+\newcommand\emilynote[1]{\textbf{{\color{cyan}#1}}}
+\newcommand{\Msolar}{M$_{\odot}$}
 
-\newcommand{\iancze}{{\sc C15}}
-
-\providecommand{\eprint}[1]{\href{http://arxiv.org/abs/#1}{#1}}
-\providecommand{\adsurl}[1]{\href{#1}{ADS}}
-\newcommand{\project}[1]{\textsl{#1}}
-
-\slugcomment{In preparation}
-
-\shorttitle{Spots on Sub-subgiants}
-
+\begin{document}
+\shorttitle{Starspots on Sub-subgiant S1063}
 \shortauthors{TBD}
 
-\bibliographystyle{yahapj}
+\title{Starspots as the Cause of Underluminosity for M67 Sub-Subgiant S1063 }
 
-\begin{document}
-
-\title{Starspots on sub sub giants }
-
-\author{TBD,\altaffilmark{1}, author list TBD}
-
-\altaffiltext{1}{TBD}
+\author{TBD}
+\affiliation{TBD}
 
@@
 
-\maketitle
-
 \section{Introduction}\label{sec:intro}
+\emilynote{This is a note from Emily.}
+\natalienote{This is a note from Natalie.}
+\gullynote{This is a note from Gully.}
 Recent studies illuminate the important role stellar magnetic activity plays in stellar structure.
@@
 The existence of sub-subgiants cannot be explained with typical single-star stellar evolutionary pathways.
-Three possible formation scenarios for sub-subgiants were put forth by \citet{leiner17}: mass transfer in a binary system, stripping of a subgiant star envelope through a dynamical encounter, and reduced luminosity as a result of inhibited convection and large starspot covering fractions due to the presence of strong magnetic fields.
+Three possible formation scenarios for sub-subgiants were put forth by \citet{geller17} and \citet{leiner17}: mass transfer in a binary system, stripping of a subgiant star envelope through a dynamical encounter, and reduced luminosity as a result of inhibited convection and large starspot covering fractions due to the presence of strong magnetic fields.
 \citet{leiner17} conclude that the majority of sub-subgiants are likely the result of strong magnetic fields.
-This is supported by the presence of H-alpha and X-ray emission and optical variability seen across the known sub-subgiant population \citep{geller17}, all observational signatures of magnetic activity and the presence of starspots.
+This interpretation is supported by the presence of H-alpha and X-ray emission and optical variability seen across the known sub-subgiant population \citep{geller17}, all observational signatures of magnetic activity and the presence of starspots.
 
-The portion of the stellar surface covered with starspots is an important observational proxy for magnetic activity.
-Monochromatic light curves are often used to identify spotted stars \citep{2014ApJS..211...24M} but can only provide a limit on the differential spot coverage: a vast null space of longitudinally symmetric starspot geometries evade detection in monochromatic lightcurves alone \citep{2019AJ....157...64L}.
-Measuring the overall spot coverage typically requires Doppler imaging or interferometry studies restricted to only the brightest and most nearby sources \citep{roettenbacher16}, or relying on inferred covering fractions from TiO band observations \citep{oneal96,fang2016,2019AJ....158..101M}.
-Testing the next era of stellar activity models requires new analysis methodologies to measure spot-covering fractions of a larger number of targets, including sub-subgiants.
+Ideally we would directly measure the radius and internal magnetic field to calibrate how the star inflates as a function of convective efficiency, and the positions of SSGs could be explained.
+In practice these quantities are difficult to measure at the precision required to demonstration inflation on single magnetically active systems, though aggregate populations have shown evidence for magnetic inflation \citep{2018AJ....155..225K,2018MNRAS.476.3245J}.
+Starspots have become a rich observational proxy for gauging the evolutionary state of stars that may be magnetically inflated, without needing to estimate magnetic field strengths.
+
+The portion of the stellar surface covered with starspots is related to the amount of magnetic activity.
+The mere existence of starspot modulation betrays magnetic activity in stars.
+Starspots rupture the otherwise-pristine photospheric boundary conditions that regulate energy loss from stars.
+Starspots emit light of their own that can be captured and analyzed to quantify the impact of such boundary condition changes.
+
+A full accounting of starspots requires careful consideration of geometrical degeneracies.
+Monochromatic light curves can indicate spotted stars \citep{2014ApJS..211...24M} but can only provide a lower limit on the differential spot coverage between the most and least spotted hemispheres.
+Longitudinally symmetric starspot geometries evade detection in monochromatic lightcurves alone \citep{2019AJ....157...64L}.
+Measuring the spot configuration typically requires Doppler imaging or interferometry studies restricted to only the brightest and most nearby sources \citep{roettenbacher16}.
+Disk-integrated covering fractions can be obtained from TiO band observations \citep{oneal96,fang2016,2019AJ....158..101M}.
+Testing the next era of stellar activity models requires precision methodologies to measure spot-covering fractions of a larger number of targets, including sub-subgiants.
 
@@
 
-In this paper we focus on a single sub-subgiant system, S1063 in the open cluster M67.
-This system is a prototypical sub-subgiant star, with an single-lined spectroscopic orbital period of 18.4 days \citep{geller17}, an X-ray luminosity of $1.3\times10^{31}$ erg s$^{-1}$ \citep{vandenberg99}, and a variable light curve in \textit{K2} and ASAS-SN (Section \ref{K2lightcurve}).
+In this paper we demonstrate the power of this methodology by focusing on a single sub-subgiant system, S1063 in the open cluster M67.
+This system is a prototypical sub-subgiant star, with an single-lined spectroscopic orbital period of 18.4 days \citep{geller17}, an X-ray luminosity of $1.3\times10^{31}$ erg s$^{-1}$ \citep{vandenberg99}, and a variable light curve in \textit{K2} and ASAS-SN (Section~\ref{sec:K2lightcurve}).
+\emph{Gaia} DR2 astrometry \citep{2016A&A...595A...1G, 2018A&A...616A...1G} indicates a parallax ($1.17\pm0.025 \;$mas) and proper motion for S1063 (\emph{Gaia} DR2 604921030968952832) consistent with other M67 members, and approaching 100\% membership probability \citep{2018ApJ...869....9G}.
+We present our observational data products in Section~\ref{sec:observations} and subsequent analysis in Section~\ref{sec:analysis}.
+Our results are given in Section~\ref{sec:results} with Discussion in Section~\ref{sec:discussion}.
+Finally, our conclusions are outlined in Section~\ref{sec:conclusions}.
 
 \section{Observation and data reduction}
+\label{sec:observations}
+
 \subsection{IGRINS observations}
@@
 The sky emission lines and telluric lines were removed with the IGRINS Pipeline Package  \citep[PLP;][]{jaejoonlee16} and a reference A0V star acquired nearby in time and airmass.
-The $H-$band spectra exhibited signal-to-noise ratio $S/N\sim50$ per pixel.
+The $H-$band spectra exhibited a signal-to-noise ratio of approximately $50$ per pixel.
 The $K-$band spectra possessed low $S/N$ and were excluded from further analysis.
 
-\begin{figure*}[hbt!]
+\begin{figure*}[ht]
   \centering
@@
 \subsection{K2 superstamp lightcurves}
-The \emph{Kepler} spacecraft targeted S0163 (EPIC 211414597) during the \emph{K2} mission \citep{howell14} in Campaigns 5, 16, 18 as part of the M67 superstamps.
+The \emph{Kepler} spacecraft targeted S1063 (EPIC 211414597) during the \emph{K2} mission \citep{howell14} in Campaigns 5, 16, 18 as part of the M67 superstamps.
 The instrumental point spread function (PSF) of S1063 fell entirely within the oversized K2 target pixel files in Campaign 5 (K2 Custom Aperture ID 200008674, channel 13) and Campaign 18 (K2 Custom Aperture ID 200233338).
@@
 The apertures were chosen to minimize flux-loss out of the aperture due to spacecraft-induced image motion, while avoiding low-$S/N$ pixels and the wings of adjacent PSFs.
-The Campaign 16 source PSF overlapped the edge of Custom Aperture ID 200200534; a mosaic of adjacent superstamps was assembled before conducting aperture photometry.
+The Campaign 16 source PSF overlapped the edge of Custom Aperture ID 200200534, therefore a mosaic of adjacent superstamps was assembled before conducting aperture photometry.
 We detrended motion-induced image artifacts with the Self Flat Field algorithm \citep{vanderburg14} implemented in \texttt{lightkurve}.  Postage stamp images are shown in Figure \ref{fig:imaging}.
 
-\subsection{Inter-campaign relative photometry with K2 Full Frame Images}\label{K2lightcurve}
+\subsection{Ground-based photometric monitoring}
+We retrieved All-Sky Automated Survey for Supernovae \citep[ASAS-SN;][]{shappee14} lightcurves from the Sky Portal \citep{2017PASP..129j4502K}.
+The lightcurves contained 758 epochs of $V-$ band photometry spanning 2013-2018 (source ASASSN-V J085113.44+115139.7) and 823 epochs of $g-$band photometry spanning mid-2017--2018.
+The $\sim8''$ ASAS-SN pixels may cause some PSF blending of the nearby-albeit-fainter source seen at the bottom of Figure \ref{fig:imaging}.
+The pixel images were not available to evaluate the extent of blending.
+
+\subsection{Inter-campaign relative photometry with K2 Full Frame Images}\label{sec:K2lightcurve}
 
@@
 
-Given the full contemporaneous coverage between ground-based ASAS-SN data with Campaign 16, we set the overall vertical registration of the \emph{K2} lightcurves such that the ASAS-SN and Campaign 16 fluxes are consistent.
-As the uncertainty in the inter-campaign offsets is larger than the internal precision of the \emph{K2} photometry we adjust the Campaign 5 data within the offset uncertainty to match the approximately one week of contemporaneous ASAS-SN coverage.
+\begin{figure*}[ht]
+    \centering
+    \begin{tabular}{cc}
+      \includegraphics[width=3in]{figures/AllCampaigns_Periodogram.pdf}   & \includegraphics[width=3in]{figures/AllCampaigns_Phased_Lightcurve.pdf}  \\
+    \end{tabular}
+    \caption{On the right, a Lomb-Scargle Periodogram of the light curve for each \emph{K2} campaign and on the left, the corresponding phased \emph{K2} light curves.
+The average period associated with maximum power across all three campaigns is P = 23.5 days.
+\deleted{The phased light curves indicate the most spotted hemisphere occurred around a rotation phase of 0.4 during C5 (shown in blue) but shifted to a rotation phase of approximately 0.7 in C16 and C18 (shown in purple and green, respectively).
+This is suggestive of the spot morphology of S1063 shifting over this 2.5-year period.} \explain{How precisely do we have to know the period to confidently detect a phase change?} }
+    \label{fig:periodogram}
+\end{figure*}
 
-\begin{figure*}[hbt!]
+\begin{figure*}[ht]
   \centering
-  \includegraphics[width=7.0in]{figures/2020_K2_ASASSN_lcurve_2panel.pdf}
-\caption{Four year lightcurve for S1063.
-\emph{K2} Campaigns 5, 16, and 18 (densely-sampled red points) and ASAS-SN $V-$band (coarsely-sampled gray points) show $\sim5-17\%$ peak-to-valley photometric variations indicative of secularly evolving surface coverage of starspots.
+  \includegraphics[width=0.95\textwidth]{figures/2020_K2_ASASSN_lcurve_2panel.pdf}
+\caption{Four year lightcurve for S1063, normalized to a maximum flux of 1.00 as denoted by the gray dashed line.
+The mean flux of 0.895 is shown with the gray dotted line.
+\emph{K2} Campaigns 5, 16, and 18 (densely-sampled red points) and ASAS-SN $V-$band (coarsely-sampled gray points) show approximately $5-17\%$ peak-to-valley photometric variations indicative of secularly evolving surface coverage of starspots.
 The orange line shows a damped, driven harmonic oscillator \emph{celerit\`e} model \citep{2017AJ....154..220F} trained on the K2 and ASAS-SN data, and then applied to the noisy ASAS-SN points, with a standard-error uncertainty band in shaded orange.
-The vertical blue bar in mid-2015 shows the epoch of IGRINS data acquisition, which shows an approximately $8\%$ flux deficit compared to global upper envelope of flux in early 2017.}
+The vertical blue bar in mid-2015 indicates the epoch of IGRINS data acquisition, which shows an approximate $8\%$ flux deficit compared to global maximum flux in early 2017.}
 \label{fig:lightcurve}
@@
 
-\subsection{Ground-based photometric monitoring}
-We retrieved All-Sky Automated Survey for Supernovae \citep[ASAS-SN;][]{shappee14} lightcurves from the Sky Portal \citep{2017PASP..129j4502K}.
-The lightcurves contained 758 epochs of $V-$ band photometry spanning 2013-2018 (source ASASSN-V J085113.44+115139.7) and 823 epochs of $g-$band photometry spanning mid-2017$-$2018.
-The $\sim8''$ ASAS-SN pixels may cause some PSF blending of the nearby-albeit-fainter source seen at the bottom of Figure \ref{fig:imaging}.
-The pixel images were not available to evaluate the extent of blending.
+\section{Analysis}
+\label{sec:analysis}
 
-\subsection{Gaia data}
-\emph{Gaia} DR2 astrometry \citep{2016A&A...595A...1G, 2018A&A...616A...1G} indicates a parallax ($1.17\pm0.025 \;$mas) and proper motion for S1063 (\emph{Gaia} DR2 604921030968952832) consistent with other M67 members, and approaching 100\% membership probability \citep{2018ApJ...869....9G}.
+%INTRO TEXT:
+%Starspots emit a spectrum of their own at a lower temperature and with distinct absorption features compared to the ambient photosphere.
+The observed spectrum is a composite of the spot and photosphere spectra and can therefore be deconvolved.
+This deconvolution constrains the spot-covering fraction as well as the spot and photosphere temperatures.
+This is possible by performing a two-temperature probabilistic spectral decomposition using the spectral inference framework \texttt{Starfish} \citep{czekala15}, recently extended to support composite spectra \citep{gullysantiago17}.
+The resulting spot characterization can be used to anchor light curve information, providing insight into the overall stellar activity level and constraining the long-term spot coverage \citep{neff95}.
+This strategy only requires high-resolution echelle spectroscopy and photometric monitoring, dramatically increasing the number of sources for which we can observationally constrain spot-covering fractions.
 
-\section{Analysis}
+Constraining starspot covering fraction for stars such as S1063 requires a careful combination of light curve interpretation and spectral analysis, using spectral decomposition tools such as \texttt{Starfish} \citep{czekala15} to benchmark epochs of starspot coverage in long-term photometric monitoring.
 
-TBD
+\subsection{Joint modeling of ASAS-SN and \emph{K2} Lightcurves}
+In order to characterize the long-term behavior of S1063 we jointly modeled the ASAS-SN and K2 lightcurves as a damped, driven Simple Harmonic Oscillator (SHO) Gaussian Process (GP) with \texttt{celerit\`e} \citep{2017AJ....154..220F}, revealing periodicity and secular changes in flux levels over a multi-year timeframe.
+This strategy offers flexibility to cope with windowing effects and the high dynamic range in data sampling and quality available across ASAS-SN and \emph{K2}.
+The ASAS-SN $V$-band and \emph{K2} photometric band share significant overlap and are treated as the same for this analysis.
 
-1. Summary and assumptions of our methods
-2.  K2 data
-3.  Zero points with FFIs or super stamps
-4.   Interpreting lightcurves
-5.  Period and amplitude of lightcurve, with multi-term Lomb-Scargle + Fourier reconstruction
-6.  Phase folded archival V-band photometry (ASASSN+)
+ We tuned a two-period GP model, with the harmonic component possessing roughly half the period $P_H\sim12.5\;\mathrm{d}$ of the fundamental period $P_0=23.5\;\mathrm{d}$.
+The harmonic overtone frequency can be seen by eye in Figure \ref{fig:lightcurve}, as the \emph{K2} lightcurves appear more complex than a pure sine wave.
+Each periodic GP term also possessed correlation amplitude and SHO quality factor which we consider nuisance parameters for the purpose of this fitting.
+We found broadly consistent values when \emph{K2} lightcurves were fitted on a per-campaign basis.
+We then fit the three campaigns \emph{simultaneously} in the following way.
+We set the overall vertical registration of the \emph{K2} lightcurves such that the ASAS-SN and Campaign 16 trends match, since M67 was contemporaneously observable from the ground for the entire duration of K2 Campaign 16.
+The uncertainty in the inter-campaign offsets calculated in Section~\ref{sec:K2lightcurve} is larger than the internal precision of the \emph{K2} photometry, so we adjust the Campaign 5 data within the offset uncertainty to match the approximately one week of temporal overlap with ASAS-SN.
+We added an additional non-periodic secular trend GP component to capture the campaign-to-campaign mean-level variation, also considered a nuisance parameter.
+
+Finally, we evaluated the trained GP model at the location of the ASAS-SN photometry, and at windows lacking data altogether.
+This trend appears in Figure \ref{fig:lightcurve} as the dark orange line with an orange standard confidence region.
+This trendline guides the eye to see broad secular changes to the amplitude encoded in the noisy ASAS-SN data, with a global maximum peak-to-valley amplitude of 17\% occurring near 2017 January, and global minimum peak-to-valley of 3\% occurring near to the time of the IGRINS measurement.
 
@@
 
-We performed two-temperature probabilistic spectral decomposition on the IGRINS $H-$band spectrum.
+Even a single epoch of IGRINS observations provides an opportunity to constrain the spot covering fraction of S1063 that can be used as a benchmark for interpreting the long-term flux variation apparent in Figure~\ref{fig:lightcurve}.
+We performed a two-temperature probabilistic spectral decomposition on the IGRINS $H-$band spectrum.
 We applied the spectral inference framework \texttt{Starfish} \citep{czekala15}, recently extended to support composite spectra comprised of mixtures of two distinct photospheric components \citep{gullysantiago17}.
-Here, the two temperature components are labeled as $T_{\mathrm{spot}}$ and $T_{\mathrm{amb}}$ for the starspot and ambient photospheric emission respectively, with a filling factor $f$ defined as the ratio of collective projected surface area of the spot groups to the projected area of the star.
+Here, the two temperature components are labeled as $T_{\mathrm{spot}}$ and $T_{\mathrm{amb}}$ for the starspot and ambient photospheric emission, respectively, with a filling factor $f$ defined as the ratio of disk-integrated projected surface area of the spot groups to the projected area of the star.
 
-We employed the \texttt{PHOENIX} precomputed synthetic model grid with grid ranges of $3000 < T_{\mathrm{eff}} \; (K) < 5300 $, $3 < \log{g \;(cm/s)}  < 4 $, and $ -0.5 <  [\mathrm{Fe}/\mathrm{H}] <0.5$.
-We trained the spectral emulator \citep{czekala15} on this grid range, while preserving the absolute model mean fluxes to enable accurate flux comparison between two photospheres of disparate characteristic temperatures.
+We employed the \texttt{PHOENIX} precomputed synthetic model grid \citep{husser13} with grid ranges of $3000 < T_{\mathrm{eff}} \; (\textrm{K}) < 5300 $, $3 < \log{g \;(\textrm{cm/s})}  < 4 $, and $ -0.5 <  [\mathrm{Fe}/\mathrm{H}] <0.5$.
+We trained the spectral emulator \citep{czekala15} on this grid range, while preserving the absolute model mean fluxes to enable accurate flux comparison between two spectra of disparate characteristic temperatures.
 This new approach offers improved accuracy over the scalar flux interpolated approach introduced in Appendix A of \citet{gullysantiago17}, especially for such a large dynamic range in effective temperature.
-The spectral emulator approach propagates the uncertainty attributable to the coarsely sampled \texttt{PHOENIX} models.
+The spectral emulator approach also propagates the uncertainty attributable to the coarsely sampled \texttt{PHOENIX} models.
 
@@
 
-Each IGRINS spectral order was fit independently, yielding over 20 individual sets of MCMC posteriors.
+Each IGRINS $H$-band spectral order was fit independently, yielding over 20 individual sets of MCMC posteriors.
 We employed \texttt{emcee} \citep{foreman13} with 5000 samples and 40 walkers, spot-checking the MCMC chains for signatures of steady-state posterior probability distributions suggestive of convergence.
 Some orders did not pass our convergence criteria, usually due to poor initialization of nuisance parameters or overfitting.
-These spectral orders were removed from future analysis, yielding a total of nine spectral orders, shown in Figure \ref{fig:IGRINS_spectra3x3}.
+Furthermore, the radial velocity $v_z$ and projected rotational broadening $v\sin{i}$ were spot-checked to verify both consistent values among spectral orders as well as posterior distributions indicative of information-rich spectral orders.
+Some relatively feature-free spectral orders such as $m=103$ did not offer enough constraining power to derive meaningful results in the face of multiple sources of degeneracy.
+Collectively, these discrepant or uninformative spectral orders were removed from future analysis, yielding a total of nine preserved spectral orders, shown in Figure \ref{fig:IGRINS_spectra3x3}.
+All spectral orders were consistent with a $v\sin{i}=10 \;\mathrm{km/s}$, with typical per-order $1-\sigma$ uncertainties of $0.2-1.0 \;\mathrm{km/s}$.
+The per-order estimates for radial velocity were all consistent with $v_z=44\;\mathrm{km/s}$ at the measurement epoch, uncorrected for barycentric motion.
 
-\subsubsection{FIGURE: IGRINS Spectra}
-\begin{figure*}
+\begin{figure*}[ht]
  \centering
- \includegraphics[width=0.98\textwidth]{figures/H_band_spectra_3x3.pdf}
- \caption{Nine $H-$band IGRINS spectral orders with probabilistic spectral decomposition.}
+ \includegraphics[width=0.90\textwidth]{figures/H_band_spectra_3x3.pdf}
+ \caption{Nine $H-$band IGRINS echelle orders showing two-component spectral decomposition of collective starspot photospheric emission, labeled with the corresponding order number $m$.
+The starspot spectrum (thick red line) and ambient photosphere spectrum (dotted blue line) combine to form the composite spectrum (solid purple line) that resembles the observed spectrum (thick gray line).
+The starspot and ambient components can share similar spectral structure, leading to a range of filling factors and temperatures ranges with nearly equivalent composite spectra; here we present a single random draw from the MCMC posterior, not a ``best fit''.
+The cool and hot temperatures $T_{\textrm{s}}$ and $T_{\textrm{amb}}$ for each draw show variety consistent with the fitting uncertainty.
+The corresponding spot filling factor, $f_{\textrm{s}}$, is also shown for each specific random draw.
+Unexplained spectral structure and over- and under- fitting of spectral lines arises from a combination of PHOENIX model imperfections, possible magnetic Zeeman broadening, and other model mis-specifications.}
  \label{fig:IGRINS_spectra3x3}
@@
 
-\subsubsection{Internal consistency of vsini, $v_z$}
-We additionally spot-checked the MCMC posteriors with posterior predictive checks... XX
+%\subsubsection{Consistency of stellar characterization}
+%Vsini is similar to before and radial velocity is what we expect given orbital phasing (NEED TO DO THE PHASING).
 
-\item Analysis of near-IR flux contribution from binary companion
-\begin{itemize}
-  \item Limits on companion types
-\end{itemize}
+%TODO: Analysis of near-IR flux contribution from binary companion
+%TODO: Limits on companion types
 
 \section{Results}
+\label{sec:results}
 
-Using the \texttt{Starfish} spectral inference results we investigate the relationship between spot temperature and filling factor.
-In Figure~\ref{fig:tspot_fillingfactor3x3} we show 2-dimensional distributions of filling factor and spot temperature of the last 200 samples for the nine orders with accepted fits.
-Similar trends between spot temperature and filling factor appear across most of the orders.
+\subsection{Spot temperature and filling factor}
+\label{sec:starfishresults}
+Using the \texttt{Starfish} spectral inference results we investigate the joint constraints on spot temperature and filling factor, marginalized over all other uncertainties in stellar properties and fitting hyper-parameters (such as Starfish-derived Gaussian Process correlation length and amplitude and continuum fitting polynomials).
+In Figure~\ref{fig:tspot_fillingfactor3x3} we show 2-dimensional posterior distributions of filling factor and spot temperature of the last 1000 samples thinned by a factor of 10 from all 40 \texttt{emcee} walkers for the nine orders with accepted fits.
+The orders show broad agreement between spot temperature and filling factor.
 Across all nine orders, the median filling factor value is 32\% with a standard deviation of 7\%, with a corresponding spot temperature of $4000 \pm 200$ K.
-The ambient photosphere temperature associated with this spot signature is $5200\pm25$ K.
-This is similar to the optical spectroscopic temperature of 5000 K determined by \citet{mathieu03}, which is expected as the optical spectrum will have less significant spot signatures than the IGRINS spectrum in the NIR.
+The ambient photosphere temperature associated with this spot signature varies from order-to-order and is broadly consistent with a range of temperatures between 5000 K and 5300 K, with a best guess value of $5200$ K.
+These values are broadly consistent with a spectroscopic temperature of 5000 K determined by \citet{mathieu03} determined from visible-wavelength spectra.
+Visible wavelength spectra principally perceive the ambient photosphere, due to the near-zero starspot contrast at those wavelengths.
+Therefore the most reliable ambient photosphere estimate likely stems from the visible-based measurement, and not our near-IR-based estimate.
 
-From the 4-year light curve of S1063 (Figure~\ref{fig:lightcurve} we determine that the IGRINS spectrum was observed at a local maximum in the stellar variability, but this flux was only 91.2\% of the global maximum over the four year period covered by ASAS-SN and \textit{K2}.
-From a first-order interpretation of light curve amplitudes, minimum light corresponds to the largest star spot coverage while maximum light corresponds to the least star spot coverage, although these assumptions are complicated by the possibility of spot evolution \citep{basri18}.
-Adopting an ambient photosphere temperature of 5200 K and a spot temperature of 4000 K, the spot coverage of S1063 must be at least 13\% to account for the flux at the time of observation, and yet these spectral inference results indicate the spot coverage at the time of the IGRINS observation was actually 32\%.
-This suggests that at maximum light over this 4-year period the spot coverage of S1063 was  approximately 20\% --- definitely not an unspotted star.
-Over the 4-years shown in Figure~\ref{fig:lightcurve}, the average flux variation is approximately 5\%, corresponding to an average spot covering fraction variation of $\pm$8\%, with a global flux minimum 10\% lower than the flux at the time of observation, requiring a spot filling factor closer to 45\%.
+\subsubsection{Light curve interpretation}
+The ASAS-SN and \textit{K2} C5 data of S1063 (Figure~\ref{fig:lightcurve}) indicate that the IGRINS observation was coincidentally acquired near its modest local maximum at an overall flux level of 91.2\%.
+This is close to the overall 89.5\% mean flux level, where the 100\% flux level is equal to the global maximum over the four-year period covered by ASAS-SN and \textit{K2}.
+The lightcurve exhibits relatively modest variability at the time of the IGRINS observations with merely 3\% peak-to-valley variation compared to its global largest variation of almost 17\% as observed around 2017 January.
 
-SQUISHY TEFF TEXT
-The standard understanding of $T_{\textrm{eff}}$ is difficult to apply to spotted stars, especially stars with variation in the spot covering fraction.
-One interpretation is to calculate the surface-averaged $T_{\textrm{eff}}$:
+For a first-order interpretation of light curve amplitudes, we posit that the lightcurve is starspot-dominated as opposed to facula-dominated.
+Under this assumption, minimum light corresponds to the largest blockage of ambient flux and therefore the largest starspot coverage on the instantaneous hemisphere projected towards the observer \cite{basri18}.
+Maximum light corresponds to the moments with the least---\emph{but not necessarily zero}---starspot coverage.
 
-\begin{equation}
-T_{\textrm{eff}}^4 = f_{\textrm{spot}} T_{\textrm{spot}}^4 + (1 -f_{\textrm{spot}}) T_{\textrm{ambient}}^4 .
-\end{equation}
+If S1063 was spot-free at the time of the global lightcurve maximum the epoch of IGRINS observation would correspond to starspots blocking 8.8\% of the total instantaneous stellar flux (100\% $-$ 91.2\% $=$ 8.8\% blocked flux at the time of observation), assuming non-emitting starspots.
+However, starspots are emitting and effectively filling in some of the light that is ``blocked''.
+This non-zero starspot emission demands that the spot covering fraction must be greater than 8.8\% at the time of the IGRINS observation.
+Adopting an ambient photosphere temperature of 5200 K and a spot temperature of 4000 K, the projected spot coverage of S1063 must be at least 13\% to account for the 8.8\% flux loss in the $V$-band.
 
-This, however, results in different $T_{\textrm{eff}}$ values for S1063 based on the instantaneous spot covering fraction.
-At the time of the IGRINS observation, the $T_{\textrm{eff}}$ would be $4900\pm100$ K, whereas the $T_{\textrm{eff}}$ corresponding to the 4-year light curve minimum would be approximately 4700 K.
+This 13\% spot coverage is a minimum value based on an assumption that the maximum lightcurve flux results from an un-spotted star.
+Our spectral inference results indicate the spot coverage at the time of the IGRINS observation was, in fact, 32\%.
+This suggests that at maximum light over this 4-year period the spot coverage of S1063 was approximately 20\%, and not zero as a first-order interpretation of the light curve would imply.
 
-\begin{itemize}
-\item We MEASURE spots in spectra
-\begin{itemize}
-  \item S1063 has $32 \pm 7$\% coverage fraction of spots with Tspot $4000\pm200$ K based on IGRINS + Starfish
-  \item Revised effective temperature using both temperature components $[f_{\textrm{spot}} * T_{\textrm{spot}}^4 + (1 -f_{\textrm{spot}}) * T_{\textrm{ambient}}^4] = T_{\textrm{eff}}^4$
+The presence of starspots at the light curve maximum acts as a starspot baseline for interpreting the lightcurve.
+Over the 4-years shown in Figure~\ref{fig:lightcurve}, the average flux variation is approximately 5\%, corresponding to an average spot covering fraction variation from each observed hemisphere of $\pm$8\%.
+The lightcurve exhibits a global flux minimum 10\% lower than the flux at the time of the IGRINS observation, requiring a spot filling factor close to 45\% on the projected hemisphere at that time.
 
-  \item *bonus* Rsini
-\end{itemize}
-\item IGRINS observations occurred at maximum of lightcurve, so total spot coverage is even greater
-\item *bonus* total spot filling factor estimate given light curve magnitude
-\item FIGURE: $T_{spot}$ versus $f_{spot}$ plot
+We therefore determine that over the time period from 2014--2018 S1063 has possessed a range of 20--45\% coverage fraction of spots, with an average close to 30\%.
+The IGRINS observation occurring near the mean global flux level fortuitously allows a robust characterization of the average state of S1063.
+These numbers possess formal uncertainties in the few percent range, and additional uncertainties from our reliance on spectral models.
+But broadly speaking, our result is firm under our assumptions--- S1063 has a large persistent starspot population that ebbs and flows in its longitudinal symmetry, resulting in variation in the peak-to-valley modulation, but always possesses an approximately 30\% spot covering fraction.
 
- \begin{figure*}[h]
+\begin{table}[]
+\label{tab:s1063parameters}
+\caption{S1063 Surface and Stellar Parameters}
+\begin{tabular}{llcccc}
+
+  &         & Spot temp  & Filling factor & Ambient temp & Radius  \\
+   &        &  (K) & (\%) &  (K) & ($R_{\odot}$) \\ \hline
+\multicolumn{3}{l}{\textit{Spectroscopic Constraints:}}  \\
+\phantom{EEE} & This work     & $4000\pm200$  & $32\pm7$    & 5200 &   3.7--4.6     \\
+& \citet{mathieu03} &  ...    &  ...    &     5000    &  2.4  \\
+\multicolumn{3}{l}{\textit{Photometric Constraints:}} \\
+& SPOTS models$^{a}$  &      &  50--80    &         &        \\
+& \citet{leiner17} & ... & ... & 4500$^\textrm{b}$ & 2.8--3.1 \\
+& & 3500$^\textrm{c}$ & 40 & 4750 & 3.4 \\
+\hline
+\multicolumn{6}{l}{$^{a}$Section~\ref{sec:model_comparison}, from \citet{somers20}.} \\
+\multicolumn{6}{l}{$^{b}$Unspotted model.} \\
+\multicolumn{6}{l}{$^{c}$Model assuming 40\% spot coverage with a spot temperature contrast of $\sim$1000 K.}
+\end{tabular}
+\end{table}
+
+%text from Leiner et al.
+2017: Similarly, adding a spot to 13008 changes the best-fit parameters to 4750 K and 3.4 RSun, closer to the 5000 K spectroscopic temperature (Mathieu et al.
+2003).
+--is this also at 40% spot covering fraction like 15028 in the previous paragraph?
+
+ \begin{figure*}[ht]
    \centering
    \begin{tabular}{ccc}
-     \subfloat{\includegraphics[width=2in]{figures/H_band_Tspot_fillingfactor_m119.pdf}} &
-     \subfloat{\includegraphics[width=2in]{figures/H_band_Tspot_fillingfactor_m118.pdf}} &
-     \subfloat{\includegraphics[width=2in]{figures/H_band_Tspot_fillingfactor_m116.pdf}} \\
-     \subfloat{\includegraphics[width=2in]{figures/H_band_Tspot_fillingfactor_m114.pdf}} &
-     \subfloat{\includegraphics[width=2in]{figures/H_band_Tspot_fillingfactor_m113.pdf}} &
-     \subfloat{\includegraphics[width=2in]{figures/H_band_Tspot_fillingfactor_m110.pdf}} \\
-     \subfloat{\includegraphics[width=2in]{figures/H_band_Tspot_fillingfactor_m109.pdf}} &
-     \subfloat{\includegraphics[width=2in]{figures/H_band_Tspot_fillingfactor_m107.pdf}} &
-     \subfloat{\includegraphics[width=2in]{figures/H_band_Tspot_fillingfactor_m106.pdf}}
+     \subfloat{\includegraphics[width=2in]{figures/H_band_Tspot_fillingfactor_m119_new.pdf}} &
+     \subfloat{\includegraphics[width=2in]{figures/H_band_Tspot_fillingfactor_m118_new.pdf}} &
+     \subfloat{\includegraphics[width=2in]{figures/H_band_Tspot_fillingfactor_m116_new.pdf}} \\
+     \subfloat{\includegraphics[width=2in]{figures/H_band_Tspot_fillingfactor_m114_new.pdf}} &
+     \subfloat{\includegraphics[width=2in]{figures/H_band_Tspot_fillingfactor_m113_new.pdf}} &
+     \subfloat{\includegraphics[width=2in]{figures/H_band_Tspot_fillingfactor_m110_new.pdf}} \\
+     \subfloat{\includegraphics[width=2in]{figures/H_band_Tspot_fillingfactor_m109_new.pdf}} &
+     \subfloat{\includegraphics[width=2in]{figures/H_band_Tspot_fillingfactor_m107_new.pdf}} &
+     \subfloat{\includegraphics[width=2in]{figures/H_band_Tspot_fillingfactor_m106_new.pdf}}
    \end{tabular}
- \caption{2-dimensional distributions of filling factor and spot temperature for the nine accepted IGRINS orders for S1063.
-The median filling factor across these nine orders is $32 \pm 7$\% with a spot temperature of $4000\pm200$ K.
-As the IGRINS spectrum was observed near maximum light, these show a lower limit on the total spot coverage fraction.
-}
+ \caption{2-dimensional distributions of filling factor and spot temperature for the nine accepted IGRINS orders for S1063, including 1000 samples of the emcee chains thinned by a factor of 10.
+Some orders demonstrate a stronger ability to constrain the spot characteristics than others, however all are consistent with the detection of a moderate covering fraction of spots.
+The median filling factor across these nine orders is $32 \pm 7$\% with a spot temperature of $4000\pm200$ K.}
  \label{fig:tspot_fillingfactor3x3}
@@
 
-\item What coverage fraction would we have measured across the rotational phase?
-\end{itemize}
+ \subsection{Comparison to evolutionary models of active stars}
+ \label{sec:model_comparison}
+
+\begin{figure*}[ht]
+    \centering
+    \includegraphics[width=0.45\linewidth]{figures/S1063_GaiaCMD.png}
+    \includegraphics[width=0.45\linewidth]{figures/S1063_2MASS_CMD.png}
+    \caption{On the left is a \textit{Gaia} color-magnitude diagram (CMD) that shows members of M67 (gray points) with SSG S1063 highlighted (red square).
+In comparison, we show SPOTS evolutionary tracks \citep{somers20} for a 1.3 \Msolar\ star with spot covering fractions of 0\%, 17\%, 51\% and 85\%.
+On the right is a similar CMD using photometry from 2MASS.}
+    \label{fig:CMDs}
+\end{figure*}
+
+Current theoretical modeling of active stars take several different approaches, including surface treatments of spots at non-zero temperatures that suppress convective energy transport \citep{somers20}, direct treatments of the interior magnetic field \citep{2013ApJ...779..183F}, and reduced mixing length models with non-emitting spots \citep{2007A&A...472L..17C}.
+
+Here, we compare the photometry of S1063 to spotted SPOTS evolutionary tracks \citep{somers20}.
+We use optical photometry from \textit{Gaia} and near-infrared photometry from 2MASS for this comparison, showing CMDs of M67 members compared to SPOTS tracks in Figure~\ref{fig:CMDs}.
+The optical photometry is most consistent with a SPOTS model with a $\sim50\%$ spot filling factor, slightly higher than the $32\%$ we find from the spectroscopic de-convolution.
+The 2MASS photometry indicates an even larger filling factor, falling in between the 51\% and 85\% SPOTS models.
+We note that while the unspotted SPOTS evolutionary track (black line in Figure~\ref{fig:CMDs}) fits the turnoff of M67 well when using 2MASS photometry, the model has a more extended subgiant branch and redder giant branch compared to the \textit{Gaia} photometry.
+This discrepancy is not resolvable by changing cluster parameters (i.e.
+reddening, distance, turnoff mass, metallicity).
+It may be due to internal model physics (i.e.
+choice of mixing length) or an error introduced when calculating model colors in the Gaia bandpasses.
+Because of this improper calibration, the spot filling factor inferred from comparisons with the \textit{Gaia} photometry may be skewed towards lower spot filling factors.
+This could explain the higher spot filling factor inferred from the 2MASS photometry, where the unspotted models are a better fit to the cluster turnoff.
+
+A summary of the surface and stellar parameters for S1063 are given in Table~\ref{tab:s1063parameters}, comparing our work here with parameters for S1063 determined in \citet{mathieu03}, \citet{leiner17}, and the SPOTS model comparison above.
+The filling factor determined via spectroscopic and photometric methods varies dramatically, with photometric methods finding a larger filling factor than our work here, although different photometric colors combinations suggest different filling factors.
+
+The spectral decomposition technique used here is sensitive to larger spot filling factors \citep{gullysantiago17}, as long as the spots are of sufficient brightness to provide a significant spectral signature.
+We detect a significant spot spectral signature in S1063, but we do not know if we are detecting the spectrum of the umbra or prenumbra.
+Although it is most likely that the penumbra is larger in area and warmer than the umbra for most stars \citep{1981ApJ...250..327V}, suggesting that this technique is more sensitive to constraining the prenumbra filling factor and the prenumbra would dominate the total spot area on the star.
+However, if SSGs have smaller penumbra it is possible this technique would under-sample the total spot coverage on the stellar surface.
+Additionally, any possible wavelength dependence of spot size would also lead to discrepant spot filling factors across photometric and spectroscopic determinations at different wavelengths.
+We note that photometry collected at different epochs can also impact the inferred photometric filling factor, but given our light curve analysis we expect epoch-based filling factor uncertainties to be at most $\sim$20\% in filling factor.
+
+We present further discuss systematic uncertainties that may add to these discrepancies in Section~\ref{sec:uncertainties}, but fully resolving the complexities of photometric and spectroscopic constraining of spot filling factors likely requires careful photometric modeling of a multi-temperature stellar surface, which is beyond the scope of this paper.
 
 \section{Discussion}
+\label{sec:discussion}
+
+The spot coverage fraction determined in this work is consistent with the range of spot coverage seen on RS CVn of 30--40\% from measuring TiO band strength \citep{oneal96, oneal98, oneal04} and Doppler imaging \citep{hackman12}.
+The similar spot coverage fraction on S1063 determined here is further evidence that this sub-subgiant and likely other sub-subgiants have high magnetic activity.
+
+Strong magnetic fields and starspots reduce convective energy transport efficiency, which in turn mutates theoretical evolutionary model tracks from their unspotted/non-magnetic counterparts \citep{2013ApJ...779..183F,somers15,somers15b,somers20}.
+Understanding the physical nature of the magnetic activity and the impact it has on stellar structure and evolution requires comparison of high fidelity observations with these theoretical models.
+An accurate position in the HR diagram position requires determination of the effective temperature ($T_{\textrm{eff}}$) having accounted for spots, as well as the stellar luminosity.
+
+\subsection{Effective temperature of spotted stars}
+The conventional observational interpretation of $T_{\textrm{eff}}$ is difficult to apply to spotted stars, especially stars with variation in the spot covering fraction over time \citep{gullysantiago17}.
+Conventionally, a spectrum can be interpreted as possessing a 1:1 mapping from its appearance to a $T_{\textrm{eff}}$-indexed template, which can be either model-based or observed.
+We...
+
+\citet{leiner17} fit the multi-band spectral energy distribution for S1063 with a single Castelli-Kurucz spectrum \citep{2003IAUS..210P.A20C} and find a best fit $T_{\textrm{eff}}$ of 4500 K.
+Knowing we are dealing with a spotted star, another interpretation is to calculate the surface-averaged $T_{\textrm{eff}}$:
+
+\begin{equation}
+T_{\textrm{eff}}^4 = f_{\textrm{s}} T_{\textrm{s}}^4 + (1 -f_{\textrm{s}}) T_{\textrm{amb}}^4 .
+\end{equation}
+
+where $f_{\textrm{s}}$ is the spot covering fraction, $T_{\textrm{s}}$ is the spot temperature, $T_{\textrm{amb}}$ is the ambient photosphere temperature.
+This single surface-averaged temperature allows for comparisons to one-dimensional stellar evolution models motivated by the surface conditions of the star \citep{somers20}.
+With this method, at the time of the IGRINS observation the $T_{\textrm{eff}}$ of S1063 is $4900\pm100$ K.
+This temperature is inconsistent with the temperature determined via SED fitting in \citet{leiner17}, indicative of the discrepancies between the spectral and photometric constraints outlined in Section~\ref{sec:model_comparison}, although we note that the previous temperature of 4500 K is between the measured spot and ambient photosphere temperatures determined in this work.
+
+Stars such as S1063, however, have observed surface-averaged $T_{\textrm{eff}}$ values that vary based on the spot covering fraction at the time of observation.
+We know from the variable light curve that stars such as S1063 have differing spot covering fractions on opposite observable hemispheres of the star causing optical variability.
+For example, at the 4-year light curve maximum when S1063 had approximately a 20\% spot covering fraction the surface-averaged $T_{\textrm{eff}}$ for the observed hemisphere of the star would be 5000 K.
+At the light curve minimum with a 45\% spot covering fraction the surface-averaged $T_{\textrm{eff}}$ for the observed hemisphere would only be 4700 K.
+
+The true surface-averaged $T_{\textrm{eff}}$ includes the entire stellar surface.
+This should be constant over a thermal timescale, including the four-year time frame in Figure~\ref{fig:lightcurve}, as is demonstrated by the constant mean flux level of 89.5\% compared to the maximum global flux.
+Observationally constraining the surface-averaged $T_{\textrm{eff}}$ requires either multi-epoch spectrum observations at both the light curve maximum and minimum, or a single observation at the mean flux level.
+The date of the IGRINS observation corresponds to a global flux level of 0.912, suggesting that observed spot coverage is a reasonable proxy for the mean state of S1063.
+Therefore, we conclude that the total surface-averaged $T_{\textrm{eff}}$ of S1063 is consistent with the observed surface-averaged $T_{\textrm{eff}}$ of $4900\pm100$ K.
+We stress, however, that determining a single $T_{\textrm{eff}}$ value for spotted stars is fraught at best, and makes model comparisons exceedingly nuanced.
+
+\subsection{Radius of S1063}
+
+The radius of S1063 gets encoded into our data streams in three ways.
+Kinematically, radius affects $v\sin{i}$, photometrically radius affects the SED and HR diagrams, and gravitationally radius affects the surface gravity $\log{g}$.
+Our weak constraints on surface gravity cannot meaningfully inform the radius.
+The SED-based photometric results suggest a radius of $R_{\star} = 3.7-4.6 R_\odot$, implausibly large compared to even the most egregiously spotted radii inflation models.
+The kinematic avenue therefore seems most promising and ostensibly least subject to astrophysical biases, so it is worth dissecting in some detail here.
+The stellar radius $R_{\star}$ contributes to the magnitude of the equatorial velocity $v_{\mathrm{eq}}$ for a given rotation rate and projected stellar inclination angle $i$:
+\begin{eqnarray}
+  v \sin{i} = \frac{2\pi R_{\star}}{P_{\mathrm{rot}}} \sin{i} \\
+  R_{\star} \sin{i} = \frac{v \sin{i} \cdot P_{\mathrm{rot}}}{2 \pi} \\
+\end{eqnarray}
+
+Our \texttt{Starfish}/IGRINS-derived $v\sin{i}=XX$ and \texttt{celerite}/K2 derived period $P_{\mathrm{rot}}=XX$ constrain $R\sin{i} = XX$, with a formal statistical uncertainty of XX.
+At first sight, $R_{\star}$ is most likely $>XX R_{\odot}$, since $\sin{i}$ is only ever less than unity.
+The combined $XX\%$ uncertainty in $R\sin{i}$ and the photometrically-derived radius uncertainty of $XX\%$ yields coarse agreement/disagreement with these two disparately-sourced estimates.
+At least three sources of unaccounted-for astrophysical uncertainties can conceivably bias the derived $v\sin{i}$ for heavily spotted sub-giants.
+The unknown limb-darkening prescription, the micro- or macro- turbulent velocity, and the latitudinal segregation of starspots.
+On the other hand, the period can be systematically biased in three significant ways: differential rotation combined with latitudinal starspot segregation, starspot evolution on timescales comparable to the rotation period, and aliasing from regularly-spaced longitudinal surface symmetries.
+
+\natalienote{
+-Rsini can also be used as a model comparison, but this Rsini is large (we think 3.7-4.6 Rsun) compared to what has been found in previous SED fits (Leiner2017)}
+
+%{f the with direct predictions for spot covering fractions of photometrically emitting spots.
+A preliminary comparison to S1063 is included in \citet{somers20}, but using a lower $T_{\textrm{eff}}$ as found in \citet{leiner17}.
+However, \citet{somers20} uses the surface-averaged temperature to define $T_{\textrm{eff}}$ (see Eq 1 in Somers20), so the $T_{\textrm{eff}}$ determined in this work is a more appropriate comparison.
+
+%-Updated temp brings these results more in line with the spot coverage implied by SPOTS models, assuming the luminosity is the same.
+SPOTS models are maybe still a little bit too spotted - close to the 51\% track compared to 32\% that we measure, but our uncertainties are large and we have systematic errors that are unaccounted for.
+
+%-Now there is tension with the colors of the SPOTS models, but colors of spots are weird.
+The lower spot coverage models predict bluer colors than observed.
+Perhaps some chromospheric component?
+This is probably fine.
+
+%-Perhaps demonstrates a need for a dual modeling approach of surface treatment with internal structure changes and comparing against a larger sample of stars
+
+\subsection{Additional sources of systematic uncertainty}
+\label{sec:uncertainties}
+We have posited a two-temperature surface two derive our estimates for filling factors and effective temperature.
+In reality, this star---and most active stars more generally---must exhibit a range of apparent surface contrasts attributable to umbra, penumbra, faculae, chromospheric emission, and other phenomena unaccounted for in this work \citep{berdyugina05, 2009A&ARv..17..251S}.
+
+Our near-IR spectral technique is most sensitive to detecting a ``sweet-spot'' in starspot contrast: cool enough to exhibit a spectrum that is qualitatively distinct from the ambient photosphere, but not so cool as to possess vanishing specific intensity.
+So for example, our technique might readily perceive the penumbra of the starspot, while ignoring the much cooler and darker umbra flux contribution \citep{1981ApJ...250..327V}.
+This umbral neglect would lead our technique to systematically underestimate the total starspot coverage, rendering our claimed estimate as a lower limit.
+On the other hand, faculae and plage act to add a hotter-than-average surface component.
+The interpretation of our two component mixture model becomes confounded if we posit the coexistence of three components: spot, ambient, and faculae \citep{1998A&A...329..747S}.
+The extent of the confounding depends on the detailed properties of such conceivable faculae, but in short faculae may act to either increase or decrease starspot coverage estimates insofar as they alter the ambient photosphere temperature that we assign \citep{2019AJ....157...11W}.
+The existence of large and hot faculae can be ruled out to some extent by the fact that they would dominate the temperature determination in visible wavelength spectra.
+The adequate agreement temperature derived from visible wavelength spectra of S1063 \citep{mathieu03} and the our near-IR derived ambient photosphere temperature suggests that faculae may be negligible.
+Chromospheric emission should mostly perturb individual lines that are known to be chromospherically active, such as Hydrogen lines.
+Our IGRINS-based technique analyzed the majority of the $H$-band with whole-spectrum fitting, where such chromospherically active lines would have negligible impact.
+
+Our reliance on \texttt{PHOENIX} synthetic spectra adds a model-dependent systematic to our entire approach.
+The unavailability of a large number of spot-free high-precision high-resolution template spectra across all of $H$-band demands the use of these models in order to compare to IGRINS data.
+The ability of such synthetic spectra to resemble starspots remains an unknown.
+We can get some clue of the performance of the synthetic spectra by examining the fit residuals, evinced in this work by comparing the purple two-component composite spectrum to the gray IGRINS spectrum in Figure \ref{fig:IGRINS_spectra3x3}.
+The IGRINS spectra exhibit absorption lines where no such line is predicted, and vice versa: lines absent from the IGRINS spectra that our composite model would predict.
+To some extent, the imperfect fitting of the synthetic spectra to our IGRINS spectra must be causing a systematic uncertainty.
+The Gaussian process ``Global Kernels'' employed in \texttt{Starfish} account for some degree of correlated data-model residual mismatching.
+We did not employ the ``Local kernels'', which cause a 30 K systematic bias in comparable quality spectra of WASP-14 also compared to the \texttt{PHOENIX} models \citet{czekala15}.
+We therefore assign at least a 30 K systematic bias in our temperature estimates based on the prospect of individual line outliers polluting our fit residuals.
+We conseassign a coarse estimate of 100--200 K to so-called ``label noise'', associated with the alignment of a best fit \texttt{PHOENIX}-provided $T_{\text{eff}}$ labels and an unseen ground-truth label for the ``True'' temperature of the spots.
+New studies of the Sun based on DKIST may offer the best future avenue for testing such assumptions and refining the ability to distinguish starspot emission from ambient photosphere.
 
@@
 
-The spot coverage fraction measured here is consistent with the range of spot coverage seen on RS CVn of 30--40\% from measuring TiO band strength \citep{oneal96, oneal98, oneal04} and Doppler imaging \citep{hackman12}.
-The similar spot coverage fraction on S1063 is further evidence that this sub-subgiant and likely other sub-subgiants have high magnetic activity.
-
-In the absence of this spectral inference technique one could assume the \textit{K2} C5 light curve maximum corresponded to zero spot presence with the light curve amplitude change implying a maximum spot coverage of 7--10\%.
+%In the absence of this spectral inference technique one could assume the \textit{K2} C5 light curve maximum corresponded to zero spot presence with the light curve amplitude change implying a maximum spot coverage of 7--10\%.
 This provides a fundamentally different view of the star ...
 
-\begin{itemize}
-\item Spot coverage is consistent with formation theories
-\item Conceivable geometries with circumpolar active longitudes, or migrating active latitudes
-\item Biases introduced if we assume a spot-free model
-\begin{itemize}
-  \item Where does subsub sit in a new HR diagram? (new Somers models)
-  \item *bonus* FIGURE: PMS HR diagram with new Somers tracks
-  \item Spot impact on SED fits
-\end{itemize}
-\end{itemize}
+%\begin{itemize}
+%\item Conceivable geometries with circumpolar active longitudes, or migrating active latitudes
+%\item Biases introduced if we assume a spot-free model
+%\begin{itemize}
+%  \item Where does subsub sit in a new HR diagram? (new Somers models)
+%  \item *bonus* FIGURE: PMS HR diagram with new Somers tracks
+%  \item Spot impact on SED fits
+%\end{itemize}
+%\end{itemize}
 
 \section{Conclusions}
+\label{sec:conclusions}
 
@@
 
-\acknowledgements
+\begin{acknowledgements}
 
 %ADS
-This research has made use of NASA’s Astrophysics Data System.
+This research has made use of the NASA Astrophysics Data System.
 %IGRINS
@@
 
-{\it Facilities:} \facility{Smith (IGRINS)}, \facility{ASAS}, \facility{Gaia}
+\end{acknowledgements}
 
-{\it Software: }
- \project{pandas} \citep{mckinney10},
- \project{emcee} \citep{foreman13},
- \project{matplotlib} \citep{hunter07},
- \project{numpy} \citep{vanderwalt11},
- \project{scipy} \citep{jones01},
- \project{ipython} \citep{perez07},
- \project{gatspy} \citep{JakeVanderplas2015},
- \project{starfish} \citep{czekala15},
- \project{seaborn} \citep{waskom14}
-%\software{%
-% \project{pandas} \citep{mckinney10}
-%    \project{emcee} \citep{foreman13},
-% \project{matplotlib} \citep{hunter07},
-% \project{numpy} \citep{vanderwalt11},
-% \project{scipy} \citep{jones01},
-% \project{ipython} \citep{perez07},
-% \project{gatspy} \citep{JakeVanderplas2015},
-% \project{starfish} \citep{czekala15}}.
+\facilities{Smith (IGRINS), Gaia, ASAS}
+
+\software{  pandas \citep{mckinney10},
+  emcee \citep{foreman13},
+  matplotlib \citep{hunter07},
+  numpy \citep{2020NumPy-Array},
+  scipy \citep{2020SciPy-NMeth},
+  ipython \citep{perez07},
+  starfish \citep{czekala15},
+  seaborn \citep{waskom14},
+  lightkurve \citep{geert_barentsen_2019_2565212}}
 
@@
 
-\bibliographystyle{apj}
 \bibliography{ms}

### 2021-05-13 document/ms.tex
:truck: Sync the paper draft from Overleaf, add latexdiff to track changes

@@
-\documentclass[modern,trackchanges]{aastex631}
+\documentclass[trackchanges]{aastex631}
 \bibliographystyle{aasjournal}
@@
 \newcommand{\Msolar}{M$_{\odot}$}
+\newcommand{\Rsun}{R$_{\odot}$}
 
 \begin{document}
-\shorttitle{Starspots on Sub-subgiant S1063}
-\shortauthors{TBD}
+\shorttitle{Starspot Coverage on Sub-subgiant S1063}
+\shortauthors{Gosnell et al.}
 
-\title{Starspots as the Cause of Underluminosity for M67 Sub-Subgiant S1063 }
+\title{Constraining the Starspot Filling Factor of Active M67 Sub-Subgiant S1063}
 
-\author{TBD}
-\affiliation{TBD}
+\author{Natalie M. Gosnell}
+\affiliation{Colorado College, Department of Physics, 14 E. Cache La Poudre St, Colorado Springs, CO 80903}
+\author{Michael A. Gully-Santiago}
+\affiliation{University of Texas at Austin}
+\author{Emily M. Leiner}
+\affiliation{CIERA, Northwestern}
+\author{Benjamin Tofflemire}
+\affiliation{University of Texas at Austin}
 
@@
 \section{Introduction}\label{sec:intro}
-\emilynote{This is a note from Emily.}
-\natalienote{This is a note from Natalie.}
-\gullynote{This is a note from Gully.}
 Recent studies illuminate the important role stellar magnetic activity plays in stellar structure.
 This impact of stellar activity and magnetic fields is seen throughout the Hertzsprung-Russell (HR) Diagram.
-For example, by biasing isochronal ages of young clusters \citep{somers15}, inflating radii of active M-dwarfs \citep{2010AJ....140.1158T,2010ApJ...718..502M,2019MNRAS.483.1125J}, causing redder multiple turnoffs in stellar clusters \citep{2009MNRAS.398L..11B,2019ApJ...876..113S}, and altering the pulsation modes of red giants \citep{2020A&A...639A..63G}.
+For example, by biasing isochronal ages of young clusters \citep{somers15}, inflating radii of active M-dwarfs \citep{2010AJ....140.1158T,2010ApJ...718..502M,2019MNRAS.483.1125J}, causing multiple redder turnoffs in stellar clusters \citep{2009MNRAS.398L..11B,2019ApJ...876..113S}, and altering the pulsation modes of red giants \citep{2020A&A...639A..63G}.
 As our ability to probe the detailed physics of stellar evolution continues to improve we must grapple with the complexities of stellar structure diverging from simpler theoretical expectations due to magnetic activity, which requires careful observational studies of magnetically active systems to test magnetic stellar models.
@@
 
-Ideally we would directly measure the radius and internal magnetic field to calibrate how the star inflates as a function of convective efficiency, and the positions of SSGs could be explained.
-In practice these quantities are difficult to measure at the precision required to demonstration inflation on single magnetically active systems, though aggregate populations have shown evidence for magnetic inflation \citep{2018AJ....155..225K,2018MNRAS.476.3245J}.
-Starspots have become a rich observational proxy for gauging the evolutionary state of stars that may be magnetically inflated, without needing to estimate magnetic field strengths.
+Ideally, we would directly measure the stellar radius and internal magnetic field strength to calibrate how the star inflates as a function of convective efficiency, thereby explaining the CMD positions of SSGs.
+In practice, these quantities are difficult or impossible to measure at the precision required to demonstrate inflation for individual magnetically active systems, though aggregate populations have shown evidence for magnetic inflation \citep{2018AJ....155..225K,2018MNRAS.476.3245J}.
+Starspots have become a rich observational proxy for gauging the evolutionary state of stars that may be magnetically inflated without needing to estimate magnetic field strengths.
 
-The portion of the stellar surface covered with starspots is related to the amount of magnetic activity.
+%The portion of the stellar surface covered with starspots is related to the amount of magnetic activity.
 The mere existence of starspot modulation betrays magnetic activity in stars.
@@
 A full accounting of starspots requires careful consideration of geometrical degeneracies.
-Monochromatic light curves can indicate spotted stars \citep{2014ApJS..211...24M} but can only provide a lower limit on the differential spot coverage between the most and least spotted hemispheres.
+Monochromatic light curves can indicate spotted stars \citep{2014ApJS..211...24M} but only provide a lower limit on the differential spot coverage between the most and least spotted hemispheres.
 Longitudinally symmetric starspot geometries evade detection in monochromatic lightcurves alone \citep{2019AJ....157...64L}.
+Disk-integrated covering fractions can be obtained from TiO band observations \citep{oneal96,fang2016,2019AJ....158..101M}.
 Measuring the spot configuration typically requires Doppler imaging or interferometry studies restricted to only the brightest and most nearby sources \citep{roettenbacher16}.
-Disk-integrated covering fractions can be obtained from TiO band observations \citep{oneal96,fang2016,2019AJ....158..101M}.
 Testing the next era of stellar activity models requires precision methodologies to measure spot-covering fractions of a larger number of targets, including sub-subgiants.
@@
 The resulting spot characterization can be used to anchor light curve information, providing insight into the overall stellar activity level and constraining the long-term spot coverage \citep{neff95}.
-This strategy only requires high-resolution echelle spectroscopy and photometric monitoring, dramatically increasing the number of sources for which we can observationally constrain spot-covering fractions.
+This strategy only requires high-resolution near-IR echelle spectroscopy and photometric monitoring, dramatically increasing the number of sources for which we can observationally constrain spot-covering fractions.
 
-In this paper we demonstrate the power of this methodology by focusing on a single sub-subgiant system, S1063 in the open cluster M67.
-This system is a prototypical sub-subgiant star, with an single-lined spectroscopic orbital period of 18.4 days \citep{geller17}, an X-ray luminosity of $1.3\times10^{31}$ erg s$^{-1}$ \citep{vandenberg99}, and a variable light curve in \textit{K2} and ASAS-SN (Section~\ref{sec:K2lightcurve}).
-\emph{Gaia} DR2 astrometry \citep{2016A&A...595A...1G, 2018A&A...616A...1G} indicates a parallax ($1.17\pm0.025 \;$mas) and proper motion for S1063 (\emph{Gaia} DR2 604921030968952832) consistent with other M67 members, and approaching 100\% membership probability \citep{2018ApJ...869....9G}.
+In this paper we demonstrate the power of this methodology by focusing on a single SSG system, S1063 in the open cluster M67.
+This system is a prototypical SSG, with an single-lined spectroscopic orbital period of 18.4 days \citep{geller17}, an X-ray luminosity of $1.3\times10^{31}$ erg s$^{-1}$ \citep{vandenberg99}, and a variable light curve in \textit{K2} and ASAS-SN (Section~\ref{sec:K2lightcurve}).
+\emph{Gaia} DR2 astrometry \citep{2016A&A...595A...1G, 2018A&A...616A...1G} indicates a parallax ($1.17\pm0.025 \;$mas) and proper motion for S1063 (\emph{Gaia} DR2 604921030968952832) consistent with other M67 members  approaching 100\% membership probability \citep{2018ApJ...869....9G}.
 We present our observational data products in Section~\ref{sec:observations} and subsequent analysis in Section~\ref{sec:analysis}.
@@
 We retrieved All-Sky Automated Survey for Supernovae \citep[ASAS-SN;][]{shappee14} lightcurves from the Sky Portal \citep{2017PASP..129j4502K}.
-The lightcurves contained 758 epochs of $V-$ band photometry spanning 2013-2018 (source ASASSN-V J085113.44+115139.7) and 823 epochs of $g-$band photometry spanning mid-2017--2018.
+The lightcurves contained 758 epochs of $V$-band photometry spanning 2013-2018 (source ASASSN-V J085113.44+115139.7) and 823 epochs of $g$-band photometry spanning mid-2017--2018.
 The $\sim8''$ ASAS-SN pixels may cause some PSF blending of the nearby-albeit-fainter source seen at the bottom of Figure \ref{fig:imaging}.
@@
 Campaigns 5 and 18 were observed on the same detector channel while a different detector channel was used for Campaign 16, therefore these offsets are not a significant measure of detector degradation across campaigns.
+We use a Lomb-Scargle periodogram on each campaign independently and recover the same dominant period of 23.5 days in all three campaigns.
+The phase-folded light curves and periodograms are shown in Figure~\ref{fig:periodogram}.
 
@@
 The average period associated with maximum power across all three campaigns is P = 23.5 days.
-\deleted{The phased light curves indicate the most spotted hemisphere occurred around a rotation phase of 0.4 during C5 (shown in blue) but shifted to a rotation phase of approximately 0.7 in C16 and C18 (shown in purple and green, respectively).
-This is suggestive of the spot morphology of S1063 shifting over this 2.5-year period.} \explain{How precisely do we have to know the period to confidently detect a phase change?} }
+}
     \label{fig:periodogram}
@@
 \emph{K2} Campaigns 5, 16, and 18 (densely-sampled red points) and ASAS-SN $V-$band (coarsely-sampled gray points) show approximately $5-17\%$ peak-to-valley photometric variations indicative of secularly evolving surface coverage of starspots.
-The orange line shows a damped, driven harmonic oscillator \emph{celerit\`e} model \citep{2017AJ....154..220F} trained on the K2 and ASAS-SN data, and then applied to the noisy ASAS-SN points, with a standard-error uncertainty band in shaded orange.
-The vertical blue bar in mid-2015 indicates the epoch of IGRINS data acquisition, which shows an approximate $8\%$ flux deficit compared to global maximum flux in early 2017.}
+The orange line shows a damped, driven harmonic oscillator \texttt{celerit\`e} model \citep{2017AJ....154..220F} trained on the \emph{K2} and ASAS-SN data, and then applied to the noisy ASAS-SN points.
+A standard-error uncertainty band is shown in shaded orange.
+The vertical blue bar in mid-2015 indicates the epoch of IGRINS data acquisition, which shows an approximate $8\%$ flux deficit compared to the global maximum flux in early 2017.}
 \label{fig:lightcurve}
@@
 
-Constraining starspot covering fraction for stars such as S1063 requires a careful combination of light curve interpretation and spectral analysis, using spectral decomposition tools such as \texttt{Starfish} \citep{czekala15} to benchmark epochs of starspot coverage in long-term photometric monitoring.
+Constraining starspot covering fraction for stars such as S1063 requires a careful combination of light curve interpretation and spectral analysis using spectral decomposition tools such as \texttt{Starfish} \citep{czekala15} to benchmark epochs of starspot coverage in long-term photometric monitoring.
 
 \subsection{Joint modeling of ASAS-SN and \emph{K2} Lightcurves}
-In order to characterize the long-term behavior of S1063 we jointly modeled the ASAS-SN and K2 lightcurves as a damped, driven Simple Harmonic Oscillator (SHO) Gaussian Process (GP) with \texttt{celerit\`e} \citep{2017AJ....154..220F}, revealing periodicity and secular changes in flux levels over a multi-year timeframe.
+Characterizing the long-term behavior of S1063 requires connecting and comparing photometry information from different missions, in this case ASAS-SN and \emph{K2}.
+To accomplish this task we jointly modeled the ASAS-SN and \emph{K2} lightcurves as a damped, driven Simple Harmonic Oscillator (SHO) Gaussian Process (GP) with \texttt{celerit\`e} \citep{2017AJ....154..220F}, revealing periodicity and secular changes in flux levels over a multi-year timeframe.
 This strategy offers flexibility to cope with windowing effects and the high dynamic range in data sampling and quality available across ASAS-SN and \emph{K2}.
@@
 
- We tuned a two-period GP model, with the harmonic component possessing roughly half the period $P_H\sim12.5\;\mathrm{d}$ of the fundamental period $P_0=23.5\;\mathrm{d}$.
+We tuned a two-period GP model with the harmonic component possessing roughly half the period $P_H\sim12.5\;\mathrm{d}$ of the fundamental period $P_0=23.5\;\mathrm{d}$.
 The harmonic overtone frequency can be seen by eye in Figure \ref{fig:lightcurve}, as the \emph{K2} lightcurves appear more complex than a pure sine wave.
-Each periodic GP term also possessed correlation amplitude and SHO quality factor which we consider nuisance parameters for the purpose of this fitting.
+Each periodic GP term also possessed a correlation amplitude and SHO quality factor which we consider nuisance parameters for the purpose of this fitting.
 We found broadly consistent values when \emph{K2} lightcurves were fitted on a per-campaign basis.
@@
 Finally, we evaluated the trained GP model at the location of the ASAS-SN photometry, and at windows lacking data altogether.
-This trend appears in Figure \ref{fig:lightcurve} as the dark orange line with an orange standard confidence region.
-This trendline guides the eye to see broad secular changes to the amplitude encoded in the noisy ASAS-SN data, with a global maximum peak-to-valley amplitude of 17\% occurring near 2017 January, and global minimum peak-to-valley of 3\% occurring near to the time of the IGRINS measurement.
+This trend appears in Figure \ref{fig:lightcurve} as the dark orange line with an orange shaded standard confidence region.
+This trendline guides the eye to see broad secular changes to the amplitude encoded in the noisy ASAS-SN data, with a global maximum peak-to-valley amplitude of 17\% occurring near 2017 January, and global minimum peak-to-valley of 3\% occurring shortly before the IGRINS measurement.
 
@@
 Even a single epoch of IGRINS observations provides an opportunity to constrain the spot covering fraction of S1063 that can be used as a benchmark for interpreting the long-term flux variation apparent in Figure~\ref{fig:lightcurve}.
-We performed a two-temperature probabilistic spectral decomposition on the IGRINS $H-$band spectrum.
+We performed a two-temperature probabilistic spectral decomposition on the IGRINS $H$-band spectrum.
 We applied the spectral inference framework \texttt{Starfish} \citep{czekala15}, recently extended to support composite spectra comprised of mixtures of two distinct photospheric components \citep{gullysantiago17}.
@@
 
-We employed the \texttt{PHOENIX} precomputed synthetic model grid \citep{husser13} with grid ranges of $3000 < T_{\mathrm{eff}} \; (\textrm{K}) < 5300 $, $3 < \log{g \;(\textrm{cm/s})}  < 4 $, and $ -0.5 <  [\mathrm{Fe}/\mathrm{H}] <0.5$.
+We employed the \texttt{PHOENIX} pre-computed synthetic model grid \citep{husser13} with grid ranges of $3000 < T_{\mathrm{eff}} \; (\textrm{K}) < 5300 $, $3 < \log{g \;(\textrm{cm/s})}  < 4 $, and $ -0.5 <  [\mathrm{Fe}/\mathrm{H}] <0.5$.
 We trained the spectral emulator \citep{czekala15} on this grid range, while preserving the absolute model mean fluxes to enable accurate flux comparison between two spectra of disparate characteristic temperatures.
@@
 We employed \texttt{emcee} \citep{foreman13} with 5000 samples and 40 walkers, spot-checking the MCMC chains for signatures of steady-state posterior probability distributions suggestive of convergence.
-Some orders did not pass our convergence criteria, usually due to poor initialization of nuisance parameters or overfitting.
+Some orders did not pass our convergence criteria, usually due to poor initialization of nuisance parameters or over-fitting.
 Furthermore, the radial velocity $v_z$ and projected rotational broadening $v\sin{i}$ were spot-checked to verify both consistent values among spectral orders as well as posterior distributions indicative of information-rich spectral orders.
-Some relatively feature-free spectral orders such as $m=103$ did not offer enough constraining power to derive meaningful results in the face of multiple sources of degeneracy.
+Some relatively feature-free spectral orders did not offer enough constraining power to derive meaningful results in the face of multiple sources of degeneracy.
 Collectively, these discrepant or uninformative spectral orders were removed from future analysis, yielding a total of nine preserved spectral orders, shown in Figure \ref{fig:IGRINS_spectra3x3}.
@@
 \label{sec:starfishresults}
-Using the \texttt{Starfish} spectral inference results we investigate the joint constraints on spot temperature and filling factor, marginalized over all other uncertainties in stellar properties and fitting hyper-parameters (such as Starfish-derived Gaussian Process correlation length and amplitude and continuum fitting polynomials).
+Using the \texttt{Starfish} spectral inference results we investigate the joint constraints on spot temperature and filling factor, marginalized over all other uncertainties in stellar properties and fitting hyper-parameters (such as \texttt{Starfish}-derived Gaussian Process correlation length and amplitude and continuum fitting polynomials).
 In Figure~\ref{fig:tspot_fillingfactor3x3} we show 2-dimensional posterior distributions of filling factor and spot temperature of the last 1000 samples thinned by a factor of 10 from all 40 \texttt{emcee} walkers for the nine orders with accepted fits.
@@
 Across all nine orders, the median filling factor value is 32\% with a standard deviation of 7\%, with a corresponding spot temperature of $4000 \pm 200$ K.
-The ambient photosphere temperature associated with this spot signature varies from order-to-order and is broadly consistent with a range of temperatures between 5000 K and 5300 K, with a best guess value of $5200$ K.
-These values are broadly consistent with a spectroscopic temperature of 5000 K determined by \citet{mathieu03} determined from visible-wavelength spectra.
+The ambient photosphere temperature associated with this spot signature varies from order-to-order and is broadly consistent with a range of temperatures between 5000 K and 5300 K, with a best guess value of 5200 K.
+These values are broadly consistent with a spectroscopic temperature of 5000 K for S1063 determined by \citet{mathieu03} determined from visible-wavelength spectra.
 Visible wavelength spectra principally perceive the ambient photosphere, due to the near-zero starspot contrast at those wavelengths.
@@
 \subsubsection{Light curve interpretation}
-The ASAS-SN and \textit{K2} C5 data of S1063 (Figure~\ref{fig:lightcurve}) indicate that the IGRINS observation was coincidentally acquired near its modest local maximum at an overall flux level of 91.2\%.
+The ASAS-SN and \textit{K2} Campaign 5 data of S1063 (Figure~\ref{fig:lightcurve}) indicate that the IGRINS observation was coincidentally acquired near its modest local maximum at an overall flux level of 91.2\%.
 This is close to the overall 89.5\% mean flux level, where the 100\% flux level is equal to the global maximum over the four-year period covered by ASAS-SN and \textit{K2}.
@@
 The presence of starspots at the light curve maximum acts as a starspot baseline for interpreting the lightcurve.
-Over the 4-years shown in Figure~\ref{fig:lightcurve}, the average flux variation is approximately 5\%, corresponding to an average spot covering fraction variation from each observed hemisphere of $\pm$8\%.
+Over the four years shown in Figure~\ref{fig:lightcurve}, the average flux variation is approximately 5\%, corresponding to an average spot covering fraction variation from each observed hemisphere of $\pm$8\%.
 The lightcurve exhibits a global flux minimum 10\% lower than the flux at the time of the IGRINS observation, requiring a spot filling factor close to 45\% on the projected hemisphere at that time.
@@
 These numbers possess formal uncertainties in the few percent range, and additional uncertainties from our reliance on spectral models.
-But broadly speaking, our result is firm under our assumptions--- S1063 has a large persistent starspot population that ebbs and flows in its longitudinal symmetry, resulting in variation in the peak-to-valley modulation, but always possesses an approximately 30\% spot covering fraction.
+But broadly speaking, our result is firm under our assumptions --- S1063 has a large persistent starspot population that ebbs and flows in its longitudinal symmetry, resulting in variation in the peak-to-valley modulation, but always possesses an approximately 30\% spot covering fraction.
 
@@
 \multicolumn{3}{l}{\textit{Spectroscopic Constraints:}}  \\
-\phantom{EEE} & This work     & $4000\pm200$  & $32\pm7$    & 5200 &   3.7--4.6     \\
+\phantom{EEE} & This work     & $4000\pm200$  & $32\pm7$    & 5200 &   3.7--4.6$^{a}$     \\
 & \citet{mathieu03} &  ...    &  ...    &     5000    &  2.4  \\
 \multicolumn{3}{l}{\textit{Photometric Constraints:}} \\
-& SPOTS models$^{a}$  &      &  50--80    &         &        \\
-& \citet{leiner17} & ... & ... & 4500$^\textrm{b}$ & 2.8--3.1 \\
-& & 3500$^\textrm{c}$ & 40 & 4750 & 3.4 \\
+& Gaia SPOTS models$^{b}$  &   4100   &  51  &   5100  &   3.0  \\
+& 2MASS SPOTS models &   4200   & 85    &   5300  &    3.1    \\
+& \citet{leiner17} & ... & ... & 4500$^{c}$ & 2.8--3.1 \\
+& & 3500$^{d}$ & 40 & 4750 & 3.4 \\
 \hline
-\multicolumn{6}{l}{$^{a}$Section~\ref{sec:model_comparison}, from \citet{somers20}.} \\
-\multicolumn{6}{l}{$^{b}$Unspotted model.} \\
-\multicolumn{6}{l}{$^{c}$Model assuming 40\% spot coverage with a spot temperature contrast of $\sim$1000 K.}
+\multicolumn{6}{l}{$^{a}$$R \sin i$, determined from $v\sin i$, see Section~\ref{sec:radius}} \\
+\multicolumn{6}{l}{$^{b}$Section~\ref{sec:model_comparison}, from \citet{somers20}.} \\
+\multicolumn{6}{l}{$^{c}$Unspotted model.} \\
+\multicolumn{6}{l}{$^{d}$Model assuming 40\% spot coverage with a spot temperature contrast of $\sim$1000 K.}
 \end{tabular}
 \end{table}
-
-%text from Leiner et al.
-2017: Similarly, adding a spot to 13008 changes the best-fit parameters to 4750 K and 3.4 RSun, closer to the 5000 K spectroscopic temperature (Mathieu et al.
-2003).
---is this also at 40% spot covering fraction like 15028 in the previous paragraph?
 
@@
     \caption{On the left is a \textit{Gaia} color-magnitude diagram (CMD) that shows members of M67 (gray points) with SSG S1063 highlighted (red square).
-In comparison, we show SPOTS evolutionary tracks \citep{somers20} for a 1.3 \Msolar\ star with spot covering fractions of 0\%, 17\%, 51\% and 85\%.
+In comparison, we show SPOTS evolutionary tracks \citep{somers20} for a 1.3 \Msolar\ star (black lines).
+The shaded blue area between the tracks indicates the region occupied by stars with spot covering fractions between 0\% and 85\% according to the SPOTS models.
 On the right is a similar CMD using photometry from 2MASS.}
@@
 Current theoretical modeling of active stars take several different approaches, including surface treatments of spots at non-zero temperatures that suppress convective energy transport \citep{somers20}, direct treatments of the interior magnetic field \citep{2013ApJ...779..183F}, and reduced mixing length models with non-emitting spots \citep{2007A&A...472L..17C}.
+Comparing observationally-constrained spot filling-factors with those from theoretical predictions can highlight current gaps in our knowledge, and therefore direct future studies.
 
 Here, we compare the photometry of S1063 to spotted SPOTS evolutionary tracks \citep{somers20}.
-We use optical photometry from \textit{Gaia} and near-infrared photometry from 2MASS for this comparison, showing CMDs of M67 members compared to SPOTS tracks in Figure~\ref{fig:CMDs}.
-The optical photometry is most consistent with a SPOTS model with a $\sim50\%$ spot filling factor, slightly higher than the $32\%$ we find from the spectroscopic de-convolution.
+SPOTS models assume the presence of star spots inhibits local flux that must escape through ambient (non-spotted) regions of the stellar surface.
+To determine photometric conversions from the stellar structure models, all SPOTS evolutionary tracks adopt a two-temperature surface with a fixed ratio of spot to ambient temperature of 0.8.
+We use optical photometry from \textit{Gaia} and near-infrared photometry from 2MASS for this comparison, showing CMDs of M67 members compared to the shaded region in the each CMD populated by SPOTS tracks in Figure~\ref{fig:CMDs}.
+As expected, spotted sub-giant models appear redder and fainter than the sub-giant branch in both CMDs.
+We also show the unspotted SPOTS evolutionary track in each CMD as a black solid line.
+This unspotted model fits the typical subgiant branch of M67 in the 2MASS CMD, however this is not true when using Gaia photometry.
+In the Gaia CMD the unspotted SPOTS model has a more extended subgiant branch and redder giant branch than observed in the cluster.
+This discrepancy is not resolvable by changing cluster parameters (i.e.
+reddening, distance, turnoff mass, metallicity).
+It may be due to internal model physics (i.e.
+choice of mixing length) or an error introduced when calculating model colors in the Gaia bandpasses.
+
+Photometry for S1063 from both Gaia and 2MASS is roughly consistent with the region populated by SPOTS evolutionary tracks.
+Generally, the spot covering fraction adopted from this model comparison would result in larger spot filling factors of approximately 50--85\%, depending on the photometry used, compared to the $32\pm7$\% filling factor found in this work.
+Another photometric comparison using a two-temperature SED fit of S1063 \citep{leiner17} finds a spot filling factor of 40\%, which is also in moderate disagreement with our results.
+
+%The optical photometry is most consistent with a SPOTS model with a $\sim50\%$ spot filling factor, slightly higher than the $32\%$ we find from the spectroscopic deconvolution.
 The 2MASS photometry indicates an even larger filling factor, falling in between the 51\% and 85\% SPOTS models.
@@
 choice of mixing length) or an error introduced when calculating model colors in the Gaia bandpasses.
-Because of this improper calibration, the spot filling factor inferred from comparisons with the \textit{Gaia} photometry may be skewed towards lower spot filling factors.
+Due to this improper calibration, the spot filling factor inferred from comparisons with the \textit{Gaia} photometry may be skewed towards lower spot filling factors.
 This could explain the higher spot filling factor inferred from the 2MASS photometry, where the unspotted models are a better fit to the cluster turnoff.
 
+We believe that some of the discrepancy between our results and those predicted by the SPOTS models may be due to limitations of the SPOTS models as diagnostic tools for single sources.
+However, observational biases may also impact the filling factors determined through spectroscopic and photometric methods.
+The spectral decomposition technique used here is sensitive to larger spot filling factors \citep{gullysantiago17}, as long as the spots are of sufficient brightness to provide a significant spectral signature.
+We do detect a significant spot spectral signature in S1063, but we do not know if we are detecting the spectrum of the umbra or prenumbra.
+It is most likely that the penumbra is larger in area and warmer than the umbra for most stars \citep{1981ApJ...250..327V}.
+Spectral decomposition techniques are more sensitive to the warmer spot components and may therefore be constraining the prenumbra filling factor, which would be larger than the umbra filling factor.
+However, we do not know if the spot morphology of SSGs follows this assumption.
+If instead SSGs have a smaller ratio of prenumbra to umbra this spectral technique would under-sample the total spot coverage on the stellar surface.
+
+Additionally, possible wavelength dependencies of spot size would lead to discrepant spot filling factors across photometric and spectroscopic determinations at different wavelengths.
+We note that photometry collected at different epochs can also impact the inferred photometric filling factor.
+Given our light curve analysis of S1063 we expect epoch-based filling factor uncertainties could be as large as $\sim$20\%, which could bring the two-temperature SED fit from \citet{leiner17} and our results into agreement.
+
 A summary of the surface and stellar parameters for S1063 are given in Table~\ref{tab:s1063parameters}, comparing our work here with parameters for S1063 determined in \citet{mathieu03}, \citet{leiner17}, and the SPOTS model comparison above.
-The filling factor determined via spectroscopic and photometric methods varies dramatically, with photometric methods finding a larger filling factor than our work here, although different photometric colors combinations suggest different filling factors.
+As the closest SPOTS model depends on the comparison photometry used (see Figure~\ref{fig:CMDs}), the stellar parameters for both models are given.
 
-The spectral decomposition technique used here is sensitive to larger spot filling factors \citep{gullysantiago17}, as long as the spots are of sufficient brightness to provide a significant spectral signature.
-We detect a significant spot spectral signature in S1063, but we do not know if we are detecting the spectrum of the umbra or prenumbra.
-Although it is most likely that the penumbra is larger in area and warmer than the umbra for most stars \citep{1981ApJ...250..327V}, suggesting that this technique is more sensitive to constraining the prenumbra filling factor and the prenumbra would dominate the total spot area on the star.
-However, if SSGs have smaller penumbra it is possible this technique would under-sample the total spot coverage on the stellar surface.
-Additionally, any possible wavelength dependence of spot size would also lead to discrepant spot filling factors across photometric and spectroscopic determinations at different wavelengths.
-We note that photometry collected at different epochs can also impact the inferred photometric filling factor, but given our light curve analysis we expect epoch-based filling factor uncertainties to be at most $\sim$20\% in filling factor.
-
-We present further discuss systematic uncertainties that may add to these discrepancies in Section~\ref{sec:uncertainties}, but fully resolving the complexities of photometric and spectroscopic constraining of spot filling factors likely requires careful photometric modeling of a multi-temperature stellar surface, which is beyond the scope of this paper.
+We further discuss systematic uncertainties that may impact these discrepancies in Section~\ref{sec:uncertainties}, but fully resolving the complexities of photometric and spectroscopic constraints of spot filling factors likely requires careful photometric and atmospheric modeling of a multi-temperature stellar surface, which is beyond the scope of this paper.
 
@@
 
-The spot coverage fraction determined in this work is consistent with the range of spot coverage seen on RS CVn of 30--40\% from measuring TiO band strength \citep{oneal96, oneal98, oneal04} and Doppler imaging \citep{hackman12}.
-The similar spot coverage fraction on S1063 determined here is further evidence that this sub-subgiant and likely other sub-subgiants have high magnetic activity.
+The spot coverage fraction for S1063 determined in this work is consistent with the range of spot coverage seen on RS CVn of 30--40\% from measuring TiO band strength \citep{oneal96, oneal98, oneal04} and Doppler imaging \citep{hackman12}.
+This is further evidence that this SSG and likely other SSGs have high magnetic activity.
 
-Strong magnetic fields and starspots reduce convective energy transport efficiency, which in turn mutates theoretical evolutionary model tracks from their unspotted/non-magnetic counterparts \citep{2013ApJ...779..183F,somers15,somers15b,somers20}.
-Understanding the physical nature of the magnetic activity and the impact it has on stellar structure and evolution requires comparison of high fidelity observations with these theoretical models.
-An accurate position in the HR diagram position requires determination of the effective temperature ($T_{\textrm{eff}}$) having accounted for spots, as well as the stellar luminosity.
+Strong magnetic fields and starspots reduce convective energy transport efficiency, which in turn alters theoretical evolutionary model tracks from their unspotted/non-magnetic counterparts \citep{2013ApJ...779..183F,somers15,somers15b,somers20}.
+Understanding the physical nature of the magnetic activity and the impact it has on stellar structure and evolution requires comparison of high-fidelity observations with these theoretical models.
+An accurate HR diagram position requires determination of the effective temperature ($T_{\textrm{eff}}$) having accounted for spots, as well as the stellar luminosity.
 
@@
 The conventional observational interpretation of $T_{\textrm{eff}}$ is difficult to apply to spotted stars, especially stars with variation in the spot covering fraction over time \citep{gullysantiago17}.
-Conventionally, a spectrum can be interpreted as possessing a 1:1 mapping from its appearance to a $T_{\textrm{eff}}$-indexed template, which can be either model-based or observed.
+Different methods of characterizing $T_{\textrm{eff}}$ complicate  comparisons between observations and theoretical models.
+
+%Conventionally, a star is thought to have a single $T_{\textrm{eff}}$ that can be easily matched to  Conventionally, a spectrum can be interpreted as possessing a 1:1 mapping from its appearance to a $T_{\textrm{eff}}$-indexed template, which can be either model-based or observed.
 We...
 
-\citet{leiner17} fit the multi-band spectral energy distribution for S1063 with a single Castelli-Kurucz spectrum \citep{2003IAUS..210P.A20C} and find a best fit $T_{\textrm{eff}}$ of 4500 K.
-Knowing we are dealing with a spotted star, another interpretation is to calculate the surface-averaged $T_{\textrm{eff}}$:
+\citet{leiner17} fit the multi-band spectral energy distribution for S1063 with a single Castelli-Kurucz spectrum \citep{2003IAUS..210P.A20C} and find a best fit single-temperature $T_{\textrm{eff}}$ of 4500 K.
+With observational confirmation that S1063 is a spotted star, another interpretation is to calculate the surface-averaged $T_{\textrm{eff}}$:
 
@@
 where $f_{\textrm{s}}$ is the spot covering fraction, $T_{\textrm{s}}$ is the spot temperature, $T_{\textrm{amb}}$ is the ambient photosphere temperature.
-This single surface-averaged temperature allows for comparisons to one-dimensional stellar evolution models motivated by the surface conditions of the star \citep{somers20}.
+This surface-averaged temperature allows for comparisons to one-dimensional stellar evolution models motivated by the surface conditions of the star \citep{somers20}.
 With this method, at the time of the IGRINS observation the $T_{\textrm{eff}}$ of S1063 is $4900\pm100$ K.
@@
 Stars such as S1063, however, have observed surface-averaged $T_{\textrm{eff}}$ values that vary based on the spot covering fraction at the time of observation.
-We know from the variable light curve that stars such as S1063 have differing spot covering fractions on opposite observable hemispheres of the star causing optical variability.
-For example, at the 4-year light curve maximum when S1063 had approximately a 20\% spot covering fraction the surface-averaged $T_{\textrm{eff}}$ for the observed hemisphere of the star would be 5000 K.
+We know from the variable light curve (Figure~\ref{fig:lightcurve}) that stars such as S1063 have differing spot covering fractions on opposite observable hemispheres of the star causing optical variability.
+For example, at the four-year light curve maximum S1063 had approximately 20\% spot covering fraction and a surface-averaged $T_{\textrm{eff}}$ (for the observed hemisphere of the star) of 5000 K.
 At the light curve minimum with a 45\% spot covering fraction the surface-averaged $T_{\textrm{eff}}$ for the observed hemisphere would only be 4700 K.
@@
 The true surface-averaged $T_{\textrm{eff}}$ includes the entire stellar surface.
-This should be constant over a thermal timescale, including the four-year time frame in Figure~\ref{fig:lightcurve}, as is demonstrated by the constant mean flux level of 89.5\% compared to the maximum global flux.
+This should be constant over a thermal timescale, much longer than the four-year time frame in Figure~\ref{fig:lightcurve}, as is demonstrated by the constant mean flux level of 89.5\% compared to the maximum global flux.
 Observationally constraining the surface-averaged $T_{\textrm{eff}}$ requires either multi-epoch spectrum observations at both the light curve maximum and minimum, or a single observation at the mean flux level.
-The date of the IGRINS observation corresponds to a global flux level of 0.912, suggesting that observed spot coverage is a reasonable proxy for the mean state of S1063.
+The date of the IGRINS observation corresponds to a flux level of 91.2\% compared to the global maximum, suggesting that observed spot coverage is a reasonable proxy for the mean state of S1063.
 Therefore, we conclude that the total surface-averaged $T_{\textrm{eff}}$ of S1063 is consistent with the observed surface-averaged $T_{\textrm{eff}}$ of $4900\pm100$ K.
-We stress, however, that determining a single $T_{\textrm{eff}}$ value for spotted stars is fraught at best, and makes model comparisons exceedingly nuanced.
+We stress, however, that determining a single $T_{\textrm{eff}}$ value for spotted stars makes model comparisons exceedingly nuanced.
 
 \subsection{Radius of S1063}
+\label{sec:radius}
 
-The radius of S1063 gets encoded into our data streams in three ways.
-Kinematically, radius affects $v\sin{i}$, photometrically radius affects the SED and HR diagrams, and gravitationally radius affects the surface gravity $\log{g}$.
-Our weak constraints on surface gravity cannot meaningfully inform the radius.
-The SED-based photometric results suggest a radius of $R_{\star} = 3.7-4.6 R_\odot$, implausibly large compared to even the most egregiously spotted radii inflation models.
-The kinematic avenue therefore seems most promising and ostensibly least subject to astrophysical biases, so it is worth dissecting in some detail here.
+The radius of S1063 is encoded into data in three ways: via surface gravity-sensitive spectral lines, in the SED and HR Diagram position, and embedded within the $v\sin{i}$ measurement.
+Observationally constraining the radius of spotted stars would help model comparisons, especially in light of the single $T_{\textrm{eff}}$ nuances elaborated above.
+
+Our weak constraints on surface gravity from the IGRINS spectra cannot meaningfully inform the radius.
+Previously determined SED-based photometric results suggest a radius of $R_{\star} = 2.8-3.4 R_\odot$ (see Table~\ref{tab:s1063parameters}).
+We elaborate on constraining the radius from $v\sin{i}$ here.
 The stellar radius $R_{\star}$ contributes to the magnitude of the equatorial velocity $v_{\mathrm{eq}}$ for a given rotation rate and projected stellar inclination angle $i$:
@@
   v \sin{i} = \frac{2\pi R_{\star}}{P_{\mathrm{rot}}} \sin{i} \\
-  R_{\star} \sin{i} = \frac{v \sin{i} \cdot P_{\mathrm{rot}}}{2 \pi} \\
+  R_{\star} \sin{i} = \frac{v \sin{i} \cdot P_{\mathrm{rot}}}{2 \pi} \label{rsini}
 \end{eqnarray}
 
-Our \texttt{Starfish}/IGRINS-derived $v\sin{i}=XX$ and \texttt{celerite}/K2 derived period $P_{\mathrm{rot}}=XX$ constrain $R\sin{i} = XX$, with a formal statistical uncertainty of XX.
-At first sight, $R_{\star}$ is most likely $>XX R_{\odot}$, since $\sin{i}$ is only ever less than unity.
-The combined $XX\%$ uncertainty in $R\sin{i}$ and the photometrically-derived radius uncertainty of $XX\%$ yields coarse agreement/disagreement with these two disparately-sourced estimates.
-At least three sources of unaccounted-for astrophysical uncertainties can conceivably bias the derived $v\sin{i}$ for heavily spotted sub-giants.
-The unknown limb-darkening prescription, the micro- or macro- turbulent velocity, and the latitudinal segregation of starspots.
+Our \texttt{Starfish}/IGRINS-derived $v\sin{i}=10.0 \pm 1.0 \; \mathrm{km\,s^{-1}}$ and \texttt{celerite}/K2 derived period $P_{\mathrm{rot}}=23.5 \pm 0.1$ constrain $R\sin{i} = 4.6 \;R_\odot$, with a formal statistical uncertainty of $\pm 0.5 \;R_\odot$.
+For stars viewed at an inclination other than perfectly edge-on, the typical inferred stellar radius $R_{\star}$ must exceed $4.6 R_{\odot}$.
+If we instead adopt the optically-determined $v\sin{i}=8\; \mathrm{km\,s^{-1}}$ from \citet{mathieu03} the radius must exceed 3.7 $R_{\odot}$.
+In either case, this kinematically-inferred radius is inconsistent with the radius range determined through photometric studies.
+A two-temperature SED of S1063 adopting the minimum $R\sin{i}$ values is far too bright compared to observed photometry, suggesting that the $R\sin{i}$ limits here are biased to larger values in some way.
+
+One possible source of this discrepancy is the spotted surface somehow alters the assumptions behind Equation \ref{rsini}.
+Possible astrophysical uncertainties that could potentially bias the $v\sin{i}$ for heavily spotted sub-giants include the adopted limb-darkening prescription, micro- or macro-turbulence, and Zeeman broadening.
+Additionally, the observed period could be biased via differential rotation combined with starspots constrained to either high or low latitudes, starspot evolution timescales similar to the rotation period, and aliasing from regularly-spaced longitudinal surface symmetries.
+The magnitude and/or direction of these period biases are generally uncertain.
+We note that the other SSG in M67, S1113, also has an anomalously-large $R\sin{i}$ value determined from $v\sin{i}$ \citep{mathieu03}, suggesting that perhaps the surface conditions of SSGs cause spectral broadening such that the standard $v\sin{i}$ measurement is not truly a measure of the stellar rotation velocity.
+A campaign of intense doppler-imaging-style observations could act to disentangle some of these uncertainties in the future, though such a campaign would require extreme spectral resolution in order to resolve surface structures given the relatively low apparent $v\sin{i}$.
+
+%We consider for the moment a hypothetical perfectly edge-on orientation.
+The kinematically derived radius exceeds its photometric counterpart by 2.6$\,\sigma$, an ostensible tension for these two disparately-sourced estimates.
+However, we consider the possibility that the star is so profoundly spotted as to alter the assumptions that lead to Equation \ref{rsini}.
+At least four sources of unaccounted-for astrophysical uncertainties can conceivably bias the derived $v\sin{i}$ for heavily spotted sub-giants.
+The limb-darkening prescription, unaccounted for Zeeman broadening, micro- or macro- turbulent velocity, and the latitudinal segregation of starspots all act to modulate the mapping from observed line profile to inferred $v\sin{i}$.
 On the other hand, the period can be systematically biased in three significant ways: differential rotation combined with latitudinal starspot segregation, starspot evolution on timescales comparable to the rotation period, and aliasing from regularly-spaced longitudinal surface symmetries.
-
-\natalienote{
--Rsini can also be used as a model comparison, but this Rsini is large (we think 3.7-4.6 Rsun) compared to what has been found in previous SED fits (Leiner2017)}
-
-%{f the with direct predictions for spot covering fractions of photometrically emitting spots.
-A preliminary comparison to S1063 is included in \citet{somers20}, but using a lower $T_{\textrm{eff}}$ as found in \citet{leiner17}.
-However, \citet{somers20} uses the surface-averaged temperature to define $T_{\textrm{eff}}$ (see Eq 1 in Somers20), so the $T_{\textrm{eff}}$ determined in this work is a more appropriate comparison.
-
-%-Updated temp brings these results more in line with the spot coverage implied by SPOTS models, assuming the luminosity is the same.
-SPOTS models are maybe still a little bit too spotted - close to the 51\% track compared to 32\% that we measure, but our uncertainties are large and we have systematic errors that are unaccounted for.
+The aggregate magnitude and/or direction of these systematic biases is generally uncertain, and even the rank order of which bias predominates may defy the routine assumptions applied to modestly spotted stars like the Sun.
+We therefore attribute the apparent tension in our radius uncertainties to these epistemic uncertainties with magnitudes comparable to or greater than the formal statistical uncertainties.
+A campaign of intense Doppler-Imaging-style observations could act to disentangle some of these uncertainties in the future, though such a campaign would require extreme spectral resolution in order to resolve surface structures given the relatively low apparent $v\sin{i}$.
 
@@
 \label{sec:uncertainties}
-We have posited a two-temperature surface two derive our estimates for filling factors and effective temperature.
-In reality, this star---and most active stars more generally---must exhibit a range of apparent surface contrasts attributable to umbra, penumbra, faculae, chromospheric emission, and other phenomena unaccounted for in this work \citep{berdyugina05, 2009A&ARv..17..251S}.
+We assume a two-temperature stellar surface to derive our estimates for spot filling factor and effective temperature.
+In reality, this star---and most active stars more generally---must exhibit a range of apparent surface features attributable to umbra, penumbra, faculae, chromospheric emission, and other phenomena unaccounted for in this work \citep{berdyugina05, 2009A&ARv..17..251S}.
+These phenomena all have different temperatures and wavelength-dependent flux contrasts with the ambient photosphere.
 
@@
 So for example, our technique might readily perceive the penumbra of the starspot, while ignoring the much cooler and darker umbra flux contribution \citep{1981ApJ...250..327V}.
-This umbral neglect would lead our technique to systematically underestimate the total starspot coverage, rendering our claimed estimate as a lower limit.
+This bias would lead our technique to systematically underestimate the total starspot coverage, rendering our claimed estimate as a lower limit.
 On the other hand, faculae and plage act to add a hotter-than-average surface component.
-The interpretation of our two component mixture model becomes confounded if we posit the coexistence of three components: spot, ambient, and faculae \citep{1998A&A...329..747S}.
-The extent of the confounding depends on the detailed properties of such conceivable faculae, but in short faculae may act to either increase or decrease starspot coverage estimates insofar as they alter the ambient photosphere temperature that we assign \citep{2019AJ....157...11W}.
+Our two-component model cannot accurately account for the coexistence of spots and faculae with an ambient photosphere \citep{1998A&A...329..747S}.
+Specifically, faculae may act to either increase or decrease starspot coverage estimates insofar as they alter the determined ambient photosphere temperature  \citep{2019AJ....157...11W}.
 The existence of large and hot faculae can be ruled out to some extent by the fact that they would dominate the temperature determination in visible wavelength spectra.
-The adequate agreement temperature derived from visible wavelength spectra of S1063 \citep{mathieu03} and the our near-IR derived ambient photosphere temperature suggests that faculae may be negligible.
+The adequate agreement in ambient temperature derived from visible \citep{mathieu03} and near-IR spectra of S1063 in this work suggests that faculae may be negligible.
 Chromospheric emission should mostly perturb individual lines that are known to be chromospherically active, such as Hydrogen lines.
@@
 Our reliance on \texttt{PHOENIX} synthetic spectra adds a model-dependent systematic to our entire approach.
-The unavailability of a large number of spot-free high-precision high-resolution template spectra across all of $H$-band demands the use of these models in order to compare to IGRINS data.
+The unavailability of a large number of spot-free high-precision high-resolution empirical template spectra across all of $H$-band demands the use of these models in order to compare to IGRINS data.
 The ability of such synthetic spectra to resemble starspots remains an unknown.
-We can get some clue of the performance of the synthetic spectra by examining the fit residuals, evinced in this work by comparing the purple two-component composite spectrum to the gray IGRINS spectrum in Figure \ref{fig:IGRINS_spectra3x3}.
-The IGRINS spectra exhibit absorption lines where no such line is predicted, and vice versa: lines absent from the IGRINS spectra that our composite model would predict.
+We can examine fit residuals to explore the performance of the synthetic spectra by comparing the purple two-component composite spectrum to the gray IGRINS spectrum in Figure \ref{fig:IGRINS_spectra3x3}.
+We see that the observed IGRINS spectrum has lines that do not appear in the model, and the model has lines that do not appear in the observed spectrum.
 To some extent, the imperfect fitting of the synthetic spectra to our IGRINS spectra must be causing a systematic uncertainty.
@@
 We therefore assign at least a 30 K systematic bias in our temperature estimates based on the prospect of individual line outliers polluting our fit residuals.
-We conseassign a coarse estimate of 100--200 K to so-called ``label noise'', associated with the alignment of a best fit \texttt{PHOENIX}-provided $T_{\text{eff}}$ labels and an unseen ground-truth label for the ``True'' temperature of the spots.
+We co-assign a coarse estimate of 100--200 K to so-called ``label noise'', associated with the alignment of a best fit \texttt{PHOENIX}-provided temperatures and an unseen ground-truth label for the ``True'' temperature of the spots.
 New studies of the Sun based on DKIST may offer the best future avenue for testing such assumptions and refining the ability to distinguish starspot emission from ambient photosphere.
 
-%%% TODO: retool below discussion for the HRD discussion
 %\subsection{Starspots as confounding factors}
@@
 
-%In the absence of this spectral inference technique one could assume the \textit{K2} C5 light curve maximum corresponded to zero spot presence with the light curve amplitude change implying a maximum spot coverage of 7--10\%.
-This provides a fundamentally different view of the star ...
-
-%\begin{itemize}
 %\item Conceivable geometries with circumpolar active longitudes, or migrating active latitudes
 %\item Biases introduced if we assume a spot-free model
-%\begin{itemize}
-%  \item Where does subsub sit in a new HR diagram? (new Somers models)
-%  \item *bonus* FIGURE: PMS HR diagram with new Somers tracks
-%  \item Spot impact on SED fits
-%\end{itemize}
-%\end{itemize}
 
@@
 
-Reiteration here.
+The impact of magnetic activity on stellar evolution is a quickly developing field in stellar astrophysics.
+SSGs serve an important sample for furthering our knowledge, as they exhibit dramatic offsets from typical stellar evolutionary pathways \citep{geller17, leiner17}.
+
+We use a combination of a light curve analysis and a near-IR spectral decomposition technique to constrain the starspot filling factor of SSG S1063 in open cluster M67.
+Previous work suggested that the underluminosity apparent in SSGs could be caused by inhibited convective energy transport due to high magnetic activity \citep{leiner17}.
+Constraining star spot filling factor is a helpful proxy for determining stellar magnetic activity, and this spectral decomposition technique allows for constraints on a much larger sample of stars than can be studied with Doppler Imaging or interferometry.
+
+We find a spot filling factor for S1063 of $32\pm7$\% at the time of the IGRINS observation.
+By combining this constraint with the variability seen in the four-year light curve we determine that this is approximately the mean state of the star over this four-year time period, with a minimum and maximum spot covering fraction of 20\% to 45\%, respectively.
+Importantly, this technique reveals that the maximum light during this time period did not correspond to an un-spotted star.
+This spot filling factor is consistent with those determined for RS CVn stars through other methods, suggesting that SSGs are another type of active giant star binary systems.
+
+The spot filling factor found here is generally less than the filling factor found through indirect photometric comparisons.
+It is possible that different sensitivities to umbra or prenumbra features of spots, wavelength dependencies in detected spot size, or differences in the observed hemisphere of the star across different epochs of observation could all result in different determinations of spot filling factor between spectroscopic and photometric techniques.
+However, the state of current stellar activity theoretical models makes direct comparison difficult.
+We encourage future work in careful conversion between stellar structure models and observational signatures, including spectroscopic templates, to help resolve these apparent discrepancies.
+%The source of the discrepancies between spectroscopic and photometric methods is not entirely clear, but may be due to different sensitivities to umbra or prenumbra features of spots, wavelength dependencies in detected spot size, or differences in the observed hemisphere of the star across different epochs of observation.
+
+We find that reporting a single ``$T_{\mathrm{eff}}$" for active spotted stars is a confusing concept at best, and can lead to unclear or possibly incorrect observational and model comparisons.
+The surface-averaged $T_{\mathrm{eff}}$ derived from our results is not consistent with a single SED-fit temperature for S1063.
+Additionally, determining the surface-averaged $T_{\mathrm{eff}}$ for S1063 would vary from 4700 K to 5000 K depending on the epoch of observation, as only one hemisphere of the star can be observed at a time.
+We encourage future work in this area to be as explicit as possible when reporting temperatures for active stars to enable the most accurate comparisons between observational and theoretical efforts.
+
+There is still much we do not understand about spot morphologies, the observational biases that impact our assumptions about spot filling factors, and how measurements of the stellar surface can be connected to the internal structure of the star.
+Focused studies such as these serve as important benchmarks for technique development, but larger studies of starspots on active stars are necessary to explore the suggested discrepancies between different observational methods of determining spot filling factors.
+These larger studies would also serve as important test samples for observational and theoretical comparisons to untangle the impact of stellar activity on stellar evolution.
 

### 2021-05-14 document/ms.tex
:truck: copy new figures from Overleaf, Makefile now uses git show and commit SHA
:memo: prose updates and edits

@@
 This impact of stellar activity and magnetic fields is seen throughout the Hertzsprung-Russell (HR) Diagram.
-For example, by biasing isochronal ages of young clusters \citep{somers15}, inflating radii of active M-dwarfs \citep{2010AJ....140.1158T,2010ApJ...718..502M,2019MNRAS.483.1125J}, causing multiple redder turnoffs in stellar clusters \citep{2009MNRAS.398L..11B,2019ApJ...876..113S}, and altering the pulsation modes of red giants \citep{2020A&A...639A..63G}.
-As our ability to probe the detailed physics of stellar evolution continues to improve we must grapple with the complexities of stellar structure diverging from simpler theoretical expectations due to magnetic activity, which requires careful observational studies of magnetically active systems to test magnetic stellar models.
+Magnetic activity biases isochronal ages of young clusters \citep{somers15}, inflates radii of active M-dwarfs \citep{2010AJ....140.1158T,2010ApJ...718..502M,2019MNRAS.483.1125J}, causes multiple redder turnoffs in stellar clusters \citep{2009MNRAS.398L..11B,2019ApJ...876..113S}, and alters the pulsation modes of red giants \citep{2020A&A...639A..63G}.
+Our collective understanding of stellar structure has diverged from non-magnetic theoretical expectations due to careful observational studies of both magnetically active and inactive systems.
 
-One example of the impact of magnetic activity is seen in sub-subgiant (SSG) stars, defined to be stars that lie below the subgiant branch on a cluster optical color-magnitude diagram (CMD), but are too red to be main sequence stars.
-These stars are commonly found in evolved open clusters and globular clusters, with 65 sub-subgiants currently identified across 17 different clusters \citep{geller17}.
-The majority of sub-subgiant stars are single-lined spectroscopic binaries with short orbital periods of a few days with moderate X-ray luminosities of $10^{30}$ to $10^{31}$ erg s$^{-1}$ \citep[and references therein]{geller17}.
+One increasingly conspicuous example of the impact of magnetic activity is the class known as sub-subgiant (SSG) stars.
+SSGs lie below the subgiant branch on a cluster optical color-magnitude diagram (CMD), but appear too red to inhabit the main sequence.
+These anomalously underluminous subgiants stand out in evolved open clusters and globular clusters, with 65 sub-subgiants currently identified across 17 different clusters \citep{geller17}.
+The majority of these cluster SSGs are single-lined spectroscopic binaries with short orbital periods of a few days and moderate X-ray luminosities of $10^{30}$ to $10^{31}$ erg s$^{-1}$ \citep[and references therein]{geller17}.
 
-The existence of sub-subgiants cannot be explained with typical single-star stellar evolutionary pathways.
-Three possible formation scenarios for sub-subgiants were put forth by \citet{geller17} and \citet{leiner17}: mass transfer in a binary system, stripping of a subgiant star envelope through a dynamical encounter, and reduced luminosity as a result of inhibited convection and large starspot covering fractions due to the presence of strong magnetic fields.
-\citet{leiner17} conclude that the majority of sub-subgiants are likely the result of strong magnetic fields.
-This interpretation is supported by the presence of H-alpha and X-ray emission and optical variability seen across the known sub-subgiant population \citep{geller17}, all observational signatures of magnetic activity and the presence of starspots.
+The existence of SSGs cannot be explained with typical single-star stellar evolutionary pathways.
+\citet{geller17} and \citet{leiner17} put forth three possible formation scenarios for SSGs: mass transfer in a binary system, stripping of a subgiant star envelope through a dynamical encounter, and reduced luminosity as a result of inhibited convection due to the presence of strong magnetic fields.
+\citet{leiner17} conclude that the majority of SSGs result from the latter: strong stellar magnetic fields and affiliated starspot covering fractions must drive suppression of convection efficiency.
+At the specific evolutionary stage of a subgiant star, this results in the dramatic underluminosity apparent in the SSG population.
+Observational evidence supports this interpretation.
+Hallmarks of activity such as  H$\alpha$ and X-ray emission, and optical variability are seen throughout the known SSG population \citep{geller17}.
 
-Ideally, we would directly measure the stellar radius and internal magnetic field strength to calibrate how the star inflates as a function of convective efficiency, thereby explaining the CMD positions of SSGs.
-In practice, these quantities are difficult or impossible to measure at the precision required to demonstrate inflation for individual magnetically active systems, though aggregate populations have shown evidence for magnetic inflation \citep{2018AJ....155..225K,2018MNRAS.476.3245J}.
-Starspots have become a rich observational proxy for gauging the evolutionary state of stars that may be magnetically inflated without needing to estimate magnetic field strengths.
+In order to characterize the impact of magnetic fields and stellar activity on stellar evolution, we would ideally directly measure the stellar radius and internal magnetic field strength to calibrate how the star inflates due to inhibited convective energy transport, thereby explaining the CMD positions of SSGs.
+Ensembles of stars have shown evidence for an average magnetic radius inflation of $10-15\%$ \citep{2018AJ....155..225K,2018MNRAS.476.3245J}.
+In practice, these quantities are difficult or impossible to measure at the precision required to demonstrate inflation for individual magnetically active systems.
 
@@
 
+Starspots have become a rich observational proxy for gauging the evolutionary state of stars that may be magnetically inflated without needing to estimate magnetic field strengths.
 A full accounting of starspots requires careful consideration of geometrical degeneracies.
@@
 Longitudinally symmetric starspot geometries evade detection in monochromatic lightcurves alone \citep{2019AJ....157...64L}.
-Disk-integrated covering fractions can be obtained from TiO band observations \citep{oneal96,fang2016,2019AJ....158..101M}.
-Measuring the spot configuration typically requires Doppler imaging or interferometry studies restricted to only the brightest and most nearby sources \citep{roettenbacher16}.
-Testing the next era of stellar activity models requires precision methodologies to measure spot-covering fractions of a larger number of targets, including sub-subgiants.
+Disk-integrated covering fractions can be obtained from TiO band observations \citep{oneal96,fang2016,2019AJ....158..101M}, but measuring the spot configuration typically requires Doppler imaging or interferometry studies restricted to only the brightest and most nearby sources \citep{roettenbacher16}.
+Testing the next era of stellar activity models requires precision methodologies to measure spot-covering fractions of a larger number of targets, including SSGs.
 
 Starspots emit a spectrum of their own at a lower temperature and with distinct absorption features compared to the ambient photosphere.
-The observed spectrum is a composite of the spot and photosphere spectra and can therefore be deconvolved.
-This deconvolution constrains the spot-covering fraction as well as the spot and photosphere temperatures.
-This is possible by performing a two-temperature probabilistic spectral decomposition using the spectral inference framework \texttt{Starfish} \citep{czekala15}, recently extended to support composite spectra \citep{gullysantiago17}.
-The resulting spot characterization can be used to anchor light curve information, providing insight into the overall stellar activity level and constraining the long-term spot coverage \citep{neff95}.
-This strategy only requires high-resolution near-IR echelle spectroscopy and photometric monitoring, dramatically increasing the number of sources for which we can observationally constrain spot-covering fractions.
+The observed spectrum is therefore a composite of the spot and photosphere spectra, which can be deconvolved.
+\citet{gullysantiago17} extend the \texttt{Starfish} \citep{czekala15} spectral inference framework to support composite spectra and two-temperature probabilistic spectral decomposition.
+This deconvolution process constrains the spot-covering fraction as well as the spot and photosphere temperatures.
+The resulting disk-average spot properties anchor a simultaneous light curve flux to the starspot coverage fraction.
+This anchored value serves as a benchmark for interpreting long-term (multi-year) flux variability \citep{neff95}.
+This strategy only requires high-resolution near-IR echelle spectroscopy and photometric monitoring, making it less demanding on telescope resources than either Doppler Imaging or interferometry.
+The technique is amenable to sources with narrow spectral lines ($v\sin{i}<10$ km/s) and stars with any stellar inclination, a distinct advantage over Doppler imaging.
+Altogether these advantages dramatically increase the number of sources for which we can observationally constrain spot-covering fractions.
 
-In this paper we demonstrate the power of this methodology by focusing on a single SSG system, S1063 in the open cluster M67.
-This system is a prototypical SSG, with an single-lined spectroscopic orbital period of 18.4 days \citep{geller17}, an X-ray luminosity of $1.3\times10^{31}$ erg s$^{-1}$ \citep{vandenberg99}, and a variable light curve in \textit{K2} and ASAS-SN (Section~\ref{sec:K2lightcurve}).
+In this paper we demonstrate the power of this methodology by focusing on a single SSG system, S1063 \citep{1977A&AS...27...89S} in the open cluster M67.
+This system is a prototypical SSG, with a single-lined spectroscopic orbital period of 18.4 days \citep{geller17}, an X-ray luminosity of $1.3\times10^{31}$ erg s$^{-1}$ \citep{vandenberg99}, and a variable light curve in \textit{K2} and ASAS-SN (Section~\ref{sec:K2lightcurve}).
 \emph{Gaia} DR2 astrometry \citep{2016A&A...595A...1G, 2018A&A...616A...1G} indicates a parallax ($1.17\pm0.025 \;$mas) and proper motion for S1063 (\emph{Gaia} DR2 604921030968952832) consistent with other M67 members  approaching 100\% membership probability \citep{2018ApJ...869....9G}.
 We present our observational data products in Section~\ref{sec:observations} and subsequent analysis in Section~\ref{sec:analysis}.
-Our results are given in Section~\ref{sec:results} with Discussion in Section~\ref{sec:discussion}.
+Our results are given in Section~\ref{sec:results} with Discussion in Section~\ref{sec:discussion} including additional discussion of the possible systematic uncertainties that may bias our results.
 Finally, our conclusions are outlined in Section~\ref{sec:conclusions}.
@@
 Aperture photometry was conducted with interactively-assigned custom apertures using the \texttt{lightkurve.interact()} feature \citep{geert_barentsen_2019_2565212}.
-The apertures were chosen to minimize flux-loss out of the aperture due to spacecraft-induced image motion, while avoiding low-$S/N$ pixels and the wings of adjacent PSFs.
+The apertures were chosen to minimize flux-loss out of the aperture due to spacecraft-induced image motion, while avoiding low-$S/N$ pixels and the wings of adjacent PSFs (\emph{c.f.} \ref{fig:imaging}).
 The Campaign 16 source PSF overlapped the edge of Custom Aperture ID 200200534, therefore a mosaic of adjacent superstamps was assembled before conducting aperture photometry.
-We detrended motion-induced image artifacts with the Self Flat Field algorithm \citep{vanderburg14} implemented in \texttt{lightkurve}.  Postage stamp images are shown in Figure \ref{fig:imaging}.
+We detrended motion-induced image artifacts with the Self Flat Field (SFF) algorithm \citep{vanderburg14} implemented in \texttt{lightkurve}.
 
@@
 The pixel images were not available to evaluate the extent of blending.
+The nearby source was verified to be non-variable in K2 data, so such blending would be expected to subdue the overall ASAS-SN lightcurve modulations while keeping the period and phase in-tact.
 
@@
 Compared to Campaign 5, the reference stars have a median flux of $93.9\pm4.2\%$ in Campaign 16 and a median flux of $98.2\pm2.8\%$ in Campaign 18.
-Campaigns 5 and 18 were observed on the same detector channel while a different detector channel was used for Campaign 16, therefore these offsets are not a significant measure of detector degradation across campaigns.
+Campaigns 5 and 18 were observed on the same detector channel while a different detector channel was used for Campaign 16, therefore the C16 offset is not a significant measure of detector degradation across campaigns.
 We use a Lomb-Scargle periodogram on each campaign independently and recover the same dominant period of 23.5 days in all three campaigns.
@@
 
-Constraining starspot covering fraction for stars such as S1063 requires a careful combination of light curve interpretation and spectral analysis using spectral decomposition tools such as \texttt{Starfish} \citep{czekala15} to benchmark epochs of starspot coverage in long-term photometric monitoring.
+%Constraining starspot covering fraction for stars such as S1063 requires a careful combination of light curve interpretation and spectral analysis using spectral decomposition tools such as \texttt{Starfish} \citep{czekala15} to benchmark epochs of starspot coverage in long-term photometric monitoring.
+Characterizing the long-term starspot coverage of S1063 requires connecting coarse ground-based and precision space-based photometry---ASAS-SN and \emph{K2}---alongside precision IGRINS spectroscopy.
+Here we lay out the calibration of these datasets to accommodate their wide range in data quality.
 
 \subsection{Joint modeling of ASAS-SN and \emph{K2} Lightcurves}
-Characterizing the long-term behavior of S1063 requires connecting and comparing photometry information from different missions, in this case ASAS-SN and \emph{K2}.
-To accomplish this task we jointly modeled the ASAS-SN and \emph{K2} lightcurves as a damped, driven Simple Harmonic Oscillator (SHO) Gaussian Process (GP) with \texttt{celerit\`e} \citep{2017AJ....154..220F}, revealing periodicity and secular changes in flux levels over a multi-year timeframe.
-This strategy offers flexibility to cope with windowing effects and the high dynamic range in data sampling and quality available across ASAS-SN and \emph{K2}.
-The ASAS-SN $V$-band and \emph{K2} photometric band share significant overlap and are treated as the same for this analysis.
 
+We attempt to unify the ASAS-SN, \emph{K2} long cadence, and \emph{K2} FFI data points into a single global lightcurve.
+The ASAS-SN $V$-band and \emph{K2} photometric system throughputs share significant wavelength coverage and are treated as adequately similar for this purpose.
+Our methodology can be thought of as learning a bandpass or ``notch'' filter from the \emph{K2} data and applying it to the ASAS-SN data.
+The advantage of this approach is to combine near-in-time ASAS-SN data points in a way that preserves that correlation structure known from \emph{K2}, without distorting the lightcurve peaks and valleys as could be expected from an unscrupulous binning procedure.
+In the end, a global lightcurve constructed in this way can guide the eye during the times when K2 data is unavailable and ASAS-SN data are sparse-but-still-informative.
+
+We jointly modeled the ASAS-SN and \emph{K2} lightcurves as a damped, driven Simple Harmonic Oscillator (SHO) Gaussian Process (GP) with \texttt{celerit\`e} \citep{2017AJ....154..220F}.
 We tuned a two-period GP model with the harmonic component possessing roughly half the period $P_H\sim12.5\;\mathrm{d}$ of the fundamental period $P_0=23.5\;\mathrm{d}$.
-The harmonic overtone frequency can be seen by eye in Figure \ref{fig:lightcurve}, as the \emph{K2} lightcurves appear more complex than a pure sine wave.
-Each periodic GP term also possessed a correlation amplitude and SHO quality factor which we consider nuisance parameters for the purpose of this fitting.
-We found broadly consistent values when \emph{K2} lightcurves were fitted on a per-campaign basis.
+The harmonic overtone frequency can be seen by eye in Figure \ref{fig:lightcurve}, as the \emph{K2} lightcurves appear more structured than a pure sine wave.
+We fit for a correlation amplitude and SHO quality factor for each periodic GP term.
+We found consistent best fit values when \emph{K2} lightcurves were fitted on a per-campaign basis.
 We then fit the three campaigns \emph{simultaneously} in the following way.
+We added an additional non-periodic secular trend GP component to capture the campaign-to-campaign mean-level variation.
 We set the overall vertical registration of the \emph{K2} lightcurves such that the ASAS-SN and Campaign 16 trends match, since M67 was contemporaneously observable from the ground for the entire duration of K2 Campaign 16.
 The uncertainty in the inter-campaign offsets calculated in Section~\ref{sec:K2lightcurve} is larger than the internal precision of the \emph{K2} photometry, so we adjust the Campaign 5 data within the offset uncertainty to match the approximately one week of temporal overlap with ASAS-SN.
-We added an additional non-periodic secular trend GP component to capture the campaign-to-campaign mean-level variation, also considered a nuisance parameter.
 
-Finally, we evaluated the trained GP model at the location of the ASAS-SN photometry, and at windows lacking data altogether.
+Finally, we transfer the pre-trained model parameters to a GP based on the ASAS-SN photometry.
+We evaluate the GP at all time points in Figure \ref{fig:lightcurve} including the seasonal data gaps.
 This trend appears in Figure \ref{fig:lightcurve} as the dark orange line with an orange shaded standard confidence region.
@@
 
-Even a single epoch of IGRINS observations provides an opportunity to constrain the spot covering fraction of S1063 that can be used as a benchmark for interpreting the long-term flux variation apparent in Figure~\ref{fig:lightcurve}.
+The IGRINS observation epoch can be seen as the vertical blue line in Figure~\ref{fig:lightcurve}.
+The filling factor derived at this moment belies the filling factor derived at all other lightcurve time points.
+
 We performed a two-temperature probabilistic spectral decomposition on the IGRINS $H$-band spectrum.

### 2021-05-18 document/ms.tex
:memo: Editting the paper! Yay!

@@
 
-\title{Constraining the Starspot Filling Factor of Active M67 Sub-Subgiant S1063}
+\title{Constraining the Starspot Filling Factor of Magnetically Active M67 Sub-Subgiant S1063}
 
@@
 The IGRINS observation epoch can be seen as the vertical blue line in Figure~\ref{fig:lightcurve}.
-The filling factor derived at this moment belies the filling factor derived at all other lightcurve time points.
+The filling factor derived at this moment will belie the filling factor projected forward and backward in time.
 
@@
 Some orders did not pass our convergence criteria, usually due to poor initialization of nuisance parameters or over-fitting.
-Furthermore, the radial velocity $v_z$ and projected rotational broadening $v\sin{i}$ were spot-checked to verify both consistent values among spectral orders as well as posterior distributions indicative of information-rich spectral orders.
+Furthermore, the radial velocity $v_z$ and projected rotational broadening $v\sin{i}$ were spot-checked to verify consistent values among spectral orders as well as posterior distributions indicative of information-rich spectral orders.
 Some relatively feature-free spectral orders did not offer enough constraining power to derive meaningful results in the face of multiple sources of degeneracy.
@@
 
-%\subsubsection{Consistency of stellar characterization}
-%Vsini is similar to before and radial velocity is what we expect given orbital phasing (NEED TO DO THE PHASING).
-
-%TODO: Analysis of near-IR flux contribution from binary companion
-%TODO: Limits on companion types
-
 \section{Results}
@@
 Across all nine orders, the median filling factor value is 32\% with a standard deviation of 7\%, with a corresponding spot temperature of $4000 \pm 200$ K.
-The ambient photosphere temperature associated with this spot signature varies from order-to-order and is broadly consistent with a range of temperatures between 5000 K and 5300 K, with a best guess value of 5200 K.
+The ambient photosphere temperature associated with this spot signature varies from order-to-order and is in the range of 5000 $-$ 5300 K, with a median value of 5200 K.
 These values are broadly consistent with a spectroscopic temperature of 5000 K for S1063 determined by \citet{mathieu03} determined from visible-wavelength spectra.
@@
 The ASAS-SN and \textit{K2} Campaign 5 data of S1063 (Figure~\ref{fig:lightcurve}) indicate that the IGRINS observation was coincidentally acquired near its modest local maximum at an overall flux level of 91.2\%.
-This is close to the overall 89.5\% mean flux level, where the 100\% flux level is equal to the global maximum over the four-year period covered by ASAS-SN and \textit{K2}.
+This is close to the overall 89.5\% mean flux level, where the 100\% flux level is defined as the global maximum over the four-year period covered by ASAS-SN and \textit{K2}.
 The lightcurve exhibits relatively modest variability at the time of the IGRINS observations with merely 3\% peak-to-valley variation compared to its global largest variation of almost 17\% as observed around 2017 January.

### 2021-05-18 document/ms.tex
:memo: Lots of content change to the discussion

@@
 A full accounting of starspots requires careful consideration of geometrical degeneracies.
-Monochromatic light curves can indicate spotted stars \citep{2014ApJS..211...24M} but only provide a lower limit on the differential spot coverage between the most and least spotted hemispheres.
+Monochromatic lightcurves can indicate spotted stars \citep{2014ApJS..211...24M} but only provide a lower limit on the differential spot coverage between the most and least spotted hemispheres.
 Longitudinally symmetric starspot geometries evade detection in monochromatic lightcurves alone \citep{2019AJ....157...64L}.
@@
 This deconvolution process constrains the spot-covering fraction as well as the spot and photosphere temperatures.
-The resulting disk-average spot properties anchor a simultaneous light curve flux to the starspot coverage fraction.
+The resulting disk-average spot properties anchor a simultaneous lightcurve flux to the starspot coverage fraction.
 This anchored value serves as a benchmark for interpreting long-term (multi-year) flux variability \citep{neff95}.
@@
 In this paper we demonstrate the power of this methodology by focusing on a single SSG system, S1063 \citep{1977A&AS...27...89S} in the open cluster M67.
-This system is a prototypical SSG, with a single-lined spectroscopic orbital period of 18.4 days \citep{geller17}, an X-ray luminosity of $1.3\times10^{31}$ erg s$^{-1}$ \citep{vandenberg99}, and a variable light curve in \textit{K2} and ASAS-SN (Section~\ref{sec:K2lightcurve}).
+This system is a prototypical SSG, with a single-lined spectroscopic orbital period of 18.4 days \citep{geller17}, an X-ray luminosity of $1.3\times10^{31}$ erg s$^{-1}$ \citep{vandenberg99}, and a variable lightcurve in \textit{K2} and ASAS-SN (Section~\ref{sec:K2lightcurve}).
 \emph{Gaia} DR2 astrometry \citep{2016A&A...595A...1G, 2018A&A...616A...1G} indicates a parallax ($1.17\pm0.025 \;$mas) and proper motion for S1063 (\emph{Gaia} DR2 604921030968952832) consistent with other M67 members  approaching 100\% membership probability \citep{2018ApJ...869....9G}.
@@
 We use a Lomb-Scargle periodogram on each campaign independently and recover the same dominant period of 23.5 days in all three campaigns.
-The phase-folded light curves and periodograms are shown in Figure~\ref{fig:periodogram}.
+The phase-folded lightcurves and periodograms are shown in Figure~\ref{fig:periodogram}.
 
@@
     \end{tabular}
-    \caption{On the right, a Lomb-Scargle Periodogram of the light curve for each \emph{K2} campaign and on the left, the corresponding phased \emph{K2} light curves.
+    \caption{On the right, a Lomb-Scargle Periodogram of the lightcurve for each \emph{K2} campaign and on the left, the corresponding phased \emph{K2} lightcurves.
 The average period associated with maximum power across all three campaigns is P = 23.5 days.
@@
   \includegraphics[width=0.95\textwidth]{figures/2020_K2_ASASSN_lcurve_2panel.pdf}
-\caption{Four year lightcurve for S1063, normalized to a maximum flux of 1.00 as denoted by the gray dashed line.
+\caption{Four year lightcurve for S1063, normalized to a maximum flux of 1.00 as denoted by the thick gray dashed line.
 The mean flux of 0.895 is shown with the gray dotted line.
-\emph{K2} Campaigns 5, 16, and 18 (densely-sampled red points) and ASAS-SN $V-$band (coarsely-sampled gray points) show approximately $5-17\%$ peak-to-valley photometric variations indicative of secularly evolving surface coverage of starspots.
+\emph{K2} Campaigns 5, 16, and 18 (densely-sampled red points) and ASAS-SN $V-$band (coarsely-sampled gray points) show approximately $3-17\%$ peak-to-valley photometric variations indicative of secularly evolving surface coverage of starspots.
 The orange line shows a damped, driven harmonic oscillator \texttt{celerit\`e} model \citep{2017AJ....154..220F} trained on the \emph{K2} and ASAS-SN data, and then applied to the noisy ASAS-SN points.
@@
 This is possible by performing a two-temperature probabilistic spectral decomposition using the spectral inference framework \texttt{Starfish} \citep{czekala15}, recently extended to support composite spectra \citep{gullysantiago17}.
-The resulting spot characterization can be used to anchor light curve information, providing insight into the overall stellar activity level and constraining the long-term spot coverage \citep{neff95}.
+The resulting spot characterization can be used to anchor lightcurve information, providing insight into the overall stellar activity level and constraining the long-term spot coverage \citep{neff95}.
 This strategy only requires high-resolution echelle spectroscopy and photometric monitoring, dramatically increasing the number of sources for which we can observationally constrain spot-covering fractions.
 
-%Constraining starspot covering fraction for stars such as S1063 requires a careful combination of light curve interpretation and spectral analysis using spectral decomposition tools such as \texttt{Starfish} \citep{czekala15} to benchmark epochs of starspot coverage in long-term photometric monitoring.
+%Constraining starspot covering fraction for stars such as S1063 requires a careful combination of lightcurve interpretation and spectral analysis using spectral decomposition tools such as \texttt{Starfish} \citep{czekala15} to benchmark epochs of starspot coverage in long-term photometric monitoring.
 Characterizing the long-term starspot coverage of S1063 requires connecting coarse ground-based and precision space-based photometry---ASAS-SN and \emph{K2}---alongside precision IGRINS spectroscopy.
@@
 
-For a first-order interpretation of light curve amplitudes, we posit that the lightcurve is starspot-dominated as opposed to facula-dominated.
-Under this assumption, minimum light corresponds to the largest blockage of ambient flux and therefore the largest starspot coverage on the instantaneous hemisphere projected towards the observer \cite{basri18}.
+For a first-order interpretation of lightcurve amplitudes, we posit that the lightcurve is starspot-dominated as opposed to facula-dominated.
+Under this assumption, minimum light corresponds to the largest blockage of ambient flux and therefore the largest starspot coverage on the instantaneous hemisphere projected towards the observer \citep{basri18}.
 Maximum light corresponds to the moments with the least---\emph{but not necessarily zero}---starspot coverage.
@@
 
-This 13\% spot coverage is a minimum value based on an assumption that the maximum lightcurve flux results from an un-spotted star.
-Our spectral inference results indicate the spot coverage at the time of the IGRINS observation was, in fact, 32\%.
-This suggests that at maximum light over this 4-year period the spot coverage of S1063 was approximately 20\%, and not zero as a first-order interpretation of the light curve would imply.
+This 13\% spot coverage is a minimum value based on an assumption that the global maximum lightcurve flux results from an un-spotted star.
+Our spectral inference results indicate the spot coverage at the time of the IGRINS observation was 32\%.
+Therefore the spot coverage of S1063 was approximately 20\% at maximum light over this 4-year period, and not zero as a first-order interpretation of the lightcurve would imply.
 
-The presence of starspots at the light curve maximum acts as a starspot baseline for interpreting the lightcurve.
+The presence of starspots at the lightcurve maximum acts as a starspot baseline for interpreting the lightcurve.
 Over the four years shown in Figure~\ref{fig:lightcurve}, the average flux variation is approximately 5\%, corresponding to an average spot covering fraction variation from each observed hemisphere of $\pm$8\%.
@@
 The IGRINS observation occurring near the mean global flux level fortuitously allows a robust characterization of the average state of S1063.
-These numbers possess formal uncertainties in the few percent range, and additional uncertainties from our reliance on spectral models.
-But broadly speaking, our result is firm under our assumptions --- S1063 has a large persistent starspot population that ebbs and flows in its longitudinal symmetry, resulting in variation in the peak-to-valley modulation, but always possesses an approximately 30\% spot covering fraction.
+These numbers possess formal uncertainties in the few percent range, and additional systematic uncertainties from our reliance on spectral models.
+But broadly speaking, our result is firm under our assumptions --- S1063 has a large persistent starspot population that ebbs and flows in its longitudinal symmetry, resulting in variation in the peak-to-valley modulation, but routinely possessing an approximately 30\% spot covering fraction.
 
@@
 However, observational biases may also impact the filling factors determined through spectroscopic and photometric methods.
-The spectral decomposition technique used here is sensitive to larger spot filling factors \citep{gullysantiago17}, as long as the spots are of sufficient brightness to provide a significant spectral signature.
-We do detect a significant spot spectral signature in S1063, but we do not know if we are detecting the spectrum of the umbra or prenumbra.
-It is most likely that the penumbra is larger in area and warmer than the umbra for most stars \citep{1981ApJ...250..327V}.
+Our near-IR spectral decomposition technique is most sensitive to detecting a ``sweet-spot'' in starspot contrast: cool enough to exhibit a spectrum that is qualitatively distinct from the ambient photosphere, but not so cool as to possess vanishing specific intensity.
+So for example, our technique might readily perceive the penumbra of the starspot, while ignoring the much cooler and darker umbra flux contribution \citep{1981ApJ...250..327V}.
+This bias would lead our technique to systematically underestimate the total starspot coverage, rendering our claimed filling factor estimate as a lower limit.
 Spectral decomposition techniques are more sensitive to the warmer spot components and may therefore be constraining the prenumbra filling factor, which would be larger than the umbra filling factor.
@@
 
-Additionally, possible wavelength dependencies of spot size would lead to discrepant spot filling factors across photometric and spectroscopic determinations at different wavelengths.
-We note that photometry collected at different epochs can also impact the inferred photometric filling factor.
-Given our light curve analysis of S1063 we expect epoch-based filling factor uncertainties could be as large as $\sim$20\%, which could bring the two-temperature SED fit from \citet{leiner17} and our results into agreement.
+Other second-order effects could be at play.
+Spots could hypothetically exhibit a perceived wavelength dependence of their boundaries that would lead to apparent discrepancies in spot filling factors across photometric and spectroscopic determinations at different wavebands.
+Such effects are not well-understood for stars other than the Sun, where the exact boundaries of active regions can be examined in different filters.
+We note that photometry collected at different epochs can also degrade the precision of SED-based photometric filling factors.
+Given our lightcurve analysis of S1063 we expect SED-based filling factor uncertainties could be as large as $\sim$20\% from unluckily sampling peaks and troughs of the lightcurve.
 
@@
 As the closest SPOTS model depends on the comparison photometry used (see Figure~\ref{fig:CMDs}), the stellar parameters for both models are given.
-
-We further discuss systematic uncertainties that may impact these discrepancies in Section~\ref{sec:uncertainties}, but fully resolving the complexities of photometric and spectroscopic constraints of spot filling factors likely requires careful photometric and atmospheric modeling of a multi-temperature stellar surface, which is beyond the scope of this paper.
+Fully resolving the complexities of photometric and spectroscopic constraints of spot filling factors likely requires careful photometric and atmospheric modeling of a multi-temperature stellar surface, which is beyond the scope of this paper.
 
@@
 The spot coverage fraction for S1063 determined in this work is consistent with the range of spot coverage seen on RS CVn of 30--40\% from measuring TiO band strength \citep{oneal96, oneal98, oneal04} and Doppler imaging \citep{hackman12}.
-This is further evidence that this SSG and likely other SSGs have high magnetic activity.
+The collective evidence supports the interpretation that S1063 and by extension other SSGs have magnetic activity so severe as to alter their positions in the HR diagram.
 
@@
 \subsection{Effective temperature of spotted stars}
-The conventional observational interpretation of $T_{\textrm{eff}}$ is difficult to apply to spotted stars, especially stars with variation in the spot covering fraction over time \citep{gullysantiago17}.
-Different methods of characterizing $T_{\textrm{eff}}$ complicate  comparisons between observations and theoretical models.
 
-%Conventionally, a star is thought to have a single $T_{\textrm{eff}}$ that can be easily matched to  Conventionally, a spectrum can be interpreted as possessing a 1:1 mapping from its appearance to a $T_{\textrm{eff}}$-indexed template, which can be either model-based or observed.
-We...
+%% Is the first sentence too obvious?
+Effective temperature relates the radius and luminosity of a star through the Stefan-Boltzmann Law.
+The radius of S1063 remains constant over thermal timescales much longer than the span of available data.
+We assume the long-time averaged luminosity also remains constant as starspots come and go on the surface, but have a near-constant time-averaged occupation fraction.
+A hint of this quasi-static luminosity state can be conceptualized in Figure \ref{fig:lightcurve} with a relatively constant mean flux level of 89.5\% compared to the maximum global flux.
+In these limits, there exists a well-defined $T_{\textrm{eff}}$ that conventionally relates the long-time-averaged luminosity and radius:
+\begin{equation}
+T_{\textrm{eff}}^4 = f_{\textrm{s}} T_{\textrm{s}}^4 + (1 -f_{\textrm{s}}) T_{\textrm{amb}}^4 . \label{defineTeff}
+\end{equation}
+where $f_{\textrm{s}}$ is the long-time-averaged spot covering fraction, $T_{\textrm{s}}$ is the long-time-averaged spot temperature, $T_{\textrm{amb}}$ is the long-time-averaged ambient photosphere temperature.
+Two factors make it challenging to measure and interpret effective temperature of spotted stars in practice.
+First, the number of surface components may be misassigned.
+For example \citet{leiner17} fit the multi-band spectral energy distribution for S1063 with a single Castelli-Kurucz spectrum \citep{2003IAUS..210P.A20C} and find a best fit single-temperature $T_{\textrm{eff}}$ of 4500 K.
+Here we show that two temperatures is better justified.
+It may be that 3 components is even better justified, requiring a further adjustment to Equation \ref{defineTeff}.
+Second, instantaneously derived effective temperatures may be acquired at a time that is not representative of the steady-state.
 
-\citet{leiner17} fit the multi-band spectral energy distribution for S1063 with a single Castelli-Kurucz spectrum \citep{2003IAUS..210P.A20C} and find a best fit single-temperature $T_{\textrm{eff}}$ of 4500 K.
-With observational confirmation that S1063 is a spotted star, another interpretation is to calculate the surface-averaged $T_{\textrm{eff}}$:
+Here we attempt to compare the surface-averaged temperature to one-dimensional stellar evolution models motivated by the surface conditions of the star \citep{somers20}.
+At the time of the IGRINS observation the $T_{\textrm{eff}}$ of S1063 derived with Equation \ref{defineTeff} is $4900\pm100$ K.
+This temperature is inconsistent with the 4500 K temperature determined via single-temperature SED fitting in \citet{leiner17}, indicative of the discrepancies between the spectral and photometric constraints outlined in Section~\ref{sec:model_comparison}, although we note that the previous temperature of 4500 K lands between the measured spot and ambient photosphere temperatures determined in this work.
 
-\begin{equation}
-T_{\textrm{eff}}^4 = f_{\textrm{s}} T_{\textrm{s}}^4 + (1 -f_{\textrm{s}}) T_{\textrm{amb}}^4 .
-\end{equation}
-
-where $f_{\textrm{s}}$ is the spot covering fraction, $T_{\textrm{s}}$ is the spot temperature, $T_{\textrm{amb}}$ is the ambient photosphere temperature.
-This surface-averaged temperature allows for comparisons to one-dimensional stellar evolution models motivated by the surface conditions of the star \citep{somers20}.
-With this method, at the time of the IGRINS observation the $T_{\textrm{eff}}$ of S1063 is $4900\pm100$ K.
-This temperature is inconsistent with the temperature determined via SED fitting in \citet{leiner17}, indicative of the discrepancies between the spectral and photometric constraints outlined in Section~\ref{sec:model_comparison}, although we note that the previous temperature of 4500 K is between the measured spot and ambient photosphere temperatures determined in this work.
-
-Stars such as S1063, however, have observed surface-averaged $T_{\textrm{eff}}$ values that vary based on the spot covering fraction at the time of observation.
-We know from the variable light curve (Figure~\ref{fig:lightcurve}) that stars such as S1063 have differing spot covering fractions on opposite observable hemispheres of the star causing optical variability.
-For example, at the four-year light curve maximum S1063 had approximately 20\% spot covering fraction and a surface-averaged $T_{\textrm{eff}}$ (for the observed hemisphere of the star) of 5000 K.
-At the light curve minimum with a 45\% spot covering fraction the surface-averaged $T_{\textrm{eff}}$ for the observed hemisphere would only be 4700 K.
+Stars such as S1063 can have instantaneously-derived $T_{\textrm{eff}}$ values that vary based on the spot covering fraction at the time of observation.
+We know from the variable lightcurve (Figure~\ref{fig:lightcurve}) that stars such as S1063 have differing spot covering fractions on opposite observable hemispheres of the star causing optical variability.
+For example, at the four-year lightcurve maximum S1063 had approximately 20\% spot covering fraction and an instantaneously-derived surface-averaged $T_{\textrm{eff}}$ (for the observed hemisphere of the star) of 5000 K.
+At the lightcurve minimum with a 45\% spot covering fraction the surface-averaged $T_{\textrm{eff}}$ for the observed hemisphere would only be 4700 K.
 
 The true surface-averaged $T_{\textrm{eff}}$ includes the entire stellar surface.
-This should be constant over a thermal timescale, much longer than the four-year time frame in Figure~\ref{fig:lightcurve}, as is demonstrated by the constant mean flux level of 89.5\% compared to the maximum global flux.
-Observationally constraining the surface-averaged $T_{\textrm{eff}}$ requires either multi-epoch spectrum observations at both the light curve maximum and minimum, or a single observation at the mean flux level.
-The date of the IGRINS observation corresponds to a flux level of 91.2\% compared to the global maximum, suggesting that observed spot coverage is a reasonable proxy for the mean state of S1063.
+Observationally constraining the surface-averaged $T_{\textrm{eff}}$ requires either multi-epoch spectrum observations at both the lightcurve maximum and minimum, or a single observation at the mean flux level.
+The date of the IGRINS observation corresponds to a flux level of 91.2\% compared to the global maximum, suggesting that observed spot coverage is a close proxy for the mean state of S1063 within the uncertainties.
 Therefore, we conclude that the total surface-averaged $T_{\textrm{eff}}$ of S1063 is consistent with the observed surface-averaged $T_{\textrm{eff}}$ of $4900\pm100$ K.
 We stress, however, that determining a single $T_{\textrm{eff}}$ value for spotted stars makes model comparisons exceedingly nuanced.
+Stars like S1063 may undergo stellar cycles with possibly massive changes to spot coverage over timescales of hundreds of years, much longer than our observational windows.
+
+\subsection{Flares}
+
+A star as allegedly active and spotted as S1063 should exhibit other metrics associated with activity beyond the already-mentioned hallmarks such as H$\alpha$, x-ray emission, and starspot coverage.
+We should see flares.
+A closer re-examination of Figures \ref{fig:periodogram} and \ref{fig:lightcurve} reveals conspicuous stellar flares in all three of the campaigns of \emph{K2}.
+The mere existence of these flares conveys supporting evidence for the magnetic interpretation for SSGs.
+The detection of flares also hints at a promising prediction for the analysis of known and undiscovered SSGs: \emph{TESS} lightcurves of sub-subgiants should exhibit a comparable frequency and amplitude of stellar flares as those seen in S1063.
+We may also expect a difference in the frequency of flares between SSGs and RS CVn stars if these two populations possess inherently different degrees of magnetic activity.
+Such a comparison will benefit from the much larger sample sizes of SSGs afforded by the all-sky \emph{TESS} mission in concert with \emph{Gaia}.
 
@@
 The radius of S1063 is encoded into data in three ways: via surface gravity-sensitive spectral lines, in the SED and HR Diagram position, and embedded within the $v\sin{i}$ measurement.
-Observationally constraining the radius of spotted stars would help model comparisons, especially in light of the single $T_{\textrm{eff}}$ nuances elaborated above.
+Measuring the radius of spotted stars would help constrain magnetic inflation models, especially in light of the single $T_{\textrm{eff}}$ nuances elaborated above.
 
-Our weak constraints on surface gravity from the IGRINS spectra cannot meaningfully inform the radius.
+Our weak constraints on surface gravity from the IGRINS spectra cannot meaningfully inform the radius without mass.
 Previously determined SED-based photometric results suggest a radius of $R_{\star} = 2.8-3.4 R_\odot$ (see Table~\ref{tab:s1063parameters}).
@@
 \begin{eqnarray}
-  v \sin{i} = \frac{2\pi R_{\star}}{P_{\mathrm{rot}}} \sin{i} \\
   R_{\star} \sin{i} = \frac{v \sin{i} \cdot P_{\mathrm{rot}}}{2 \pi} \label{rsini}
@@
 If we instead adopt the optically-determined $v\sin{i}=8\; \mathrm{km\,s^{-1}}$ from \citet{mathieu03} the radius must exceed 3.7 $R_{\odot}$.
-In either case, this kinematically-inferred radius is inconsistent with the radius range determined through photometric studies.
-A two-temperature SED of S1063 adopting the minimum $R\sin{i}$ values is far too bright compared to observed photometry, suggesting that the $R\sin{i}$ limits here are biased to larger values in some way.
+In either case, this kinematically-inferred radius is larger than the radius range determined through photometric studies.
+A two-temperature SED of S1063 adopting the minimum $R\sin{i}$ values is far too bright compared to observed photometry, suggesting our $R\sin{i}$ limits may be biased to larger values in some way.
 
-One possible source of this discrepancy is the spotted surface somehow alters the assumptions behind Equation \ref{rsini}.
+One possible source of this radius discrepancy is the spotted surface somehow alters the assumptions behind Equation \ref{rsini}.
 Possible astrophysical uncertainties that could potentially bias the $v\sin{i}$ for heavily spotted sub-giants include the adopted limb-darkening prescription, micro- or macro-turbulence, and Zeeman broadening.
@@
 We note that the other SSG in M67, S1113, also has an anomalously-large $R\sin{i}$ value determined from $v\sin{i}$ \citep{mathieu03}, suggesting that perhaps the surface conditions of SSGs cause spectral broadening such that the standard $v\sin{i}$ measurement is not truly a measure of the stellar rotation velocity.
-A campaign of intense doppler-imaging-style observations could act to disentangle some of these uncertainties in the future, though such a campaign would require extreme spectral resolution in order to resolve surface structures given the relatively low apparent $v\sin{i}$.
+A campaign of intense Doppler-imaging-style observations could act to disentangle some of these uncertainties in the future, though such a campaign would require extreme spectral resolution in order to resolve surface structures given the relatively low apparent $v\sin{i}$.
+
+The star could hypothetically be much larger than SED-based estimates, meaning the SED is understating the total luminosity somehow, an unlikely but conceivable scenario.
+We assume a two-temperature stellar surface to derive our estimates for spot filling factor and effective temperature.
+In reality, this star---and most active stars more generally---must exhibit a range of apparent surface features attributable to umbra, penumbra, faculae, chromospheric emission, and other phenomena unaccounted for in this work \citep{berdyugina05, 2009A&ARv..17..251S}.
+These phenomena all have different temperatures and wavelength-dependent flux contrasts with the ambient photosphere.
+
+The prospect of undercounting umbra suggests yet another candidate interpretation of the SED-$R\sin{i}$ tension: S1063 really is as large as $4.6 R_{\odot}$, but it has a profound coverage of imperceptibly dark umbra that has gone undetected with our methodology.
+Such a seemingly perverse scenario is oddly self-consistent: painting a surface with dark umbra represents the ultimate impediment to a star's ability to transport away its internal energy, demanding that the star increase dramatically in radius in order to reach energy balance.
+The SED would not readily betray the existence of these dark umbral regions, nor would any other of the measurements presented here.
+
+One technique could help discern such pathologically magnetically dark stars.
+Stellar surface tomography with occulting bodies such as eclipsing binaries or large planets provide a stringent test.
+The occultation depths, impact parameters, orbital parameters, and occultation durations for an ensemble of SSG eclipsing binaries would encode a pattern of primary stars losing too little flux during occultations.
+Eclipse depths would be too shallow.
+Or, if SSG starspots are small and distributed quasi-isotropically, eclipses would show dramatic spot-crossing events as eclipse chords contain gigantic black patches surrounded by brighter ambient photosphere.
+S1063 does not show evidence for occultations in its \emph{K2} lightcurve.
+Future larger samples of SSG EBs may help retire these scenarios, however unlikely they may seem.
 
@@
 \label{sec:uncertainties}
-We assume a two-temperature stellar surface to derive our estimates for spot filling factor and effective temperature.
-In reality, this star---and most active stars more generally---must exhibit a range of apparent surface features attributable to umbra, penumbra, faculae, chromospheric emission, and other phenomena unaccounted for in this work \citep{berdyugina05, 2009A&ARv..17..251S}.
-These phenomena all have different temperatures and wavelength-dependent flux contrasts with the ambient photosphere.
 
-Our near-IR spectral technique is most sensitive to detecting a ``sweet-spot'' in starspot contrast: cool enough to exhibit a spectrum that is qualitatively distinct from the ambient photosphere, but not so cool as to possess vanishing specific intensity.
-So for example, our technique might readily perceive the penumbra of the starspot, while ignoring the much cooler and darker umbra flux contribution \citep{1981ApJ...250..327V}.
-This bias would lead our technique to systematically underestimate the total starspot coverage, rendering our claimed estimate as a lower limit.
 On the other hand, faculae and plage act to add a hotter-than-average surface component.
 Our two-component model cannot accurately account for the coexistence of spots and faculae with an ambient photosphere \citep{1998A&A...329..747S}.
-Specifically, faculae may act to either increase or decrease starspot coverage estimates insofar as they alter the determined ambient photosphere temperature  \citep{2019AJ....157...11W}.
+Specifically, faculae may act to either increase or decrease starspot coverage estimates insofar as they act to boost the perceived ambient photosphere features and accordingly bias the derived temperature  \citep{2019AJ....157...11W}.
 The existence of large and hot faculae can be ruled out to some extent by the fact that they would dominate the temperature determination in visible wavelength spectra.
 The adequate agreement in ambient temperature derived from visible \citep{mathieu03} and near-IR spectra of S1063 in this work suggests that faculae may be negligible.
-Chromospheric emission should mostly perturb individual lines that are known to be chromospherically active, such as Hydrogen lines.
-Our IGRINS-based technique analyzed the majority of the $H$-band with whole-spectrum fitting, where such chromospherically active lines would have negligible impact.
+Chromospheric emission should mostly perturb individual lines that are known to be chromospherically active.
+Our IGRINS-based technique analyzed the majority of the $H$-band with whole-spectrum fitting, where such isolated chromospherically active lines would have negligible impact.
 
@@
 We see that the observed IGRINS spectrum has lines that do not appear in the model, and the model has lines that do not appear in the observed spectrum.
-To some extent, the imperfect fitting of the synthetic spectra to our IGRINS spectra must be causing a systematic uncertainty.
 The Gaussian process ``Global Kernels'' employed in \texttt{Starfish} account for some degree of correlated data-model residual mismatching.
-We did not employ the ``Local kernels'', which cause a 30 K systematic bias in comparable quality spectra of WASP-14 also compared to the \texttt{PHOENIX} models \citet{czekala15}.
+We did not employ the ``Local kernels'' approach, which cause a 30 K systematic bias in comparable quality spectra of WASP-14 also compared to the \texttt{PHOENIX} models \citet{czekala15}.
 We therefore assign at least a 30 K systematic bias in our temperature estimates based on the prospect of individual line outliers polluting our fit residuals.
@@
 
-We use a combination of a light curve analysis and a near-IR spectral decomposition technique to constrain the starspot filling factor of SSG S1063 in open cluster M67.
+We use a combination of a lightcurve analysis and a near-IR spectral decomposition technique to constrain the starspot filling factor of SSG S1063 in open cluster M67.
 Previous work suggested that the underluminosity apparent in SSGs could be caused by inhibited convective energy transport due to high magnetic activity \citep{leiner17}.
@@
 We find a spot filling factor for S1063 of $32\pm7$\% at the time of the IGRINS observation.
-By combining this constraint with the variability seen in the four-year light curve we determine that this is approximately the mean state of the star over this four-year time period, with a minimum and maximum spot covering fraction of 20\% to 45\%, respectively.
+By combining this constraint with the variability seen in the four-year lightcurve we determine that this is approximately the mean state of the star over this four-year time period, with a minimum and maximum spot covering fraction of 20\% to 45\%, respectively.
 Importantly, this technique reveals that the maximum light during this time period did not correspond to an un-spotted star.
@@
 
-The spot filling factor found here is generally less than the filling factor found through indirect photometric comparisons.
+The numerous sources of astrophysical uncertainties underscore how difficult it is to conduct a census for the effects of magnetic activity on a star.
+Geometric degeneracies, secular evolution, and starspot contrast effects make the problem partially degenerate.
 It is possible that different sensitivities to umbra or prenumbra features of spots, wavelength dependencies in detected spot size, or differences in the observed hemisphere of the star across different epochs of observation could all result in different determinations of spot filling factor between spectroscopic and photometric techniques.

### 2021-11-04 document/ms.tex
The accepted version of the paper, woohoo!
yay

@@
-\documentclass[trackchanges]{aastex631}
+\documentclass[twocolumn,tighten]{aastex631}
 \bibliographystyle{aasjournal}
@@
 
-\newcommand\natalienote[1]{\textbf{{\color{orange}#1}}}
-\newcommand\gullynote[1]{\textbf{{\color{magenta}#1}}}
-\newcommand\emilynote[1]{\textbf{{\color{cyan}#1}}}
+\hyphenpenalty=5000
+
 \newcommand{\Msolar}{M$_{\odot}$}
@@
 
+\received{02 Jun 2021}
+\revised{01 Nov 2021}
+\accepted{02 Nov 2021}
+
 \begin{document}
-\shorttitle{Starspot Coverage on Sub-subgiant S1063}
+\shorttitle{Starspot Properties of Sub-Subgiant S1063}
 \shortauthors{Gosnell et al.}
 
-\title{Constraining the Starspot Filling Factor of Magnetically Active M67 Sub-Subgiant S1063}
+\title{Observationally Constraining the Starspot Properties of Magnetically Active M67 Sub-Subgiant S1063}
 
-\author{Natalie M. Gosnell}
-\affiliation{Colorado College, Department of Physics, 14 E. Cache La Poudre St, Colorado Springs, CO 80903}
-\author{Michael A. Gully-Santiago}
-\affiliation{University of Texas at Austin}
-\author{Emily M. Leiner}
-\affiliation{CIERA, Northwestern}
-\author{Benjamin Tofflemire}
-\affiliation{University of Texas at Austin}
+\author[0000-0002-8443-0723]{Natalie M. Gosnell}
+\affiliation{Department of Physics, Colorado College, 14 E. Cache La Poudre St, Colorado Springs, CO 80903}
+\email{ngosnell@coloradocollege.edu}
+
+\author[0000-0002-4020-3457]{Michael A. Gully-Santiago}
+\affiliation{Department of Astronomy, The University of Texas at Austin, Austin, TX 78712, USA}
+
+\author[0000-0002-3944-8406]{Emily M. Leiner}
+\affiliation{Center for Interdisciplinary Exploration and Research in Astrophysics (CIERA) and Department of Physics and Astronomy, Northwestern University, 1800 Sherman Ave., Evanston, IL 60201, USA}
+
+\author[0000-0003-2053-0749]{Benjamin M. Tofflemire}
+\altaffiliation{51 Pegasi b Fellow}
+\affiliation{Department of Astronomy, The University of Texas at Austin, Austin, TX 78712, USA}
 
@@
 
-We measure the starspots on a sub-subgiant.
+Our understanding of the impact of magnetic activity on stellar evolution continues to unfold.
+This impact is seen in sub-subgiant stars, defined to be stars that sit below the subgiant branch and red of the main sequence in a cluster color-magnitude diagram.
+Here we focus on S1063, a prototypical sub-subgiant in open cluster M67.
+We use a novel technique combining a two-temperature spectral decomposition and light curve analysis to constrain starspot properties over a multi-year time frame.
+Using a high-resolution near-infrared IGRINS spectrum and photometric data from \emph{K2} and ASAS-SN, we find a projected spot filling factor of $32\pm7$\% with a spot temperature of $4000\pm200$ K.
+This value anchors the variability seen in the light curve, indicating the spot filling factor of S1063 ranged from 20\% to 45\% over a four-year time period with an average spot filling factor of 30\%.
+These values are generally lower than those determined from photometric model comparisons but still indicate that S1063, and likely other sub-subgiants, are magnetically active spotted stars.
+We find observational and theoretical comparisons of spotted stars are nuanced due to the projected spot coverage impacting estimates of the surface-averaged effective temperature.
+The starspot properties found here are similar to those found in RS CVn systems, supporting classifying sub-subgiants as another type of active giant star binary system.
+This technique opens the possibility of characterizing the surface conditions of many more spotted stars than previous methods, allowing for larger future studies to test theoretical models of magnetically active stars.
 
@@
 
-\keywords{stars: fundamental parameters ---  stars: statistics}
+%\keywords{Subgiant stars (1646), Stellar activity (1580), Starspots (1572), Spectroscopy (1558), Light curves (918), Open star clusters (1160), Near infrared astronomy (1093)}
 
 \section{Introduction}\label{sec:intro}
-Recent studies illuminate the important role stellar magnetic activity plays in stellar structure.
-This impact of stellar activity and magnetic fields is seen throughout the Hertzsprung-Russell (HR) Diagram.
+Recent studies illuminate the important role stellar magnetic activity has on stellar structure as the impact of stellar activity and magnetic fields is seen throughout the Hertzsprung-Russell (HR) Diagram.
 Magnetic activity biases isochronal ages of young clusters \citep{somers15}, inflates radii of active M-dwarfs \citep{2010AJ....140.1158T,2010ApJ...718..502M,2019MNRAS.483.1125J}, causes multiple redder turnoffs in stellar clusters \citep{2009MNRAS.398L..11B,2019ApJ...876..113S}, and alters the pulsation modes of red giants \citep{2020A&A...639A..63G}.
-Our collective understanding of stellar structure has diverged from non-magnetic theoretical expectations due to careful observational studies of both magnetically active and inactive systems.
+Our collective understanding of stellar structure has diverged from non-magnetic theoretical expectations thanks to careful observational studies of both magnetically active and inactive systems.
 
 One increasingly conspicuous example of the impact of magnetic activity is the class known as sub-subgiant (SSG) stars.
-SSGs lie below the subgiant branch on a cluster optical color-magnitude diagram (CMD), but appear too red to inhabit the main sequence.
-These anomalously underluminous subgiants stand out in evolved open clusters and globular clusters, with 65 sub-subgiants currently identified across 17 different clusters \citep{geller17}.
-The majority of these cluster SSGs are single-lined spectroscopic binaries with short orbital periods of a few days and moderate X-ray luminosities of $10^{30}$ to $10^{31}$ erg s$^{-1}$ \citep[and references therein]{geller17}.
+SSGs lie below the subgiant branch on a cluster optical color-magnitude diagram (CMD), but are too red to be on the main sequence.
+These anomalously underluminous subgiants stand out in evolved open clusters and globular clusters, with 65 sub-subgiants currently identified across 16 different clusters \citep{geller17}.
+Where orbital information is available, the majority of these cluster SSGs are single-lined spectroscopic binaries with short orbital periods of a few days.
+Many SSGs also exhibit moderate X-ray luminosities of $10^{30}$ to $10^{31}$ erg s$^{-1}$ \citep[and references therein]{geller17}.
 
-The existence of SSGs cannot be explained with typical single-star stellar evolutionary pathways.
-\citet{geller17} and \citet{leiner17} put forth three possible formation scenarios for SSGs: mass transfer in a binary system, stripping of a subgiant star envelope through a dynamical encounter, and reduced luminosity as a result of inhibited convection due to the presence of strong magnetic fields.
-\citet{leiner17} conclude that the majority of SSGs result from the latter: strong stellar magnetic fields and affiliated starspot covering fractions must drive suppression of convection efficiency.
-At the specific evolutionary stage of a subgiant star, this results in the dramatic underluminosity apparent in the SSG population.
-Observational evidence supports this interpretation.
-Hallmarks of activity such as  H$\alpha$ and X-ray emission, and optical variability are seen throughout the known SSG population \citep{geller17}.
+The existence of SSGs cannot be explained with typical single-star evolutionary pathways.
+\citet{geller17} and \citet{leiner17} put forth four possible formation scenarios for SSGs: mass transfer in a binary system, a collision between two main sequence stars, removing material from a subgiant star envelope through a dynamical encounter, and reduced luminosity as a result of inhibited convection due to the presence of strong magnetic fields.
+\citet{leiner17} conclude that mass transfer and dynamical formation pathways cannot account for the observed frequencies of SSGs in open clusters.
+The observed SSGs may instead be the result of strong magnetic fields and the affiliated starspot covering fractions suppressing convective energy transport.
+At the specific evolutionary stage of a subgiant star this would result in the dramatic underluminosity apparent in the SSG population, although more work into the physics of this mechanism is necessary.
 
-In order to characterize the impact of magnetic fields and stellar activity on stellar evolution, we would ideally directly measure the stellar radius and internal magnetic field strength to calibrate how the star inflates due to inhibited convective energy transport, thereby explaining the CMD positions of SSGs.
-Ensembles of stars have shown evidence for an average magnetic radius inflation of $10-15\%$ \citep{2018AJ....155..225K,2018MNRAS.476.3245J}.
-In practice, these quantities are difficult or impossible to measure at the precision required to demonstrate inflation for individual magnetically active systems.
+Observational evidence supports this interpretation, as hallmarks of activity such as  H$\alpha$ and X-ray emission and optical variability (e.g., large spot modulation, flares) are seen throughout the known SSG population \citep{geller17}.
+This interpretation is further supported by theoretical work demonstrating strong internal magnetic fields can inhibit convective energy transport \citep{2007A&A...472L..17C} and cause radius inflation \citep{2013ApJ...779..183F}.
+Treatments of the surface properties of magnetically active spotted stars also exhibit an underluminosity in the SSG region of a CMD \citep{somers20}.
+However, comparison between these model predictions and observations can be difficult.
 
-%The portion of the stellar surface covered with starspots is related to the amount of magnetic activity.
-The mere existence of starspot modulation betrays magnetic activity in stars.
-Starspots rupture the otherwise-pristine photospheric boundary conditions that regulate energy loss from stars.
-Starspots emit light of their own that can be captured and analyzed to quantify the impact of such boundary condition changes.
+In order to characterize the impact of magnetic fields and stellar activity on stellar evolution, we would ideally directly measure the stellar radius and internal magnetic field strength to calibrate how the star inflates due to inhibited convective energy transport, thereby explaining the CMD positions of SSGs and other active stars.
+Although ensembles of stars show evidence for an average magnetic radius inflation of 10--15\% \citep{2018AJ....155..225K,2018MNRAS.476.3245J}, these quantities are difficult or impossible to measure at the precision required to demonstrate inflation for individual magnetically active systems.
 
-Starspots have become a rich observational proxy for gauging the evolutionary state of stars that may be magnetically inflated without needing to estimate magnetic field strengths.
+Starspots have become a rich observational proxy for gauging the activity level of stars that may be magnetically inflated without needing to estimate magnetic field strengths.
 A full accounting of starspots requires careful consideration of geometrical degeneracies.
-Monochromatic lightcurves can indicate spotted stars \citep{2014ApJS..211...24M} but only provide a lower limit on the differential spot coverage between the most and least spotted hemispheres.
-Longitudinally symmetric starspot geometries evade detection in monochromatic lightcurves alone \citep{2019AJ....157...64L}.
+Monochromatic light curves can indicate the presence of starspots \citep{2014ApJS..211...24M} but only provide a lower limit on the differential spot coverage between the most- and least-spotted hemispheres.
+Longitudinally-symmetric starspot geometries evade detection in monochromatic light curves alone \citep{2019AJ....157...64L}.
 Disk-integrated covering fractions can be obtained from TiO band observations \citep{oneal96,fang2016,2019AJ....158..101M}, but measuring the spot configuration typically requires Doppler imaging or interferometry studies restricted to only the brightest and most nearby sources \citep{roettenbacher16}.
-Testing the next era of stellar activity models requires precision methodologies to measure spot-covering fractions of a larger number of targets, including SSGs.
+Testing the next era of stellar activity models requires precision methodologies to measure spot covering fractions of a larger number of targets, including SSGs.
 
@@
 The observed spectrum is therefore a composite of the spot and photosphere spectra, which can be deconvolved.
-\citet{gullysantiago17} extend the \texttt{Starfish} \citep{czekala15} spectral inference framework to support composite spectra and two-temperature probabilistic spectral decomposition.
-This deconvolution process constrains the spot-covering fraction as well as the spot and photosphere temperatures.
-The resulting disk-average spot properties anchor a simultaneous lightcurve flux to the starspot coverage fraction.
+\citet{gullysantiago17} extended the \texttt{Starfish}\footnote{\url{https://github.com/Starfish-develop/Starfish}} \citep{czekala15} spectral inference framework to support composite spectra and two-temperature probabilistic spectral decomposition.
+This deconvolution process constrains the spot covering fraction as well as the spot and photosphere temperatures.
+The resulting disk-average spot properties anchor a simultaneous light curve flux to the starspot coverage fraction.
 This anchored value serves as a benchmark for interpreting long-term (multi-year) flux variability \citep{neff95}.
-This strategy only requires high-resolution near-IR echelle spectroscopy and photometric monitoring, making it less demanding on telescope resources than either Doppler Imaging or interferometry.
-The technique is amenable to sources with narrow spectral lines ($v\sin{i}<10$ km/s) and stars with any stellar inclination, a distinct advantage over Doppler imaging.
-Altogether these advantages dramatically increase the number of sources for which we can observationally constrain spot-covering fractions.
+This strategy only requires high-resolution near-infrared (near-IR) echelle spectroscopy and photometric monitoring, making it less demanding on telescope resources than either Doppler imaging or interferometry.
+The technique is amenable to sources with narrow to moderate width spectral lines and stars with any stellar inclination, a distinct advantage over Doppler imaging.
+These advantages dramatically increase the number of sources for which we can observationally constrain spot covering fractions.
 
 In this paper we demonstrate the power of this methodology by focusing on a single SSG system, S1063 \citep{1977A&AS...27...89S} in the open cluster M67.
-This system is a prototypical SSG, with a single-lined spectroscopic orbital period of 18.4 days \citep{geller17}, an X-ray luminosity of $1.3\times10^{31}$ erg s$^{-1}$ \citep{vandenberg99}, and a variable lightcurve in \textit{K2} and ASAS-SN (Section~\ref{sec:K2lightcurve}).
+This system is a prototypical SSG, with a single-lined spectroscopic orbital period of $P_{\mathrm{orb}} = 18.38775\pm0.00009$ days, eccentricity $e = 0.207\pm0.009$, and a mass fraction of $1.4\pm0.04\times10^{-2}\;M_{\odot}$ \citep{geller2021}.
+S1063 has an X-ray luminosity of $1.3\times10^{31}$ erg s$^{-1}$ \citep{vandenberg99}, and a variable light curve in \textit{K2} and ASAS-SN (Section~\ref{sec:K2lightcurve}).
 \emph{Gaia} DR2 astrometry \citep{2016A&A...595A...1G, 2018A&A...616A...1G} indicates a parallax ($1.17\pm0.025 \;$mas) and proper motion for S1063 (\emph{Gaia} DR2 604921030968952832) consistent with other M67 members  approaching 100\% membership probability \citep{2018ApJ...869....9G}.
@@
 \subsection{IGRINS observations}
-A high resolution spectrum of S1063 was acquired with the $R=45,000$ Immersion Grating Infrared Spectrograph \citep[IGRINS;][]{park14} at UT 2015-04-26 $03^h29^m$ at the $2.7\;$m Harlan J.
+A high resolution spectrum of S1063 was acquired with the $R\sim45,000$ Immersion Grating Infrared Spectrograph \citep[IGRINS;][]{park14} at UT 2015-04-26 $03^h29^m$ at the $2.7\;$m Harlan J.
 Smith Telescope at McDonald Observatory.
@@
 The sky emission lines and telluric lines were removed with the IGRINS Pipeline Package  \citep[PLP;][]{jaejoonlee16} and a reference A0V star acquired nearby in time and airmass.
-The $H-$band spectra exhibited a signal-to-noise ratio of approximately $50$ per pixel.
-The $K-$band spectra possessed low $S/N$ and were excluded from further analysis.
+The $H$-band spectra exhibited a signal-to-noise ratio ($S/N$) of approximately 50 per pixel.
+The $K$-band spectra possessed low $S/N$ and were excluded from further analysis.
+The observation occurred at a binary orbital phase of 0.148 \citep[][]{geller2021}, near an extreme of the RV variation.
 
-\begin{figure*}[ht]
+\subsection{K2 superstamp light curves}
+The \emph{Kepler} spacecraft targeted S1063 (EPIC 211414597) during the \emph{K2} mission \citep{howell14} in Campaigns 5, 16, and 18 as part of the M67 superstamps.
+The instrumental point spread function (PSF) of S1063 fell entirely within the oversized \emph{K2} target pixel files in Campaign 5 (K2 Custom Aperture ID 200008674, channel 13) and Campaign 18 (K2 Custom Aperture ID 200233338).
+Aperture photometry was conducted with interactively-assigned custom apertures using the \texttt{lightkurve.interact()} feature \citep{geert_barentsen_2019_2565212}.
+The apertures were chosen to minimize flux loss out of the aperture due to spacecraft-induced image motion, while avoiding low-$S/N$ pixels and the wings of adjacent PSFs (\emph{c.f.} Figure~\ref{fig:imaging}).
+The Campaign 16 source PSF overlapped the edge of Custom Aperture ID 200200534, therefore a mosaic of adjacent superstamps was assembled before conducting aperture photometry.
+We detrended motion-induced image artifacts with the Self Flat Field algorithm \citep{vanderburg14} implemented in \texttt{lightkurve}.
+
+\begin{figure*}[]
   \centering
   \begin{tabular}{ccccc}
-    \subfloat{\includegraphics[width=1in]{figures/S1063_60x60arcsec_PS1_g.png}} &
-    \subfloat{\includegraphics[width=1in]{figures/S1063_60x60arcsec_2M_J.png}} &
-    \subfloat{\includegraphics[width=1in]{figures/S1063_60x60arcsec_K2_C5.png}} &
-    \subfloat{\includegraphics[width=1in]{figures/S1063_60x60arcsec_K2_C16.png}} &
-    \subfloat{\includegraphics[width=1in]{figures/S1063_60x60arcsec_K2_C18.png}} \\
+    \subfloat{\includegraphics[width=1in]{S1063_60x60arcsec_PS1_g.png}} &
+    \subfloat{\includegraphics[width=1in]{S1063_60x60arcsec_2M_J.png}} &
+    \subfloat{\includegraphics[width=1in]{S1063_60x60arcsec_K2_C5.png}} &
+    \subfloat{\includegraphics[width=1in]{S1063_60x60arcsec_K2_C16.png}} &
+    \subfloat{\includegraphics[width=1in]{S1063_60x60arcsec_K2_C18.png}} \\
   \end{tabular}
 \caption{Imaging of S1063 in $60'' \times 60''$ postage stamps.
-\emph{left-to-right:} Pan-STARRS $g$-band co-added image contemporaneous with C16; 2MASS $J-$band; K2 Campaigns 5, 16, 18 from Full Frame Images.
+\emph{Left-to-right:} Pan-STARRS $g$-band co-added image contemporaneous with C16; 2MASS $J-$band; K2 Campaigns 5, 16, 18 from Full Frame Images.
 S1063 is sufficiently separated from nearby sources in the coarse \emph{Kepler} imaging.}
@@
 
-\subsection{K2 superstamp lightcurves}
-The \emph{Kepler} spacecraft targeted S1063 (EPIC 211414597) during the \emph{K2} mission \citep{howell14} in Campaigns 5, 16, 18 as part of the M67 superstamps.
-The instrumental point spread function (PSF) of S1063 fell entirely within the oversized K2 target pixel files in Campaign 5 (K2 Custom Aperture ID 200008674, channel 13) and Campaign 18 (K2 Custom Aperture ID 200233338).
-Aperture photometry was conducted with interactively-assigned custom apertures using the \texttt{lightkurve.interact()} feature \citep{geert_barentsen_2019_2565212}.
-The apertures were chosen to minimize flux-loss out of the aperture due to spacecraft-induced image motion, while avoiding low-$S/N$ pixels and the wings of adjacent PSFs (\emph{c.f.} \ref{fig:imaging}).
-The Campaign 16 source PSF overlapped the edge of Custom Aperture ID 200200534, therefore a mosaic of adjacent superstamps was assembled before conducting aperture photometry.
-We detrended motion-induced image artifacts with the Self Flat Field (SFF) algorithm \citep{vanderburg14} implemented in \texttt{lightkurve}.
-
 \subsection{Ground-based photometric monitoring}
-We retrieved All-Sky Automated Survey for Supernovae \citep[ASAS-SN;][]{shappee14} lightcurves from the Sky Portal \citep{2017PASP..129j4502K}.
-The lightcurves contained 758 epochs of $V$-band photometry spanning 2013-2018 (source ASASSN-V J085113.44+115139.7) and 823 epochs of $g$-band photometry spanning mid-2017--2018.
+We retrieved All-Sky Automated Survey for Supernovae \citep[ASAS-SN;][]{shappee14} light curves from the Sky Portal \citep{2017PASP..129j4502K}.
+The light curves contained 758 epochs of $V$-band photometry spanning 2014--2018 (ASASSN-V J085113.44+115139.7) and 823 epochs of $g$-band photometry spanning mid-2017--2018.
 The $\sim8''$ ASAS-SN pixels may cause some PSF blending of the nearby-albeit-fainter source seen at the bottom of Figure \ref{fig:imaging}.
 The pixel images were not available to evaluate the extent of blending.
-The nearby source was verified to be non-variable in K2 data, so such blending would be expected to subdue the overall ASAS-SN lightcurve modulations while keeping the period and phase in-tact.
+Nearby sources were verified to be non-variable in \emph{K2} data, so such blending would be expected to subdue the overall ASAS-SN light curve modulations while keeping the period and phase intact.
 
 \subsection{Inter-campaign relative photometry with K2 Full Frame Images}\label{sec:K2lightcurve}
-
-Stellar activity cycles on S1063 can secularly change the stellar brightness on timescales comparable to the separation of the three campaigns of \emph{K2} observations.
+Variation in stellar activity on S1063 can potentially change the stellar brightness on timescales comparable to the separation of the three campaigns of \emph{K2} observations.
 The comparison of flux levels among repeated \emph{K2} campaigns requires accounting for detector responsivity degradation on these same timescales.
@@
 
-To account for sensitivity changes, we calibrate the system-integrated throughput for \emph{Kepler} detector channels including the M67 field for Campaigns 5, 16, and 18.
-We measure aperture photometry for approximately 2000 isolated reference stars from the Full Frame Images, keeping only those stars that were observed in all three campaigns.
-Compared to Campaign 5, the reference stars have a median flux of $93.9\pm4.2\%$ in Campaign 16 and a median flux of $98.2\pm2.8\%$ in Campaign 18.
-Campaigns 5 and 18 were observed on the same detector channel while a different detector channel was used for Campaign 16, therefore the C16 offset is not a significant measure of detector degradation across campaigns.
-We use a Lomb-Scargle periodogram on each campaign independently and recover the same dominant period of 23.5 days in all three campaigns.
-The phase-folded lightcurves and periodograms are shown in Figure~\ref{fig:periodogram}.
-
-\begin{figure*}[ht]
+\begin{figure*}[]
     \centering
     \begin{tabular}{cc}
-      \includegraphics[width=3in]{figures/AllCampaigns_Periodogram.pdf}   & \includegraphics[width=3in]{figures/AllCampaigns_Phased_Lightcurve.pdf}  \\
+      \includegraphics[width=3in]{AllCampaigns_Periodogram.pdf}   & \includegraphics[width=3in]{AllCampaigns_Phased_Lightcurve.pdf}  \\
     \end{tabular}
-    \caption{On the right, a Lomb-Scargle Periodogram of the lightcurve for each \emph{K2} campaign and on the left, the corresponding phased \emph{K2} lightcurves.
-The average period associated with maximum power across all three campaigns is P = 23.5 days.
+    \caption{On the right, a Lomb-Scargle periodogram of the light curve of S1063 for each \emph{K2} campaign and on the left, the corresponding phased \emph{K2} light curves.
+The average period associated with maximum power across all three campaigns is $P_{\mathrm{rot}} = 23.5 \pm 0.2$ days.
 }
@@
 
+To account for sensitivity changes, we calibrate the system-integrated throughput for \emph{Kepler} detector channels including the M67 field for Campaigns 5, 16, and 18.
+We measure aperture photometry for approximately 2000 isolated reference stars from the Full Frame Images (FFIs), keeping only those stars that were observed in all three campaigns.
+Compared to Campaign 5, the reference stars have a median flux of $93.9\pm4.2\%$ in Campaign 16 and a median flux of $98.2\pm2.8\%$ in Campaign 18.
+Campaigns 5 and 18 were observed on the same detector channel while a different detector channel was used for Campaign 16, therefore the Campaign 16 offset is not a significant measure of detector degradation across campaigns.
+We use a Lomb-Scargle periodogram \citep{LombScargle} on each campaign independently and find the rotation period to be consistent across all campaigns, with a mean rotation period of $P_{\mathrm{rot}} = 23.5 \pm 0.2$ days.
+The rotation period is longer than the known binary period of $P_{\mathrm{orb}} = 18.38775$ days because the slightly eccentric ($e = 0.2$) system is not yet fully synchronized.
+This is expected as the tidal circularization period in M67 is approximately 11 days \citep{geller2021}.
+The periodograms and phase-folded light curves are shown in Figure~\ref{fig:periodogram}.
+We note that the light curves of all three campaigns exhibit flaring events.
+
 \begin{figure*}[ht]
   \centering
-  \includegraphics[width=0.95\textwidth]{figures/2020_K2_ASASSN_lcurve_2panel.pdf}
-\caption{Four year lightcurve for S1063, normalized to a maximum flux of 1.00 as denoted by the thick gray dashed line.
+  \includegraphics[width=0.95\textwidth]{2020_K2_ASASSN_lcurve_2panel.pdf}
+\caption{Four year light curve for S1063, normalized to a maximum flux of 1.00 as denoted by the thick gray dashed line.
 The mean flux of 0.895 is shown with the gray dotted line.
@@
 
-%INTRO TEXT:
-%Starspots emit a spectrum of their own at a lower temperature and with distinct absorption features compared to the ambient photosphere.
-The observed spectrum is a composite of the spot and photosphere spectra and can therefore be deconvolved.
-This deconvolution constrains the spot-covering fraction as well as the spot and photosphere temperatures.
-This is possible by performing a two-temperature probabilistic spectral decomposition using the spectral inference framework \texttt{Starfish} \citep{czekala15}, recently extended to support composite spectra \citep{gullysantiago17}.
-The resulting spot characterization can be used to anchor lightcurve information, providing insight into the overall stellar activity level and constraining the long-term spot coverage \citep{neff95}.
-This strategy only requires high-resolution echelle spectroscopy and photometric monitoring, dramatically increasing the number of sources for which we can observationally constrain spot-covering fractions.
-
-%Constraining starspot covering fraction for stars such as S1063 requires a careful combination of lightcurve interpretation and spectral analysis using spectral decomposition tools such as \texttt{Starfish} \citep{czekala15} to benchmark epochs of starspot coverage in long-term photometric monitoring.
 Characterizing the long-term starspot coverage of S1063 requires connecting coarse ground-based and precision space-based photometry---ASAS-SN and \emph{K2}---alongside precision IGRINS spectroscopy.
@@
 
-\subsection{Joint modeling of ASAS-SN and \emph{K2} Lightcurves}
+\subsection{Joint modeling of ASAS-SN and \emph{K2} light curves}
 
-We attempt to unify the ASAS-SN, \emph{K2} long cadence, and \emph{K2} FFI data points into a single global lightcurve.
-The ASAS-SN $V$-band and \emph{K2} photometric system throughputs share significant wavelength coverage and are treated as adequately similar for this purpose.
+We attempt to unify the ASAS-SN, \emph{K2} long cadence, and \emph{K2} FFI data points into a single global light curve.
+The ASAS-SN $V$-band and \emph{K2} photometric system throughputs share significant, but not identical, wavelength coverage.
+We investigate the effect of bandpass differences in Section~\ref{sec:lightcurveinterp}, and treat the Kepler and $V$ bands as adequately similar for this purpose.
 Our methodology can be thought of as learning a bandpass or ``notch'' filter from the \emph{K2} data and applying it to the ASAS-SN data.
-The advantage of this approach is to combine near-in-time ASAS-SN data points in a way that preserves that correlation structure known from \emph{K2}, without distorting the lightcurve peaks and valleys as could be expected from an unscrupulous binning procedure.
-In the end, a global lightcurve constructed in this way can guide the eye during the times when K2 data is unavailable and ASAS-SN data are sparse-but-still-informative.
+The advantage of this approach is to combine near-in-time ASAS-SN data points in a way that preserves the correlation structure known from \emph{K2} without distorting the light curve peaks and valleys through a binning procedure.
+A global light curve constructed in this way can guide the eye during times when \emph{K2} data is unavailable and ASAS-SN data are sparse, but still informative.
 
-We jointly modeled the ASAS-SN and \emph{K2} lightcurves as a damped, driven Simple Harmonic Oscillator (SHO) Gaussian Process (GP) with \texttt{celerit\`e} \citep{2017AJ....154..220F}.
+We jointly modeled the ASAS-SN and \emph{K2} light curves as a damped, driven Simple Harmonic Oscillator (SHO) Gaussian Process (GP) with \texttt{celerit\`e} \citep{2017AJ....154..220F}.
 We tuned a two-period GP model with the harmonic component possessing roughly half the period $P_H\sim12.5\;\mathrm{d}$ of the fundamental period $P_0=23.5\;\mathrm{d}$.
-The harmonic overtone frequency can be seen by eye in Figure \ref{fig:lightcurve}, as the \emph{K2} lightcurves appear more structured than a pure sine wave.
+The harmonic overtone frequency can be seen by eye in Figure \ref{fig:lightcurve}, as the \emph{K2} light curves appear more structured than a pure sine wave.
 We fit for a correlation amplitude and SHO quality factor for each periodic GP term.
-We found consistent best fit values when \emph{K2} lightcurves were fitted on a per-campaign basis.
-We then fit the three campaigns \emph{simultaneously} in the following way.
-We added an additional non-periodic secular trend GP component to capture the campaign-to-campaign mean-level variation.
-We set the overall vertical registration of the \emph{K2} lightcurves such that the ASAS-SN and Campaign 16 trends match, since M67 was contemporaneously observable from the ground for the entire duration of K2 Campaign 16.
+We found consistent best fit values when \emph{K2} light curves were fitted on a per-campaign basis.
+We then fit the three campaigns simultaneously by adding an additional non-periodic secular trend GP component to capture the campaign-to-campaign mean-level variation.
+We set the overall vertical registration of the \emph{K2} light curves such that the ASAS-SN and Campaign 16 trends match, since M67 was contemporaneously observable from the ground for the entire duration of Campaign 16.
 The uncertainty in the inter-campaign offsets calculated in Section~\ref{sec:K2lightcurve} is larger than the internal precision of the \emph{K2} photometry, so we adjust the Campaign 5 data within the offset uncertainty to match the approximately one week of temporal overlap with ASAS-SN.
 
-Finally, we transfer the pre-trained model parameters to a GP based on the ASAS-SN photometry.
-We evaluate the GP at all time points in Figure \ref{fig:lightcurve} including the seasonal data gaps.
-This trend appears in Figure \ref{fig:lightcurve} as the dark orange line with an orange shaded standard confidence region.
+Finally, we transfer the model parameters pre-trained from the \emph{K2} fit to a GP based on the ASAS-SN photometry.
+We attempted to apply a GP to the \emph{K2} and ASAS-SN data simultaneously but the result had numerical artifacts due to quality and cadence differences between the datasets.
+We evaluate the ASAS-SN GP at all time points in Figure~\ref{fig:lightcurve} including the seasonal data gaps.
+This trend appears in Figure~\ref{fig:lightcurve} as the dark orange line with an orange shaded standard confidence region.
 This trendline guides the eye to see broad secular changes to the amplitude encoded in the noisy ASAS-SN data, with a global maximum peak-to-valley amplitude of 17\% occurring near 2017 January, and global minimum peak-to-valley of 3\% occurring shortly before the IGRINS measurement.
 
-\subsection{IGRINS two-temperature spectral decomposition}
+\subsection{IGRINS Spectral Analysis}
+
+\subsubsection{Broadening Function Analysis}
+
+To measure the radial velocity of S1063 and to search for spectroscopic signatures of its binary companion at NIR wavelengths, we compute a spectral-line broadening function (BF) for the IGRINS spectrum \citep[e.g.,][]{Tofflemireetal2019}.
+The BF is a linear inversion of the observed spectrum with a narrow-lined spectral template.
+It is a profile that, when convolved with the narrow-lined template, reproduces the observed spectrum.
+As a result, the BF represents the average absorption line profile of stellar components present in the spectrum, carrying information on their radial velocities and rotational broadening (i.e., $v \sin i$).
+
+Using a 5000 K, $\log g$ = 4.0 pre-computed PHOENIX model \citep{husser13} as our narrow-lined template, we compute the BF for each spectral order considered in Section \ref{sec:starfish} below (9 in total).
+We then combine them into a single, high signal-to-noise BF.
+The resultant BF contains only one significant peak ($>3 \sigma$), indicating that we do not detect the binary companion.
+We fit a rotationally-broadened line profile \citep[][]{gray_book} to the S1063 component, measuring a barycentric radial velocity of 14.6$\pm$0.2 km s$^{-1}$ and a $v \sin i$ of $11.3\pm0.7$ km s$^{-1}$.
+The radial velocity agrees with the \citet{geller2021} orbital solution for the given orbital phase.
+
+\subsubsection{Two-Temperature Spectral Decomposition}
+\label{sec:starfish}
 
 The IGRINS observation epoch can be seen as the vertical blue line in Figure~\ref{fig:lightcurve}.
-The filling factor derived at this moment will belie the filling factor projected forward and backward in time.
+The filling factor derived at this moment will serve as the anchor for the filling factor projected forward and backward in time.
 
@@
 Here, the two temperature components are labeled as $T_{\mathrm{spot}}$ and $T_{\mathrm{amb}}$ for the starspot and ambient photospheric emission, respectively, with a filling factor $f$ defined as the ratio of disk-integrated projected surface area of the spot groups to the projected area of the star.
+Given that we do not detect the binary companion in the BF above, and at the observed binary phase we expect the primary and secondary to have an RV separation of more than  50 km s$^-1$, we are confident our single-velocity spectral decomposition of S1063 is not systematically impacted by the secondary.
 
@@
 The pre-defined grid ranges place uniform priors over their domain.
-Additionally, a threshold of 4500 K separated the allowed domains for the spot and ambient temperatures, yielding uniform priors $3000 < T_{\mathrm{spot}} \; (K) < 4500 $ and $4500 < T_{\mathrm{amb}} \; (K) < 5300$.
-
-\subsubsection{MCMC convergence and posterior predictive checks}
+Additionally, a threshold of 4500 K separated the allowed domains for the spot and ambient temperatures, yielding uniform priors $3000 < T_{\mathrm{spot}} \; (\mathrm{K}) < 4500 $ and $4500 < T_{\mathrm{amb}} \; (\mathrm{K}) < 5300$.
 
@@
 Collectively, these discrepant or uninformative spectral orders were removed from future analysis, yielding a total of nine preserved spectral orders, shown in Figure \ref{fig:IGRINS_spectra3x3}.
-All spectral orders were consistent with a $v\sin{i}=10 \;\mathrm{km/s}$, with typical per-order $1-\sigma$ uncertainties of $0.2-1.0 \;\mathrm{km/s}$.
-The per-order estimates for radial velocity were all consistent with $v_z=44\;\mathrm{km/s}$ at the measurement epoch, uncorrected for barycentric motion.
+The per-order estimates for radial velocity are all consistent with $v_z=44$ km s$^{-1}$ at the measurement epoch, uncorrected for barycentric motion.
+All spectral orders except for $m=106$ are consistent with a $v\sin{i}=10$ km s$^{-1}$, with typical per-order 1-$\sigma$ uncertainties of 0.2--1.0 km s$^{-1}$.
+The fit to order 106 finds $v\sin{i}=15\pm3$ km s$^{-1}$.
+As can be seen in Figure~\ref{fig:IGRINS_spectra3x3}, this particular order contains few significant spectral lines.
+Although the fit converged and is included in our subsequent analysis, this order in particular demonstrates some of the systematic uncertainties in this process.
 
@@
  \centering
- \includegraphics[width=0.90\textwidth]{figures/H_band_spectra_3x3.pdf}
- \caption{Nine $H-$band IGRINS echelle orders showing two-component spectral decomposition of collective starspot photospheric emission, labeled with the corresponding order number $m$.
+ \includegraphics[width=0.92\textwidth]{H_band_spectra_3x3.pdf}
+ \caption{Nine $H$-band IGRINS echelle orders showing two-component spectral decomposition of collective starspot photospheric emission, labeled with the corresponding order number $m$.
 The starspot spectrum (thick red line) and ambient photosphere spectrum (dotted blue line) combine to form the composite spectrum (solid purple line) that resembles the observed spectrum (thick gray line).
 The starspot and ambient components can share similar spectral structure, leading to a range of filling factors and temperatures ranges with nearly equivalent composite spectra; here we present a single random draw from the MCMC posterior, not a ``best fit''.
-The cool and hot temperatures $T_{\textrm{s}}$ and $T_{\textrm{amb}}$ for each draw show variety consistent with the fitting uncertainty.
-The corresponding spot filling factor, $f_{\textrm{s}}$, is also shown for each specific random draw.
-Unexplained spectral structure and over- and under- fitting of spectral lines arises from a combination of PHOENIX model imperfections, possible magnetic Zeeman broadening, and other model mis-specifications.}
+The cool and hot temperatures $T_{\mathrm{s}}$ and $T_{\mathrm{amb}}$ for each draw show variety consistent with the fitting uncertainty.
+The corresponding spot filling factor, $f_{\mathrm{s}}$, is also shown for each specific random draw.
+Unexplained spectral structure and over- and under-fitting of spectral lines arises from a combination of PHOENIX model imperfections, possible magnetic Zeeman broadening, and other model mis-specifications.}
  \label{fig:IGRINS_spectra3x3}
@@
 Across all nine orders, the median filling factor value is 32\% with a standard deviation of 7\%, with a corresponding spot temperature of $4000 \pm 200$ K.
-The ambient photosphere temperature associated with this spot signature varies from order-to-order and is in the range of 5000 $-$ 5300 K, with a median value of 5200 K.
-These values are broadly consistent with a spectroscopic temperature of 5000 K for S1063 determined by \citet{mathieu03} determined from visible-wavelength spectra.
-Visible wavelength spectra principally perceive the ambient photosphere, due to the near-zero starspot contrast at those wavelengths.
-Therefore the most reliable ambient photosphere estimate likely stems from the visible-based measurement, and not our near-IR-based estimate.
+We note that although the fit results for order 106 appear disparate in Figure~\ref{fig:tspot_fillingfactor3x3}, likely due to systematic effects, excluding order 106 from the analysis does not change the median filling factor or spot temperature values.
+The ambient photosphere temperature associated with this spot signature varies from order-to-order and is in the range of 5000--5300 K, with a median value of 5200 K.
+These values are broadly consistent with a spectroscopic temperature of 5000 K for S1063 from by \citet{mathieu03} determined from visible-wavelength spectra.
 
 \subsubsection{Light curve interpretation}
-The ASAS-SN and \textit{K2} Campaign 5 data of S1063 (Figure~\ref{fig:lightcurve}) indicate that the IGRINS observation was coincidentally acquired near its modest local maximum at an overall flux level of 91.2\%.
+\label{sec:lightcurveinterp}
+The ASAS-SN and \textit{K2} Campaign 5 data of S1063 (Figure~\ref{fig:lightcurve}) indicate that the IGRINS observation was coincidentally acquired near the modest local maximum at an overall flux level of 91.2\%.
 This is close to the overall 89.5\% mean flux level, where the 100\% flux level is defined as the global maximum over the four-year period covered by ASAS-SN and \textit{K2}.
-The lightcurve exhibits relatively modest variability at the time of the IGRINS observations with merely 3\% peak-to-valley variation compared to its global largest variation of almost 17\% as observed around 2017 January.
+The light curve exhibits relatively modest variability just before the time of the IGRINS observation with merely 3\% peak-to-valley variation compared to the largest global variation of almost 17\% as observed around 2017 January.
 
-For a first-order interpretation of lightcurve amplitudes, we posit that the lightcurve is starspot-dominated as opposed to facula-dominated.
+For a first-order interpretation of light curve amplitudes, we posit that the light curve is starspot-dominated as opposed to facula-dominated.
 Under this assumption, minimum light corresponds to the largest blockage of ambient flux and therefore the largest starspot coverage on the instantaneous hemisphere projected towards the observer \citep{basri18}.
@@
 
-If S1063 was spot-free at the time of the global lightcurve maximum the epoch of IGRINS observation would correspond to starspots blocking 8.8\% of the total instantaneous stellar flux (100\% $-$ 91.2\% $=$ 8.8\% blocked flux at the time of observation), assuming non-emitting starspots.
+If S1063 was spot-free at the time of the global light curve maximum, the epoch of IGRINS observation would correspond to starspots blocking 8.8\% of the total instantaneous stellar flux (100\% $-$ 91.2\% $=$ 8.8\% blocked flux at the time of observation), assuming non-emitting starspots.
 However, starspots are emitting and effectively filling in some of the light that is ``blocked''.
 This non-zero starspot emission demands that the spot covering fraction must be greater than 8.8\% at the time of the IGRINS observation.
-Adopting an ambient photosphere temperature of 5200 K and a spot temperature of 4000 K, the projected spot coverage of S1063 must be at least 13\% to account for the 8.8\% flux loss in the $V$-band.
+Adopting an ambient photosphere temperature of 5200 K and a spot temperature of 4000 K, the projected spot coverage of S1063 must be at least 13\% to account for the 8.8\% flux loss in the ASAS-SN optical band.
 
-This 13\% spot coverage is a minimum value based on an assumption that the global maximum lightcurve flux results from an un-spotted star.
-Our spectral inference results indicate the spot coverage at the time of the IGRINS observation was 32\%.
-Therefore the spot coverage of S1063 was approximately 20\% at maximum light over this 4-year period, and not zero as a first-order interpretation of the lightcurve would imply.
+This 13\% spot coverage is a minimum value based on an assumption that the global maximum light curve flux results from an un-spotted star.
+Our spectral inference results indicate the spot coverage at the time of the IGRINS observation was $32\pm7$\%.
+Therefore the spot coverage of S1063 was approximately 20\% at maximum light over this four-year period, and not zero as a first-order interpretation of the light curve would imply.
 
-The presence of starspots at the lightcurve maximum acts as a starspot baseline for interpreting the lightcurve.
-Over the four years shown in Figure~\ref{fig:lightcurve}, the average flux variation is approximately 5\%, corresponding to an average spot covering fraction variation from each observed hemisphere of $\pm$8\%.
-The lightcurve exhibits a global flux minimum 10\% lower than the flux at the time of the IGRINS observation, requiring a spot filling factor close to 45\% on the projected hemisphere at that time.
+The presence of starspots at the light curve maximum acts as a starspot baseline for interpreting the light curve.
+Over the four years shown in Figure~\ref{fig:lightcurve}, the average flux variation is approximately 5\%, corresponding to an average spot covering fraction variation between each observed hemisphere of $\pm$8\%.
+The light curve exhibits a global flux minimum 10\% lower than the flux at the time of the IGRINS observation, requiring a spot filling factor close to 45\% on the projected hemisphere at that time.
 
-We therefore determine that over the time period from 2014--2018 S1063 has possessed a range of 20--45\% coverage fraction of spots, with an average close to 30\%.
+We therefore determine that over the time period from 2014--2018 S1063 possessed a range of 20--45\% spot coverage fraction on the projected hemisphere, with an average close to 30\%.
 The IGRINS observation occurring near the mean global flux level fortuitously allows a robust characterization of the average state of S1063.
@@
 
-\begin{table}[]
+Finally, we investigate how bandpass differences between the broad K2-bandpass and the ASAS-SN $V$-band may impact our light curve analyses.
+The $V$-band is bluer on average than the wider and red-weighted K2-bandpass, so we expect the presence of starspots to result in slightly more contrast in $V$ than in the K2-band, as more spot coverage results in less bluer flux.
+We confirm this by integrating spotted spectra (assuming 5200 K ambient photosphere and 4000 K spots) over a range of filling factors against both transmission curves.
+We find that a 1\% change in filling factor results in a $0.78$\% loss of flux in K2 and an $0.83$\% loss of flux in $V$-band.
+This could result in an approximately 6\% higher light curve amplitude observed in $V$-band than would be observed with K2.
+However, we emphasize that our global light curve trends are determined using only the ASAS-SN $V$-band photometry, therefore the slight discrepancy does not impact our results.
+The quality of the ASAS-SN data is not sufficient to confirm this expected $\sim6$\% amplitude difference between $V$-band and K2.
+
+\begin{table*}[]
 \label{tab:s1063parameters}
@@
 \end{tabular}
-\end{table}
+\end{table*}
 
@@
    \begin{tabular}{ccc}
-     \subfloat{\includegraphics[width=2in]{figures/H_band_Tspot_fillingfactor_m119_new.pdf}} &
-     \subfloat{\includegraphics[width=2in]{figures/H_band_Tspot_fillingfactor_m118_new.pdf}} &
-     \subfloat{\includegraphics[width=2in]{figures/H_band_Tspot_fillingfactor_m116_new.pdf}} \\
-     \subfloat{\includegraphics[width=2in]{figures/H_band_Tspot_fillingfactor_m114_new.pdf}} &
-     \subfloat{\includegraphics[width=2in]{figures/H_band_Tspot_fillingfactor_m113_new.pdf}} &
-     \subfloat{\includegraphics[width=2in]{figures/H_band_Tspot_fillingfactor_m110_new.pdf}} \\
-     \subfloat{\includegraphics[width=2in]{figures/H_band_Tspot_fillingfactor_m109_new.pdf}} &
-     \subfloat{\includegraphics[width=2in]{figures/H_band_Tspot_fillingfactor_m107_new.pdf}} &
-     \subfloat{\includegraphics[width=2in]{figures/H_band_Tspot_fillingfactor_m106_new.pdf}}
+     \subfloat{\includegraphics[width=2in]{H_band_Tspot_fillingfactor_m119_new.pdf}} &
+     \subfloat{\includegraphics[width=2in]{H_band_Tspot_fillingfactor_m118_new.pdf}} &
+     \subfloat{\includegraphics[width=2in]{H_band_Tspot_fillingfactor_m116_new.pdf}} \\
+     \subfloat{\includegraphics[width=2in]{H_band_Tspot_fillingfactor_m114_new.pdf}} &
+     \subfloat{\includegraphics[width=2in]{H_band_Tspot_fillingfactor_m113_new.pdf}} &
+     \subfloat{\includegraphics[width=2in]{H_band_Tspot_fillingfactor_m110_new.pdf}} \\
+     \subfloat{\includegraphics[width=2in]{H_band_Tspot_fillingfactor_m109_new.pdf}} &
+     \subfloat{\includegraphics[width=2in]{H_band_Tspot_fillingfactor_m107_new.pdf}} &
+     \subfloat{\includegraphics[width=2in]{H_band_Tspot_fillingfactor_m106_new.pdf}}
    \end{tabular}
@@
     \centering
-    \includegraphics[width=0.45\linewidth]{figures/S1063_GaiaCMD.png}
-    \includegraphics[width=0.45\linewidth]{figures/S1063_2MASS_CMD.png}
+    \includegraphics[width=0.45\linewidth]{S1063_GaiaCMD.png}
+    \includegraphics[width=0.45\linewidth]{S1063_2MASS_CMD.png}
     \caption{On the left is a \textit{Gaia} color-magnitude diagram (CMD) that shows members of M67 (gray points) with SSG S1063 highlighted (red square).
@@
 Here, we compare the photometry of S1063 to spotted SPOTS evolutionary tracks \citep{somers20}.
-SPOTS models assume the presence of star spots inhibits local flux that must escape through ambient (non-spotted) regions of the stellar surface.
+SPOTS models assume the presence of starspots inhibits local flux that must instead escape through ambient (non-spotted) regions of the stellar surface.
 To determine photometric conversions from the stellar structure models, all SPOTS evolutionary tracks adopt a two-temperature surface with a fixed ratio of spot to ambient temperature of 0.8.
-We use optical photometry from \textit{Gaia} and near-infrared photometry from 2MASS for this comparison, showing CMDs of M67 members compared to the shaded region in the each CMD populated by SPOTS tracks in Figure~\ref{fig:CMDs}.
-As expected, spotted sub-giant models appear redder and fainter than the sub-giant branch in both CMDs.
+To compare these models against S1063 we use optical photometry from Gaia \citep{2016A&A...595A...1G,2018A&A...616A...1G} and near-IR photometry from 2MASS \citep{2mass}.
+In Figure~\ref{fig:CMDs} we show CMDs of M67 members \citep{geller2015} compared to the shaded region in each CMD populated by SPOTS tracks.
+As expected, spotted subgiant models appear redder and fainter than the subgiant branch in both CMDs.
 We also show the unspotted SPOTS evolutionary track in each CMD as a black solid line.
-This unspotted model fits the typical subgiant branch of M67 in the 2MASS CMD, however this is not true when using Gaia photometry.
+This unspotted model generally fits the typical subgiant branch of M67 in the 2MASS CMD, however this is not true when using Gaia photometry.
 In the Gaia CMD the unspotted SPOTS model has a more extended subgiant branch and redder giant branch than observed in the cluster.
@@
 reddening, distance, turnoff mass, metallicity).
-It may be due to internal model physics (i.e.
+It may be due to internal model physics (e.g.
 choice of mixing length) or an error introduced when calculating model colors in the Gaia bandpasses.
+Despite this small discrepancy, we include these models as a helpful illustration of how starspots may impact evolutionary tracks on a CMD.
 
 Photometry for S1063 from both Gaia and 2MASS is roughly consistent with the region populated by SPOTS evolutionary tracks.
-Generally, the spot covering fraction adopted from this model comparison would result in larger spot filling factors of approximately 50--85\%, depending on the photometry used, compared to the $32\pm7$\% filling factor found in this work.
-Another photometric comparison using a two-temperature SED fit of S1063 \citep{leiner17} finds a spot filling factor of 40\%, which is also in moderate disagreement with our results.
+Generally, the spot covering fraction adopted from this model comparison would result in larger spot filling factors of approximately 50--85\%, depending on the photometry used.
+\citet{leiner17} also conclude similarly large filling factors would be necessary to reproduce the spectral energy distribution of S1063, compared to the $32\pm7$\% filling factor found in this work.
 
-%The optical photometry is most consistent with a SPOTS model with a $\sim50\%$ spot filling factor, slightly higher than the $32\%$ we find from the spectroscopic deconvolution.
-The 2MASS photometry indicates an even larger filling factor, falling in between the 51\% and 85\% SPOTS models.
-We note that while the unspotted SPOTS evolutionary track (black line in Figure~\ref{fig:CMDs}) fits the turnoff of M67 well when using 2MASS photometry, the model has a more extended subgiant branch and redder giant branch compared to the \textit{Gaia} photometry.
-This discrepancy is not resolvable by changing cluster parameters (i.e.
-reddening, distance, turnoff mass, metallicity).
-It may be due to internal model physics (i.e.
-choice of mixing length) or an error introduced when calculating model colors in the Gaia bandpasses.
-Due to this improper calibration, the spot filling factor inferred from comparisons with the \textit{Gaia} photometry may be skewed towards lower spot filling factors.
-This could explain the higher spot filling factor inferred from the 2MASS photometry, where the unspotted models are a better fit to the cluster turnoff.
-
-We believe that some of the discrepancy between our results and those predicted by the SPOTS models may be due to limitations of the SPOTS models as diagnostic tools for single sources.
-However, observational biases may also impact the filling factors determined through spectroscopic and photometric methods.
+Observational biases may impact the filling factors determined through spectroscopic and photometric methods.
 Our near-IR spectral decomposition technique is most sensitive to detecting a ``sweet-spot'' in starspot contrast: cool enough to exhibit a spectrum that is qualitatively distinct from the ambient photosphere, but not so cool as to possess vanishing specific intensity.
-So for example, our technique might readily perceive the penumbra of the starspot, while ignoring the much cooler and darker umbra flux contribution \citep{1981ApJ...250..327V}.
-This bias would lead our technique to systematically underestimate the total starspot coverage, rendering our claimed filling factor estimate as a lower limit.
-Spectral decomposition techniques are more sensitive to the warmer spot components and may therefore be constraining the prenumbra filling factor, which would be larger than the umbra filling factor.
-However, we do not know if the spot morphology of SSGs follows this assumption.
-If instead SSGs have a smaller ratio of prenumbra to umbra this spectral technique would under-sample the total spot coverage on the stellar surface.
+As a result, spectral decomposition techniques are more sensitive to warmer spot components and may therefore be constraining the prenumbra rather than umbra filling factor \citep{1981ApJ...250..327V}.
+Depending on the ratio of prenumbra to umbra this could lead our technique to systematically underestimate the total starspot coverage, placing our filling factor constraint as a lower limit.
 
 Other second-order effects could be at play.
-Spots could hypothetically exhibit a perceived wavelength dependence of their boundaries that would lead to apparent discrepancies in spot filling factors across photometric and spectroscopic determinations at different wavebands.
-Such effects are not well-understood for stars other than the Sun, where the exact boundaries of active regions can be examined in different filters.
+Spot boundaries could hypothetically exhibit a perceived wavelength dependence leading to apparent discrepancies in spot filling factors across photometric and spectroscopic determinations at different wavebands.
+Such effects are not well understood for stars other than the Sun, where the exact boundaries of active regions can be examined in different filters.
 We note that photometry collected at different epochs can also degrade the precision of SED-based photometric filling factors.
-Given our lightcurve analysis of S1063 we expect SED-based filling factor uncertainties could be as large as $\sim$20\% from unluckily sampling peaks and troughs of the lightcurve.
+Given our light curve analysis of S1063 we expect SED-based filling factor uncertainties could be as large as $\sim$20\% if the individual photometry observations span peaks and troughs of the light curve.
 
@@
 
-The spot coverage fraction for S1063 determined in this work is consistent with the range of spot coverage seen on RS CVn of 30--40\% from measuring TiO band strength \citep{oneal96, oneal98, oneal04} and Doppler imaging \citep{hackman12}.
-The collective evidence supports the interpretation that S1063 and by extension other SSGs have magnetic activity so severe as to alter their positions in the HR diagram.
+The spot coverage fraction for S1063 determined in this work is consistent with the range of spot coverage seen on RS CVn systems of 30--40\% from measuring TiO band strength \citep{oneal96, oneal98, oneal04} and Doppler imaging \citep{hackman12}.
+The collective evidence supports the interpretation that S1063, and by extension other SSGs, have magnetic activity significant enough to alter their positions in the HR diagram, although continued work is needed in the photometric modeling of these sources (see Section~\ref{sec:model_comparison}).
+This interpretation is further supported by the flares present in the \emph{K2} light curves (see Figure~\ref{fig:periodogram}), which is a clear indicator of magnetic activity.
 
 Strong magnetic fields and starspots reduce convective energy transport efficiency, which in turn alters theoretical evolutionary model tracks from their unspotted/non-magnetic counterparts \citep{2013ApJ...779..183F,somers15,somers15b,somers20}.
-Understanding the physical nature of the magnetic activity and the impact it has on stellar structure and evolution requires comparison of high-fidelity observations with these theoretical models.
-An accurate HR diagram position requires determination of the effective temperature ($T_{\textrm{eff}}$) having accounted for spots, as well as the stellar luminosity.
+Understanding the physical nature of magnetic activity and the impact it has on stellar structure and evolution requires comparison of high-fidelity observations with these theoretical models.
+An accurate HR diagram position requires determination of the effective temperature ($T_{\mathrm{eff}}$) having accounted for spots, as well as the stellar luminosity.
 
@@
 %% Is the first sentence too obvious?
-Effective temperature relates the radius and luminosity of a star through the Stefan-Boltzmann Law.
+The radius and luminosity of a star provide an effective temperature through the Stefan-Boltzmann Law.
 The radius of S1063 remains constant over thermal timescales much longer than the span of available data.
-We assume the long-time averaged luminosity also remains constant as starspots come and go on the surface, but have a near-constant time-averaged occupation fraction.
-A hint of this quasi-static luminosity state can be conceptualized in Figure \ref{fig:lightcurve} with a relatively constant mean flux level of 89.5\% compared to the maximum global flux.
-In these limits, there exists a well-defined $T_{\textrm{eff}}$ that conventionally relates the long-time-averaged luminosity and radius:
+We assume the time-averaged luminosity also remains constant as starspots come and go on the surface, but have a near-constant time-averaged filling factor.
+This is supported by Figure \ref{fig:lightcurve} showing a relatively constant mean flux level of 89.5\% compared to the maximum global flux.
+With these assumptions, there theoretically exists a well-defined $T_{\mathrm{eff}}$ that conventionally relates the time-averaged bolometric luminosity and radius.
+For example, \citet{leiner17} fit the multi-band spectral energy distribution for S1063 with a single Castelli-Kurucz spectrum \citep{2003IAUS..210P.A20C} and find a best fit single-temperature $T_{\mathrm{eff}}$ of 4500 K.
+Our results, however, indicate that S1063 has a multi-temperature surface.
+Therefore, we can calculate a surface-averaged temperature:
 \begin{equation}
-T_{\textrm{eff}}^4 = f_{\textrm{s}} T_{\textrm{s}}^4 + (1 -f_{\textrm{s}}) T_{\textrm{amb}}^4 . \label{defineTeff}
+T_{\mathrm{eff}}^4 = f_{\mathrm{s}} T_{\mathrm{s}}^4 + (1 -f_{\mathrm{s}}) T_{\mathrm{amb}}^4 . \label{defineTeff}
 \end{equation}
-where $f_{\textrm{s}}$ is the long-time-averaged spot covering fraction, $T_{\textrm{s}}$ is the long-time-averaged spot temperature, $T_{\textrm{amb}}$ is the long-time-averaged ambient photosphere temperature.
-Two factors make it challenging to measure and interpret effective temperature of spotted stars in practice.
-First, the number of surface components may be misassigned.
-For example \citet{leiner17} fit the multi-band spectral energy distribution for S1063 with a single Castelli-Kurucz spectrum \citep{2003IAUS..210P.A20C} and find a best fit single-temperature $T_{\textrm{eff}}$ of 4500 K.
-Here we show that two temperatures is better justified.
-It may be that 3 components is even better justified, requiring a further adjustment to Equation \ref{defineTeff}.
-Second, instantaneously derived effective temperatures may be acquired at a time that is not representative of the steady-state.
+where $f_{\mathrm{s}}$ is the spot covering fraction, $T_{\mathrm{s}}$ is the spot temperature, and $T_{\mathrm{amb}}$ is the ambient photosphere temperature.
+This surface-averaged $T_{\mathrm{eff}}$ can be calculated for either a specific epoch of observation or using time-averaged values.
 
-Here we attempt to compare the surface-averaged temperature to one-dimensional stellar evolution models motivated by the surface conditions of the star \citep{somers20}.
-At the time of the IGRINS observation the $T_{\textrm{eff}}$ of S1063 derived with Equation \ref{defineTeff} is $4900\pm100$ K.
-This temperature is inconsistent with the 4500 K temperature determined via single-temperature SED fitting in \citet{leiner17}, indicative of the discrepancies between the spectral and photometric constraints outlined in Section~\ref{sec:model_comparison}, although we note that the previous temperature of 4500 K lands between the measured spot and ambient photosphere temperatures determined in this work.
+At the epoch of the IGRINS observation the $T_{\mathrm{eff}}$ of S1063 derived with Equation \ref{defineTeff} is $4900\pm100$ K.
+This temperature is inconsistent with the 4500 K temperature determined via single-temperature SED fitting in \citet{leiner17}, possibly indicative of the discrepancies between the spectral and photometric constraints outlined in Section~\ref{sec:model_comparison}, although we note that the previous temperature of 4500 K is between the measured spot and ambient photosphere temperatures determined in this work.
 
-Stars such as S1063 can have instantaneously-derived $T_{\textrm{eff}}$ values that vary based on the spot covering fraction at the time of observation.
-We know from the variable lightcurve (Figure~\ref{fig:lightcurve}) that stars such as S1063 have differing spot covering fractions on opposite observable hemispheres of the star causing optical variability.
-For example, at the four-year lightcurve maximum S1063 had approximately 20\% spot covering fraction and an instantaneously-derived surface-averaged $T_{\textrm{eff}}$ (for the observed hemisphere of the star) of 5000 K.
-At the lightcurve minimum with a 45\% spot covering fraction the surface-averaged $T_{\textrm{eff}}$ for the observed hemisphere would only be 4700 K.
+The instantaneously-derived $T_{\mathrm{eff}}$ value varies based on the spot covering fraction at the time of observation.
+We know from the variable light curve (Figure~\ref{fig:lightcurve}) that stars such as S1063 have differing spot covering fractions on opposite observable hemispheres of the star.
+For example, at the four-year light curve maximum S1063 had approximately a 20\% spot covering fraction and therefore an instantaneously-derived surface-averaged $T_{\mathrm{eff}}$ (for the observed hemisphere of the star) of 5000 K.
+At the light curve minimum with a 45\% spot covering fraction the surface-averaged $T_{\mathrm{eff}}$ for the observed hemisphere would only be 4700 K.
 
-The true surface-averaged $T_{\textrm{eff}}$ includes the entire stellar surface.
-Observationally constraining the surface-averaged $T_{\textrm{eff}}$ requires either multi-epoch spectrum observations at both the lightcurve maximum and minimum, or a single observation at the mean flux level.
-The date of the IGRINS observation corresponds to a flux level of 91.2\% compared to the global maximum, suggesting that observed spot coverage is a close proxy for the mean state of S1063 within the uncertainties.
-Therefore, we conclude that the total surface-averaged $T_{\textrm{eff}}$ of S1063 is consistent with the observed surface-averaged $T_{\textrm{eff}}$ of $4900\pm100$ K.
-We stress, however, that determining a single $T_{\textrm{eff}}$ value for spotted stars makes model comparisons exceedingly nuanced.
-Stars like S1063 may undergo stellar cycles with possibly massive changes to spot coverage over timescales of hundreds of years, much longer than our observational windows.
-
-\subsection{Flares}
-
-A star as allegedly active and spotted as S1063 should exhibit other metrics associated with activity beyond the already-mentioned hallmarks such as H$\alpha$, x-ray emission, and starspot coverage.
-We should see flares.
-A closer re-examination of Figures \ref{fig:periodogram} and \ref{fig:lightcurve} reveals conspicuous stellar flares in all three of the campaigns of \emph{K2}.
-The mere existence of these flares conveys supporting evidence for the magnetic interpretation for SSGs.
-The detection of flares also hints at a promising prediction for the analysis of known and undiscovered SSGs: \emph{TESS} lightcurves of sub-subgiants should exhibit a comparable frequency and amplitude of stellar flares as those seen in S1063.
-We may also expect a difference in the frequency of flares between SSGs and RS CVn stars if these two populations possess inherently different degrees of magnetic activity.
-Such a comparison will benefit from the much larger sample sizes of SSGs afforded by the all-sky \emph{TESS} mission in concert with \emph{Gaia}.
+The true surface-averaged $T_{\mathrm{eff}}$ includes the entire stellar surface.
+Observationally constraining the surface-averaged $T_{\mathrm{eff}}$ requires either multi-epoch spectrum observations at both the light curve maximum and minimum, or a single observation at the mean flux level.
+The date of the IGRINS observation corresponds to a flux level of 91.2\% compared to the global maximum, suggesting that observed spot coverage is a close proxy for the mean state of S1063 with a flux level of 89.5\%.
+Therefore, we conclude that the total surface-averaged $T_{\mathrm{eff}}$ of S1063 is consistent with the observed surface-averaged $T_{\mathrm{eff}}$ of $4900\pm100$ K.
+We stress, however, that determining a single $T_{\mathrm{eff}}$ value for spotted stars makes model comparisons exceedingly nuanced.
 
@@
 
-The radius of S1063 is encoded into data in three ways: via surface gravity-sensitive spectral lines, in the SED and HR Diagram position, and embedded within the $v\sin{i}$ measurement.
-Measuring the radius of spotted stars would help constrain magnetic inflation models, especially in light of the single $T_{\textrm{eff}}$ nuances elaborated above.
+The radius of S1063, important for determining the bolometric luminosity, is encoded into data in three ways: via surface gravity-sensitive spectral lines, in the SED and HR Diagram position through the luminosity, and embedded within the $v\sin{i}$ measurement.
+Measuring the radius of spotted stars would help constrain magnetic inflation models, especially in light of the $T_{\mathrm{eff}}$ nuances elaborated above.
 
-Our weak constraints on surface gravity from the IGRINS spectra cannot meaningfully inform the radius without mass.
-Previously determined SED-based photometric results suggest a radius of $R_{\star} = 2.8-3.4 R_\odot$ (see Table~\ref{tab:s1063parameters}).
+Our weak constraints on surface gravity from the IGRINS spectra cannot meaningfully inform the radius without an independent measurement of the stellar mass.
+Previously determined SED-based photometric results suggest a radius of $R_{\star} = $2.8--3.4 $R_\odot$ (see Table~\ref{tab:s1063parameters}).
 We elaborate on constraining the radius from $v\sin{i}$ here.
-The stellar radius $R_{\star}$ contributes to the magnitude of the equatorial velocity $v_{\mathrm{eq}}$ for a given rotation rate and projected stellar inclination angle $i$:
+
+The stellar radius $R_{\star}$ contributes to the observed magnitude of the equatorial velocity $v$ given a rotation rate $P_{\mathrm{rot}}$ and projected stellar inclination angle $i$:
 \begin{eqnarray} 
@@
 
-Our \texttt{Starfish}/IGRINS-derived $v\sin{i}=10.0 \pm 1.0 \; \mathrm{km\,s^{-1}}$ and \texttt{celerite}/K2 derived period $P_{\mathrm{rot}}=23.5 \pm 0.1$ constrain $R\sin{i} = 4.6 \;R_\odot$, with a formal statistical uncertainty of $\pm 0.5 \;R_\odot$.
-For stars viewed at an inclination other than perfectly edge-on, the typical inferred stellar radius $R_{\star}$ must exceed $4.6 R_{\odot}$.
+Our \texttt{Starfish}/IGRINS-derived $v\sin{i}=10.0 \pm 1.0 \; \mathrm{km\,s^{-1}}$ and \texttt{celerite}/K2 derived period $P_{\mathrm{rot}}=23.5 \pm 0.2$ days constrain $R\sin{i} = 4.6 \;R_\odot$, with a formal statistical uncertainty of $\pm 0.5 \;R_\odot$.
+For stars viewed at an inclination other than perfectly edge-on, the typical inferred stellar radius $R_{\star}$ must exceed 4.6 $R_{\odot}$.
 If we instead adopt the optically-determined $v\sin{i}=8\; \mathrm{km\,s^{-1}}$ from \citet{mathieu03} the radius must exceed 3.7 $R_{\odot}$.
-In either case, this kinematically-inferred radius is larger than the radius range determined through photometric studies.
-A two-temperature SED of S1063 adopting the minimum $R\sin{i}$ values is far too bright compared to observed photometry, suggesting our $R\sin{i}$ limits may be biased to larger values in some way.
+In either case, this kinematically-inferred radius is larger than and inconsistent with the radius range determined through photometric studies.
+A two-temperature SED of S1063 adopting the minimum $R\sin{i}$ value is too bright compared to observed photometry, suggesting the $R\sin{i}$ limits may be biased to larger values in some way.
 
 One possible source of this radius discrepancy is the spotted surface somehow alters the assumptions behind Equation \ref{rsini}.
-Possible astrophysical uncertainties that could potentially bias the $v\sin{i}$ for heavily spotted sub-giants include the adopted limb-darkening prescription, micro- or macro-turbulence, and Zeeman broadening.
+Possible astrophysical uncertainties that could potentially bias $v\sin{i}$ values of heavily spotted subgiants include the adopted limb-darkening prescription, micro- or macro-turbulence, and Zeeman broadening.
 Additionally, the observed period could be biased via differential rotation combined with starspots constrained to either high or low latitudes, starspot evolution timescales similar to the rotation period, and aliasing from regularly-spaced longitudinal surface symmetries.
 The magnitude and/or direction of these period biases are generally uncertain.
-We note that the other SSG in M67, S1113, also has an anomalously-large $R\sin{i}$ value determined from $v\sin{i}$ \citep{mathieu03}, suggesting that perhaps the surface conditions of SSGs cause spectral broadening such that the standard $v\sin{i}$ measurement is not truly a measure of the stellar rotation velocity.
+We note that the other SSG in M67, S1113, also has an anomalously-large $R\sin{i}$ value determined from $v\sin{i}$ \citep{mathieu03}, suggesting that perhaps the surface conditions of SSGs cause spectral broadening such that the standard $v\sin{i}$ measurement is not truly a measure of the projected stellar rotation velocity.
 A campaign of intense Doppler-imaging-style observations could act to disentangle some of these uncertainties in the future, though such a campaign would require extreme spectral resolution in order to resolve surface structures given the relatively low apparent $v\sin{i}$.
 
-The star could hypothetically be much larger than SED-based estimates, meaning the SED is understating the total luminosity somehow, an unlikely but conceivable scenario.
-We assume a two-temperature stellar surface to derive our estimates for spot filling factor and effective temperature.
+Another possibility is S1063 could hypothetically be much larger than SED-based estimates, meaning a one- or two-temperature fit to the SED is understating the total luminosity.
+In this work we assume a two-temperature stellar surface to derive our estimates for spot filling factor and effective temperature.
 In reality, this star---and most active stars more generally---must exhibit a range of apparent surface features attributable to umbra, penumbra, faculae, chromospheric emission, and other phenomena unaccounted for in this work \citep{berdyugina05, 2009A&ARv..17..251S}.
@@
 
-The prospect of undercounting umbra suggests yet another candidate interpretation of the SED-$R\sin{i}$ tension: S1063 really is as large as $4.6 R_{\odot}$, but it has a profound coverage of imperceptibly dark umbra that has gone undetected with our methodology.
-Such a seemingly perverse scenario is oddly self-consistent: painting a surface with dark umbra represents the ultimate impediment to a star's ability to transport away its internal energy, demanding that the star increase dramatically in radius in order to reach energy balance.
-The SED would not readily betray the existence of these dark umbral regions, nor would any other of the measurements presented here.
+The prospect of undercounting umbra suggests yet another candidate interpretation of the SED-$R\sin{i}$ tension: S1063 really has a radius of 3.7--4.6 $R_{\odot}$ or larger, but has a profound coverage of imperceptibly dark umbra that is undetected with our methodology.
+This scenario is oddly self-consistent: painting a surface with dark umbra dramatically impedes the ability of the star to transport away internal energy, demanding a dramatic increase in radius in order to reach energy balance.
+The SED would mask the existence of these dark umbral regions, as would our spectroscopic methods presented here.
 
-One technique could help discern such pathologically magnetically dark stars.
-Stellar surface tomography with occulting bodies such as eclipsing binaries or large planets provide a stringent test.
-The occultation depths, impact parameters, orbital parameters, and occultation durations for an ensemble of SSG eclipsing binaries would encode a pattern of primary stars losing too little flux during occultations.
-Eclipse depths would be too shallow.
-Or, if SSG starspots are small and distributed quasi-isotropically, eclipses would show dramatic spot-crossing events as eclipse chords contain gigantic black patches surrounded by brighter ambient photosphere.
-S1063 does not show evidence for occultations in its \emph{K2} lightcurve.
-Future larger samples of SSG EBs may help retire these scenarios, however unlikely they may seem.
-
-%We consider for the moment a hypothetical perfectly edge-on orientation.
-The kinematically derived radius exceeds its photometric counterpart by 2.6$\,\sigma$, an ostensible tension for these two disparately-sourced estimates.
-However, we consider the possibility that the star is so profoundly spotted as to alter the assumptions that lead to Equation \ref{rsini}.
-At least four sources of unaccounted-for astrophysical uncertainties can conceivably bias the derived $v\sin{i}$ for heavily spotted sub-giants.
-The limb-darkening prescription, unaccounted for Zeeman broadening, micro- or macro- turbulent velocity, and the latitudinal segregation of starspots all act to modulate the mapping from observed line profile to inferred $v\sin{i}$.
-On the other hand, the period can be systematically biased in three significant ways: differential rotation combined with latitudinal starspot segregation, starspot evolution on timescales comparable to the rotation period, and aliasing from regularly-spaced longitudinal surface symmetries.
-The aggregate magnitude and/or direction of these systematic biases is generally uncertain, and even the rank order of which bias predominates may defy the routine assumptions applied to modestly spotted stars like the Sun.
-We therefore attribute the apparent tension in our radius uncertainties to these epistemic uncertainties with magnitudes comparable to or greater than the formal statistical uncertainties.
-A campaign of intense Doppler-Imaging-style observations could act to disentangle some of these uncertainties in the future, though such a campaign would require extreme spectral resolution in order to resolve surface structures given the relatively low apparent $v\sin{i}$.
-
-%-Now there is tension with the colors of the SPOTS models, but colors of spots are weird.
-The lower spot coverage models predict bluer colors than observed.
-Perhaps some chromospheric component?
-This is probably fine.
-
-%-Perhaps demonstrates a need for a dual modeling approach of surface treatment with internal structure changes and comparing against a larger sample of stars
+Studying SSGs in eclipsing binaries would provide strong constraints on the stellar radius as well as provide a stringent test to discern a significant presence of dark umbra, where an ensemble of SSG eclipsing binaries would reveal a pattern of primary stars with shallow eclipse depths.
+If SSG starspots are small and distributed quasi-isotropically, eclipses would also show dramatic spot-crossing events as eclipse chords contain gigantic black patches surrounded by brighter ambient photosphere.
+Future large samples of SSG eclipsing binaries may help investigate these scenarios while providing crucial radius measurements necessary for confident comparisons of this class of stars to theoretical stellar evolutionary models.
 
@@
 
-On the other hand, faculae and plage act to add a hotter-than-average surface component.
+Compared to umbra, faculae and plage act to add a hotter-than-average surface component.
 Our two-component model cannot accurately account for the coexistence of spots and faculae with an ambient photosphere \citep{1998A&A...329..747S}.
@@
 Our reliance on \texttt{PHOENIX} synthetic spectra adds a model-dependent systematic to our entire approach.
-The unavailability of a large number of spot-free high-precision high-resolution empirical template spectra across all of $H$-band demands the use of these models in order to compare to IGRINS data.
+The current lack of numerous spot-free high-precision and high-resolution empirical template spectra across all of $H$-band demands the use of these models in order to compare to IGRINS data.
 The ability of such synthetic spectra to resemble starspots remains an unknown.
@@
 The Gaussian process ``Global Kernels'' employed in \texttt{Starfish} account for some degree of correlated data-model residual mismatching.
-We did not employ the ``Local kernels'' approach, which cause a 30 K systematic bias in comparable quality spectra of WASP-14 also compared to the \texttt{PHOENIX} models \citet{czekala15}.
+We did not employ the ``Local kernels'' approach, which would otherwise have corrected for an up to 30 K systematic bias in comparable quality spectra of WASP-14 also compared to the \texttt{PHOENIX} models \citep{czekala15}.
 We therefore assign at least a 30 K systematic bias in our temperature estimates based on the prospect of individual line outliers polluting our fit residuals.
-We co-assign a coarse estimate of 100--200 K to so-called ``label noise'', associated with the alignment of a best fit \texttt{PHOENIX}-provided temperatures and an unseen ground-truth label for the ``True'' temperature of the spots.
+We co-assign a coarse estimate of 100--200 K to so-called ``label noise,'' associated with the alignment of a best fit \texttt{PHOENIX}-provided temperatures and an unseen ground-truth label for the ``True'' temperature of the spots.
 New studies of the Sun based on DKIST may offer the best future avenue for testing such assumptions and refining the ability to distinguish starspot emission from ambient photosphere.
-
-%\subsection{Starspots as confounding factors}
-%Mass, age, and metallicity uniquely map a main sequence star to its HR diagram position.
-A fourth factor---rotation---confounds this mapping in as-yet-unknown ways.
-Rotation might enhance spread in HR diagram positions (cite XX Davenport, Douglas?), with the most conspicuous spreads in the pre-main sequence regime (cite XX Covey, Stauffer).
-Spreads in the HR diagram offer clues to the consequences of rotation.
-Increased rotation heightens the magnetic dynamo strength and concomitant surface magnetic field.
-These magnetic fields suppress convective efficiency, meaning the star must increase in size at a lower effective temperature to allow the same amount of internal energy to escape (cite XX Feiden): rotating stars become bigger and cooler than their non-rotating counterparts (cite XX Somers).
-The interplay of rotation, dynamo, and surface fields remain an active area of research, with bright prospects for a unified theory involving the degree of magnetic complexity parameter (cite XX Garraffo).
-
-%Surface magnetic fields offer two key observational manifestations.
-The Zeeman Effect splits spectral line levels in magnetic-sensitive atomic transitions (cite XX Johns-Krull).
-Starspots induce stellar surface inhomogeneities that can be seen in the modulation of
-
-%The story in the post-main sequence is less clear.  Angular momentum transport governs rotation  as stars evolve over orders of magnitude in size.
-
-%\item Conceivable geometries with circumpolar active longitudes, or migrating active latitudes
-%\item Biases introduced if we assume a spot-free model
-
 \section{Conclusions}
@@
 
-The impact of magnetic activity on stellar evolution is a quickly developing field in stellar astrophysics.
-SSGs serve an important sample for furthering our knowledge, as they exhibit dramatic offsets from typical stellar evolutionary pathways \citep{geller17, leiner17}.
+We use a novel combination of a light curve analysis and a near-IR spectral decomposition technique to constrain the starspot filling factor and spot temperature of SSG S1063 in open cluster M67.
+Previous work suggested that the underluminosity apparent in SSGs could be caused by inhibited convective energy transport due to high magnetic activity \citep{leiner17}.
+Constraining the starspot filling factor is a helpful proxy for determining stellar magnetic activity, allowing us to directly compare observed photometry to model predictions for active stars.
+Additionally, our technique allows for constraints on a much larger sample of stars than can be studied with Doppler imaging or interferometry.
 
-We use a combination of a lightcurve analysis and a near-IR spectral decomposition technique to constrain the starspot filling factor of SSG S1063 in open cluster M67.
-Previous work suggested that the underluminosity apparent in SSGs could be caused by inhibited convective energy transport due to high magnetic activity \citep{leiner17}.
-Constraining star spot filling factor is a helpful proxy for determining stellar magnetic activity, and this spectral decomposition technique allows for constraints on a much larger sample of stars than can be studied with Doppler Imaging or interferometry.
+Assuming a two-temperature surface, we find a spot filling factor for S1063 of $32\pm7$\% at the time of the IGRINS observation with a spot temperature of $4000\pm200$ K, compared to the ambient photosphere temperature of 5200 K.
+We use this constraint to interpret the long-term variability observed in a four-year light curve combining ground-based ASAS-SN data with space-based \emph{K2} campaigns, with a minimum and maximum projected spot covering fraction of 20\% to 45\%, respectively.
+Importantly, this technique reveals that the maximum light during this time period does not correspond to an un-spotted star.
 
-We find a spot filling factor for S1063 of $32\pm7$\% at the time of the IGRINS observation.
-By combining this constraint with the variability seen in the four-year lightcurve we determine that this is approximately the mean state of the star over this four-year time period, with a minimum and maximum spot covering fraction of 20\% to 45\%, respectively.
-Importantly, this technique reveals that the maximum light during this time period did not correspond to an un-spotted star.
-This spot filling factor is consistent with those determined for RS CVn stars through other methods, suggesting that SSGs are another type of active giant star binary systems.
+Although the instantaneous spot filling factor changes based on the observation epoch, the time of the IGRINS observation happens to approximate the mean state of the star over this four-year time period.
+This spot filling factor is consistent with those determined for RS CVn systems through other methods, suggesting that SSGs are another type of active giant star binary system.
 
-The numerous sources of astrophysical uncertainties underscore how difficult it is to conduct a census for the effects of magnetic activity on a star.
-Geometric degeneracies, secular evolution, and starspot contrast effects make the problem partially degenerate.
-It is possible that different sensitivities to umbra or prenumbra features of spots, wavelength dependencies in detected spot size, or differences in the observed hemisphere of the star across different epochs of observation could all result in different determinations of spot filling factor between spectroscopic and photometric techniques.
-However, the state of current stellar activity theoretical models makes direct comparison difficult.
-We encourage future work in careful conversion between stellar structure models and observational signatures, including spectroscopic templates, to help resolve these apparent discrepancies.
-%The source of the discrepancies between spectroscopic and photometric methods is not entirely clear, but may be due to different sensitivities to umbra or prenumbra features of spots, wavelength dependencies in detected spot size, or differences in the observed hemisphere of the star across different epochs of observation.
+Careful comparison of observational constraints and theoretical predictions is necessary to understand the physical mechanisms responsible for how magnetic activity alters stellar evolution in stars such as SSGs, but this comparison can be fraught.
+We find that reporting a single ``$T_{\mathrm{eff}}$" for active spotted stars is a complicated prospect, possibly leading to unclear or possibly incorrect observational and model comparisons.
+The surface-averaged $T_{\mathrm{eff}}$ derived from our results is not consistent with a single SED-fit temperature for S1063.
+Additionally, the instantaneously-observed surface-averaged $T_{\mathrm{eff}}$ for S1063 varies from 4700 K to 5000 K depending on the epoch of observation, as only one hemisphere of the star can be observed at a time.
+We also find a wide range of observational constraints on the radius of S1063, and suggest that surface conditions of SSGs may inflate $R\sin{i}$ values.
+We encourage future work to be as explicit as possible when reporting temperatures and radii for active stars to enable the most accurate comparisons between observational and theoretical efforts.
 
-We find that reporting a single ``$T_{\mathrm{eff}}$" for active spotted stars is a confusing concept at best, and can lead to unclear or possibly incorrect observational and model comparisons.
-The surface-averaged $T_{\mathrm{eff}}$ derived from our results is not consistent with a single SED-fit temperature for S1063.
-Additionally, determining the surface-averaged $T_{\mathrm{eff}}$ for S1063 would vary from 4700 K to 5000 K depending on the epoch of observation, as only one hemisphere of the star can be observed at a time.
-We encourage future work in this area to be as explicit as possible when reporting temperatures for active stars to enable the most accurate comparisons between observational and theoretical efforts.
+There is still much to learn about spot morphologies and temperature profiles, the observational biases impacting constraints of spot filling factors, and how to connect measurements of the stellar surface to the internal structure.
+SSGs serve an important sample for furthering our knowledge in these areas, as they exhibit dramatic offsets from typical stellar evolutionary pathways.
+Focused studies such as this one serve as important benchmarks for technique development.
+Future larger studies of SSGs will provide important test samples for observational and theoretical comparisons to further untangle the impact of stellar activity on stellar evolution.
 
-There is still much we do not understand about spot morphologies, the observational biases that impact our assumptions about spot filling factors, and how measurements of the stellar surface can be connected to the internal structure of the star.
-Focused studies such as these serve as important benchmarks for technique development, but larger studies of starspots on active stars are necessary to explore the suggested discrepancies between different observational methods of determining spot filling factors.
-These larger studies would also serve as important test samples for observational and theoretical comparisons to untangle the impact of stellar activity on stellar evolution.
+%\begin{acknowledgements}
 
-\clearpage
-\pagebreak
+\section{Acknowledgements}
+We thank the referee for their helpful comments which improved this paper.
+NMG is a Cottrell Scholar receiving support from the Research Corporation for Science Advancement under grant ID 27528.
+EML is supported by an NSF Astronomy and Astrophysics Postdoctoral Fellowship under award AST-1801937.
 
-%\appendix
-%\section{Appendix heading}
-%\label{methods-details}
-%Placeholder text
+The custom project files including Jupyter Notebooks, raw and reduced data, Starfish configuration files, reproducible python environment files, and entire project revision history is publicly available as a git repository at \url{https://github.com/BrownDwarf/subsub}.
 
-\begin{acknowledgements}
-
-%ADS
 This research has made use of the NASA Astrophysics Data System.
-%IGRINS
 This work used the Immersion Grating Infrared Spectrometer (IGRINS) that was developed under a collaboration between the University of Texas at Austin and the Korea Astronomy and Space Science Institute (KASI) with the financial support of the US National Science Foundation under grant AST-1229522, of the University of Texas at Austin, and of the Korean GMT Project of KASI.
-%Kepler
-This paper includes data collected by the Kepler mission. Funding for the Kepler mission is provided by the NASA Science Mission directorate.
-% MAST
+This paper includes data collected by the Kepler mission.
+Funding for the Kepler mission is provided by the NASA Science Mission directorate.
 Some of the data presented in this paper were obtained from the Mikulski Archive for Space Telescopes (MAST).
 STScI is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS5-26555.
+This work has made use of data from the European Space Agency (ESA) mission {\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed by the {\it Gaia} Data Processing and Analysis Consortium (DPAC, \url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}).
+Funding for the DPAC has been provided by national institutions, in particular the institutions participating in the {\it Gaia} Multilateral Agreement.
+%\end{acknowledgements}
 
-%gaia
-This work has made use of data from the European Space Agency (ESA) mission
-{\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed by the {\it Gaia}
-Data Processing and Analysis Consortium (DPAC,
-\url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding for the DPAC
-has been provided by national institutions, in particular the institutions
-participating in the {\it Gaia} Multilateral Agreement.
+\facilities{Smith (IGRINS), ASAS, Kepler, Gaia, PS1}
 
-\end{acknowledgements}
-
-\facilities{Smith (IGRINS), Gaia, ASAS}
-
-\software{  pandas \citep{mckinney10},
+\software{pandas \citep{mckinney10},
   emcee \citep{foreman13},
+  celerite \citep{2017AJ....154..220F},
   matplotlib \citep{hunter07},
@@
   seaborn \citep{waskom14},
-  lightkurve \citep{geert_barentsen_2019_2565212}}
-
-\clearpage
+  lightkurve \citep{geert_barentsen_2019_2565212},
+  saphires \citep{Tofflemireetal2019} }
 
